# Information about this project

## Abstract

Earthworms are key ecosystem engineers whose life-history traits are strongly influenced by environmental conditions and chemical stress. Mechanistic models are therefore needed to integrate these multiple drivers and predict organism responses under realistic exposure scenarios. In this study, we first developed a Dynamic Energy Budget (DEB) model for *Aporrectodea caliginosa* describing the effects of food availability, population density, and adult isolation on growth, maturation, and reproduction, and subsequently extended this model into a DEB–Toxicokinetic–Toxicodynamic (DEB-TKTD) framework to characterize the effects of imidacloprid and epoxiconazole.

The baseline DEB model was calibrated using literature data and a new density experiment initiated at the juvenile stage. Alternative formulations were compared regarding food acquisition, reserve contribution to fresh body mass, and post-maturation energy allocation. The best-supported formulations combined a progressive change in energy allocation after maturation, a normalized hyperbolic functional response, and a weak contribution of reserves to fresh body mass. Density-dependent reductions in juvenile growth were largely explained by lower food acquisition per individual, while simulations of isolated adults suggested that reproductive energy may be partly redirected toward somatic processes when mating opportunities are absent.

The DEB model was then coupled with previously calibrated two-compartment toxicokinetic models and toxicity data for juvenile growth, adult growth, and reproduction. Toxicodynamic parameters and alternative physiological modes of action were estimated independently for both pesticides. Imidacloprid effects were best described by a combined reduction in assimilation and growth, whereas reduced assimilation alone provided the most parsimonious explanation for epoxiconazole toxicity. Estimated internal tolerance concentrations were substantially lower for imidacloprid than for epoxiconazole, consistently with its greater toxicity across life-history endpoints. The models captured the overall concentration-dependent responses, although systematic deviations remained at high imidacloprid and mortality were not fully represented.

By linking environmental conditions, internal exposure, energetic processes, and life-history responses within a unified framework, this study provides a mechanistic basis for predicting pesticide effects in earthworms and supports future applications to chemical mixtures and multiple environmental stressors.

## Preliminary information about this study

This study is part of the french [ANR project EEWORM](https://eeworm-website-eeworm-28029feb17f172b5d59fe25680d42ab1a87633fff.pages-forge.inrae.fr).

### Contributors

**Authors of this study** (Credit synthaxe) :

-   [Lisa Gollot](https://orcid.org/0009-0004-5074-4275) : Conceptualization, Data curation, Formal Analysis, Investigation, Methodology, Software, Validation, Visualization, Writing – Original Draft Preparation.
-   Laura Frattaroli (INRAE research technician) : Data curation, Investigation, Methodology, Writing – Review & Editing.
-   [Raphaël Royauté](https://rroyaute.github.io)\$ : Conceptualization, Funding Acquisition, Methodology, Project Administration, Resources, Supervision, Writing – Review & Editing.
-   [Juliette Faburé](https://orcid.org/0000-0002-8055-3224) : Funding Acquisition, Methodology, Resources, Supervision, Writing – Review & Editing.
-   [Rémy Beaudouin](https://orcid.org/0000-0002-2855-1571) : Formal Analysis, Funding Acquisition, Methodology, Resources, Software, Supervision, Writing – Review & Editing.

**Interns/technicians who also contributed to this study** :

-   Valentine Lebars (M1 internship) : Toxicokinetics tests & EC50 tests & Earthworms breeding (May - July 2024)
-   Maia Collombel (L3 internship) : Toxicokinetics tests & EC50 tests & Earthworms breeding (May - June 2024)
-   Laura Frattaroli (research technician) : Earthworms breeding & Mixture tests (October 2024 - August 2025)
-   Julien Rouyer (Gap year intership of engineering school) : Earthworms breeding & Mixture tests (October - December 2024)
-   Cheikh Ahmed Tidane Sarr (M2 intership) : Mixture tests (March - August 2025)

### Fundings

This work was funded by the French National Research Agency (ANR) through the project EEWORM (N°ANR-23-CE34-0002) and the Biosphera graduate school of the University Paris-Saclay (PhD Grant).

### GANTT {#sec-GANTT}

```{r,, include=F}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)
library(forcats)
library(nord)

Nord_frost <- nord(palette = "frost")
Nord_aurora <- nord(palette = "aurora")
Nord_polar <- nord(palette = "polarnight")
```

```{r, echo=F, warning=F}
#| fig-cap: GANTT
#| label: fig-GANTT
#| fig-width: 15
#| fig-height: 5

# Sample data
data_gantt <- data.frame(
  task = c(
    "1. Preliminary tests",                      # 1
    "2.1. EC50 tests for IMD",                   # 2
    "2.2. EC50 tests for EPX",                   # 3
    "2.3. TK Experiment for IMD and EPX",
    "2.4. GUT Experiment",
    "2.5. TK BIS",
    "3.1. Mixture tests - Autumn 2024",          # 4
    "3.2. Mixture tests - Small test with IMD",  # 5
    "3.3. Mixture tests - Spring 2025",          # 6
    "3.3. Mixture tests - Hatchling monitoring", # 7
    "4. DENS Experiment"
  ),
  start_date = as.Date(
    c(
      "2024-03-05",                              # 1
      "2024-04-01",                              # 2
      "2024-05-03",                              # 3
      "2024-05-28",
      "2026-09-16",
      "2026-10-14",
      "2024-10-14",                              # 4
      "2025-01-07",                              # 5
      "2025-03-25",                              # 6
      "2025-04-30",                              # 7
      "2025-06-18"
    )
  ),
  end_date = as.Date(
    c
    ("2024-04-19",                               # 1
      "2024-08-08",                              # 2
      "2024-08-08",                              # 3
      "2024-07-08",
      "2026-09-17",
      "2026-11-28",
      "2024-12-18",                              # 4
      "2025-02-05",                              # 5
      "2025-04-30",                              # 6
      "2025-06-10",                              # 7
      "2025-11-05"
    )
  ),
  status = c(
    "Completed",                                 # 1
    "Completed",                                 # 2
    "Completed",                                 # 3
    "Completed",
    "Completed",
    "Completed",
    "Completed",                                 # 4
    "Completed",                                 # 5
    "Completed",                                 # 6
    "Completed",                                  # 7
    "Completed"
  )
)

# Custom color palette for the statuses

status_colors <- c("In Progress" = Nord_frost[1], "Completed" = Nord_frost[4])

# Creating the Gantt chart
ggplot(
  data_gantt, 
  aes(
    x = start_date, 
    # y = reorder(task, -as.numeric(start_date))
    y = fct_rev(task)
  )
) +  # Reorder tasks
  
  geom_segment(
    aes(
      xend = end_date, 
      yend = task, 
      color = status
    ), 
    size = 6, 
    lineend = "round",
    alpha = 0.7
  ) +  # Rounded bars
  
  geom_text(
    aes(
      x = ymd(start_date) + (ymd(end_date)-ymd(start_date))/2, 
      label = task,
    ),
    hjust = 0.5,
    vjust = -1.2,
    size = 4, 
    color = "black",
    fontface = "bold"
  )+
  
  scale_color_manual(values = status_colors) +  # Apply custom colors
  
  labs(
    title = "Project Timeline",
    x = NULL,  # Remove axis title for x
    y = NULL,  # Remove axis title for y
    color = "Status"
  ) +
  
  theme_minimal(base_family = "Arial") +                                          # Use a clean, sans-serif font
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),             # Title style
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    # axis.text.y = element_text(size = 12, hjust = 0, face = "bold"),                                        # Make task labels bold
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 10, color = "grey40"),                      # Date labels in grey
    panel.grid.minor = element_blank(),                                           # Remove minor grid lines
    panel.grid.major.y = element_blank(),                                         # Remove horizontal grid lines
    panel.grid.major.x = element_line(color = "grey85", linetype = "dashed")      # Subtle dashed vertical grid
  ) +
  scale_x_date(
    date_labels = "%b %Y", 
    date_breaks = "2 month", 
    expand = c(0, 0),
    limits = c(ymd("2024-02-01"), ymd("2026-12-31"))
    )  # Custom date formatting


```

## How to use this repository ?

### Repository organisation

The git repository linked to this website is available [here](https://github.com/LisaGllt/Acali-DEB).

Folders containing files concerning directly the study :

-   `data` folder : Contains the raw data files with direct notations from the experiments
-   `functions` folder : Contains R scripts with general functions used throughout different scripts
-   `quarto` folder : Contains all the `.qmd` files that generate the html pages, and their associated cache and files which cannot be moved to another folder.
-   `mod` folder : Contain all the models generated.
-   `photos` folder : Contains all photos used in html pages
-   `fig` folder : Contains all figure generated by quarto documents
-   `references` folder
    -   `apa.csl` : File of the reference style used for the website
    -   `reference.bib` : File containing all references from a zotero library

Folders concerning the setup of the git repository and the web pages :

-   `_book` : Where the final html pages are created
-   `index.qmd` : Home page of the web site (cannot be put in the `quarto` folder)
-   `_quarto.yaml` : YAML file that setup the structure of the website from the quarto (`.qmd`) documents
-   `_freeze` folder : Cache the results of code blocks (code cells) to avoid recalculating them on each execution
-   `.git`, `.gitignore` & `.github` : Git related folders
-   `.quarto` : Store configuration files, metadata, and intermediate files related to a Quarto project
-   `.Rproj.user` & `Acali-DEB.Rproj` : R project related files
-   `appearance` folder :
    -   `html_css.scss` : CSS file to modify the look of the html pages
    -   `lightnord.theme` : Theme to use for code blocks displayed in the html pages

### How to reproduce everything

If you wish to reproduce the results of this study, all you need are available in the `quarto` folder and the `mod` folder.

Instructions :

-   Whether or not you want to run the models again, please delete the folders from the `quarto` folder that end by `_cache` or `_files` and delete all the figures present in the `fig` folder.
    -   If you do not want to run the models again, move on to the next step
    -   If you wish to run the models again, please delete the files in `mod` but the `.model` files and keep the arborescence)
-   Then, you can render again all .qmd files from the `quarto` folder in the alphabetical order of their name. Some code line will have to be de-commented for some figures to be rendered again.
