```{r, include = F}
library(here)
source(file=here::here("functions/fun.R"))
f_load_libraries_colors()

path_fig <- here::here("fig/DENS/")

pal_dens <- c(Nord_aurora[5], rev(Nord_frost))
```

# DENS experiment - Impact of density and food quantity

## Protocol

Synchronized newly hatched earthworms are put in cosms with 200 g of Closeaux soil with a WHC of 70%. They are fed every 14 days and the soil is renewed every 28 days. Soil humidity is checked every week. Earthworms are weighted every 14 days. Once at least one earthworm is adult, cocoons produced are retrieved every 28 days when changing the soil.

Conditions :

-   D1 : One earthworm per cosm \| Food = 3 g/14 days
-   D2 : 2 earthworms per cosm \| Food = 3 g/14 days
-   D2b : 2 earthworms per cosm \| Food = 6 g/14 days
-   D5 : 5 earthworms per cosm \| Food = 3 g/14 days
-   D7 : 7 earthworms per cosm \| Food = 3 g/14 days

Some earthworm died in the first 14 days of the experiment. Another batch of earthworms were then started 28 days after the first one.

## Results

```{r}
df_dens_growth_full <- read_excel(here::here("data/Data_expe_raw/Data_DENS.xlsx"), sheet=1)%>%
  mutate(
    ID = paste0(Lot, Condition, Nb_rep),
    Weight = as.numeric(w),
    L = Weight^(1/3), 
    Lot = as.factor(Lot),
    Nb_rep = paste0(Lot, Nb_rep)
    ) 

df_dens_growth <- df_dens_growth_full |> 
  filter(Keep == "Yes") |> 
  filter(!(Nb_rep %in% c("B1", "B2")))

# Mean at the replicate level
df_dens_growth_mean_rep <- df_dens_growth %>%
  aggregate(Weight~Condition+Nb_rep+Lot+t, FUN=mean)

# Mean at the condition level
df_dens_growth_mean_cond <- df_dens_growth %>%
  aggregate(Weight~Condition+t, FUN=mean)

df_dens_repro <- read_excel(here::here("data/Data_expe_raw/Data_DENS.xlsx"), sheet=2)%>%
  mutate(
    ID = paste0(Lot, Condition, Nb_rep),
    Lot = as.factor(Lot),
    Nb_rep = paste0(Lot, Nb_rep)
    ) |> 
  filter(Keep == "Yes") |> 
  filter(!(Nb_rep %in% c("B1", "B2")))

df_dens_repro_mean_cond <- df_dens_repro %>%
  aggregate(Reproduction~Condition+t, FUN=mean)

```

### Initial conditions

```{r, warning = F, message = F}
#| fig-cap: Initial weight of earthworms.
#| label: fig-densinit
#| fig-height: 4
#| fig-width: 6


df_dens_t0 <- subset(df_dens_growth, t==0)

p <- ggplot(
  data = df_dens_t0,
  aes(
    x = "",
    y = Weight
  )
)+
  geom_boxplot(
    alpha=0,
    color=Nord_polar[4]
  )+
  geom_dotplot(
    aes(
    color = Lot,
    fill = Lot
    ),
    binaxis='y',
    stackdir='center',
    alpha=0.5
  )+
  labs(
    x="Conditions",
    y = "Weight (mg)"
  )+
  scale_color_manual(
    values = c(Nord_frost[4], Nord_polar[4])
  )+
  scale_fill_manual(
    values = c(Nord_frost[4], Nord_polar[4])
  )+
  facet_wrap(
    ~Condition,
    ncol=5
    )+
  theme_minimal()
p
```

```{r, include=FALSE}
ggsave(
  filename = "DENS_initial_state.png",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
```

```{r}
cat("Summary of initial weights : \n")
summary(df_dens_t0$Weight)
```

### Growth trajectories

@fig-densgrowthtraj shows all data points collected during the experiment.

```{r, warning = F, message = F}
#| fig-cap: Growth trajectories of earthworms per conditions.
#| label: fig-densgrowthtraj
#| fig-height: 8
#| fig-width: 8

xmax <- 170
ymax <- 2500

p <- ggplot()+
  geom_point(
    data = df_dens_growth_full,
    aes(
      x=t,
      y=Weight,
      color=as.factor(Condition),
      group=as.factor(ID)
    ),
    alpha=0.5,
    size=1
  )+
  geom_point(
    data = df_dens_growth_mean_rep,
    aes(
      x=t,
      y=Weight,
      color=as.factor(Condition)
    ),
    size=1.2
  )+
  geom_line(
    data = df_dens_growth_mean_rep,
    aes(
      x=t,
      y=Weight,
      color=as.factor(Condition)
    )
  )+
  scale_color_manual(
    name="Conditions",
    values=pal_dens
    )+
  facet_grid(cols=vars(Condition), rows=vars(Nb_rep))+
  scale_x_continuous(
    limits = c(0, xmax),       
    breaks = seq(0, xmax, by = 28),
    minor_breaks = seq(0, xmax, by = 14) 
  ) +
  ylim(0, ymax)+
  labs(
    x="Time (days)",
    y = "Weight (mg)"
  )+
  theme_minimal()
p
```

```{r, include=FALSE}
ggsave(
  filename = "DENS_growth_replicates.png",
  plot = p,
  width = 6, height = 10,
  path = path_fig
)
```

## Effect of density

### Juvenile growth rate

```{r growthrate, message=F, warning=F}
f_GrowthRate <- function(data){
 
  df_GrowthRate <- data.frame() 
 
  for (i in unique(data$ID_cosm)){

    data_i <- subset(data, ID_cosm == i) 
    Nb_vdt_i <- unique(subset(data_i, t==0)$Nb_vdt)
    Food_i <- unique(subset(data_i, t==0)$Food)
    Nb_rep_i <- unique(subset(data_i, t==0)$Nb_rep)
    Lot_i <- unique(subset(data_i, t==0)$Lot)
    Condition_i <- unique(subset(data_i, t==0)$Condition)
   
    if (length(na.omit(data_i$L))<2) {
      a.Est <- NA
      
    }else if(length(na.omit(data_i$L))==2){ 
     
      a.Est <- (subset(data_i, !t==0)$L - subset(data_i, t==0)$L)/subset(data_i, !t==0)$t # (L(t=t)-L(t=0))/t
     
    }else{
      lm_i <- lm(L~t, data=data_i)
      a.Est <- lm_i$coefficients[2]
    }
   
    df_GrowthRate_i <- data.frame(
      ID_cosm = i,
      Nb_vdt = Nb_vdt_i,
      Food = Food_i,
      Nb_rep = Nb_rep_i,
      Lot = Lot_i,
      Condition = Condition_i,
      Growth_rate = a.Est
    )
    
    df_GrowthRate <- rbind(df_GrowthRate, df_GrowthRate_i)
  }
 
  return(df_GrowthRate) 
}

df_dens_juv_mean <- df_dens_growth |> 
  filter(Status == "J") |> 
  aggregate(Weight~Condition+Nb_rep+Nb_vdt+Food+Lot+t, FUN=mean) |> 
  mutate(
    ID_cosm = paste0(Condition, Nb_rep),
    L = Weight^(1/3),
    Nb_vdt_f = as.factor(Nb_vdt)
  )

df_GrowthRate <- f_GrowthRate(df_dens_juv_mean) |> 
  mutate(
    Nb_vdt_f = as.factor(Nb_vdt),
    Food_f = as.factor(Food)
  )

df_GrowthRate_mean <- df_GrowthRate |> 
  aggregate(Growth_rate~Condition, FUN=mean)

```

```{r, warning = F, message = F}
#| fig-cap: Growth rates of earthworms per condition
#| label: fig-densgrowthratedens
#| fig-height: 6
#| fig-width: 8

p <- ggplot(
  data = df_GrowthRate,
  aes(
    x = Condition,
    y = Growth_rate
  )
)+
  geom_boxplot(
    alpha=0,
    color=Nord_polar[4],
    fill=Nord_frost[4]
  )+
  geom_dotplot(
    binaxis='y',
    stackdir='center',
    alpha=0.5,
    color=Nord_frost[4],
    fill=Nord_frost[4]
  )+
  labs(
    x = "Density (# earthworm / cosm)",
    y = expression(paste("Growth rate (",mg^{1/3},"/day)"))
  )+
  theme_minimal()
p
```

```{r GRsummary}
#| tbl-cap: Growth rate per condition

df_GrowthRate_mean <- df_GrowthRate |> 
  aggregate(Growth_rate~Condition, FUN=mean)
df_GrowthRate_mean |> datatable(
  options = list(
    dom = 't',
    pageLength = nrow(df_GrowthRate_mean),
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
    )
  ),
  class = "hover"
)
```

Is there an effect of density on juvenile growth rate ?

```{r statDGR}
anova_model <- aov(Growth_rate ~ Condition, data = subset(df_GrowthRate, Condition != "D2b"))
summary(anova_model)
# Normalité des résidus
shapiro.test(residuals(anova_model))
# Homogénéité des variances
bartlett.test(Growth_rate ~ Condition, data = df_GrowthRate)
TukeyHSD(anova_model)
```

```{r}
df_dens_growth_dens <- df_dens_growth |> 
  filter(!(Condition %in% c("D2b")))
df_dens_growth_dens_mean_rep <- df_dens_growth_mean_rep |> 
  filter(!(Condition %in% c("D2b")))

pal_dens_dens <- c("#B48EAD", "#5E81AC", "#88C0D0", "#8FBCBB")
```

```{r, warning = F, message = F}
#| fig-cap: Growth trajectories of earthworms per conditions.
#| label: fig-densgrowthtraj21
#| fig-height: 8
#| fig-width: 8


xmax <- 170
ymax <- 2000

p <- ggplot()+
  geom_point(
    data = df_dens_growth_dens,
    aes(
      x=t,
      y=Weight,
      color=as.factor(Condition),
      group=as.factor(ID)
    ),
    alpha=0.5,
    size=2
  )+
  geom_point(
    data = df_dens_growth_dens_mean_rep,
    aes(
      x=t,
      y=Weight,
      color=as.factor(Condition)
    ),
    size=2
  )+
  geom_line(
    data = df_dens_growth_dens_mean_rep,
    aes(
      x=t,
      y=Weight,
      color=as.factor(Condition)
    )
  )+
  scale_color_manual(
    name="Replicate\nnumber",
    values=pal_dens_dens
    )+
  facet_grid(cols=vars(Condition), rows=vars(Nb_rep))+
  scale_x_continuous(
    limits = c(0, xmax),       
    breaks = seq(0, xmax, by = 28),
    minor_breaks = seq(0, xmax, by = 14) 
  ) +
  ylim(0, ymax)+
  labs(
    x="Time (days)",
    y = "Weight (mg)"
  )+
  theme_minimal()
p
```

### Cocoon production

```{r, warning = F, message = F}
#| fig-cap: Reproduction of earthworms per conditions.
#| label: fig-densegg
#| fig-height: 8
#| fig-width: 8

xmax <- 170
ymax <- 25

p <- ggplot()+
  geom_point(
    data = subset(df_dens_repro, Condition != "D2b"),
    aes(
      x=t,
      y=Reproduction,
      color=as.factor(Condition)
    ),
    size=2
  )+
  geom_line(
    data = subset(df_dens_repro, Condition != "D2b"),
    aes(
      x=t,
      y=Reproduction,
      color=as.factor(Condition)
    )
  )+
  scale_color_manual(
    name="Replicate\nnumber",
    values=pal_dens
    )+
  facet_grid(cols=vars(Condition), rows=vars(Nb_rep))+
  scale_x_continuous(
    limits = c(0, xmax),       
    breaks = seq(0, xmax, by = 28),
    minor_breaks = seq(0, xmax, by = 14) 
  ) +
  ylim(0, ymax)+
  labs(
    x="Time (days)",
    y = "Cumulated reproduction (#/ind)"
  )+
  theme_minimal()
p
```

```{r}
#| tbl-cap: Reproduction rate per condition

df_dens_repro_clean <- df_dens_repro |>
  filter(!(Condition %in% c("D1"))) |>
  arrange(ID, t) |>
  group_by(ID) |>
  mutate(
    start_repro = min(t[Nb_cocoons > 0], na.rm = TRUE)
  ) |>
  ungroup() |>
  filter(is.finite(start_repro)) |>
  arrange(ID, t) |>
  group_by(ID) |>
  mutate(
    dt = t - lag(t)
  ) |>
  ungroup()  |>
  mutate(
    Repro_rate = Nb_cocoons / (Nb_vdt * dt)
  ) |> 
  filter(Repro_rate!=0) |> 
  group_by(ID) |> 
  slice(-1) |> # Remove first repro rate bc reproduction started some unknow time during the previous 28 days.
  summarise(
    Repro_rate = mean(Repro_rate, na.rm = TRUE),
    Condition = first(Condition),
    Food = first(Food),
    Nb_vdt = first(Nb_vdt),
    .groups = "drop"
  ) |> 
  ungroup()


df_dens_reprorate_mean <- df_dens_repro_clean %>%
  aggregate(Repro_rate~Condition, FUN=mean)

df_dens_reprorate_mean  |> 
  mutate(Repro_rate = round(Repro_rate, 2)) |> 
  datatable(
  options = list(
    dom = 't',
    pageLength = nrow(df_dens_reprorate_mean),
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
    )
  ),
  class = "hover"
)
```

Is there an effect of density on earthworm reproduction ?

```{r statDR}
model <- glm(
  Repro_rate ~ Condition,
  family = Gamma(link = "log"),
  data = df_dens_repro_clean |> filter(!(Condition == "D2b") & !is.na(Repro_rate))
)
summary(model)

emmeans(model, pairwise ~ Condition, adjust = "tukey")
```

## Effect of food

### Juvenile growth rate

```{r, message=F, warning=F}
df_GrowthRate_food <- subset(df_GrowthRate, Nb_vdt == 2)
```

```{r, warning = F, message = F}
#| fig-cap: Growth rates of earthworms per food condition (density = 2).
#| label: fig-densgrowthratefood
#| fig-height: 4
#| fig-width: 6


p <- ggplot(
  data = df_GrowthRate_food,
  aes(
    x = Food_f,
    y = Growth_rate
  )
)+
  geom_boxplot(
    alpha=0,
    color=Nord_polar[4],
    fill=Nord_frost[4]
  )+
  geom_dotplot(
    binaxis='y',
    stackdir='center',
    alpha=0.5,
    color=Nord_frost[4],
    fill=Nord_frost[4]
  )+
  labs(
    x = "Horse dung quantity given per earthworm every 14 days",
    y = expression(paste("Growth rate (",mg^{1/3},"/day)"))
  )+
  theme_minimal()
p
```

Is there an effect of food on growth rate ?

```{r}
shapiro.test(df_GrowthRate_food$Growth_rate) # Si pas signif alors donnee pas inconsistentes avec une loi normale
var.test(df_GrowthRate_food$Growth_rate~df_GrowthRate_food$Food) # Si pas signif alors variance égale
t.test(df_GrowthRate_food$Growth_rate~df_GrowthRate_food$Food, alternative = "two.sided", var.equal=T) # si signif différence signif entre les deux groupes
```

### Cocoon production

```{r, message=F, warning=F}
df_dens_repro_clean_food <- subset(df_dens_repro_clean, Nb_vdt == 2) |> 
  mutate(Food_f = as.factor(Food))
```

```{r, warning = F, message = F}
#| fig-cap: Reproduction rates of earthworms per food condition (density = 2).
#| label: fig-densreproratefood
#| fig-height: 4
#| fig-width: 6

p <- ggplot(
  data = df_dens_repro_clean_food,
  aes(
    x = Food_f,
    y = Repro_rate
  )
)+
  geom_boxplot(
    alpha=0,
    color=Nord_polar[4],
    fill=Nord_frost[4]
  )+
  geom_dotplot(
    binaxis='y',
    stackdir='center',
    alpha=0.5,
    color=Nord_frost[4],
    fill=Nord_frost[4]
  )+
  labs(
    x = "Horse dung quantity given per earthworm every 14 days",
    y = expression(paste("Reproduction rate (#/ind/day)"))
  )+
  theme_minimal()
p
```

## Summary figures

```{r}
#| fig-cap: Growth curves and cumulative reproduction of earthworms across density treatments (cosm densities of 1, 2, 5, and 7 individuals). Small points correspond to the mean weight of earthworm at the replicate level, bigger plain squares correspond to the mean weight at the condition level.
#| label: fig-summarydens
#| fig-height: 6
#| fig-width: 8


t_max <- max((df_dens_growth_mean_rep |> filter(!(Condition == "D2b")))$t)

p_G <- ggplot()+
  geom_point(
    data = df_dens_growth_mean_rep |> filter(!(Condition == "D2b")),
    aes(
      x = t,
      y = Weight,
      color = Condition
    ),
    alpha = 0.5,
    size = 1.4
  )+
  geom_line(
    data = df_dens_growth_mean_cond |> filter(!(Condition == "D2b")),
    aes(
      x = t,
      y = Weight,
      color = Condition
    )
  )+
  geom_point(
    data = df_dens_growth_mean_cond |> filter(!(Condition == "D2b")),
    aes(
      x = t,
      y = Weight,
      color = Condition
    ),
    size = 2,
    shape = shape_EPX
  )+
  facet_wrap(
    ~ Condition, ncol=4
  )+
  scale_x_continuous(     
    breaks = seq(0, t_max, by = 28),        
    minor_breaks = seq(0, t_max, by = 14)
  ) +
  labs(x = "Time (days)", y = "Weight (mg)")+
  scale_color_manual(values = pal_dens[-3])+
  theme_minimal()+
  theme(legend.position = "none")

p_R <- ggplot()+
  geom_point(
    data = df_dens_repro |> filter(!(Condition == "D2b")),
    aes(
      x = t,
      y = Reproduction,
      color = Condition
    ),
    alpha = 0.5,
    size = 1.4
  )+
  geom_line(
    data = df_dens_repro_mean_cond |> filter(!(Condition == "D2b")),
    aes(
      x = t,
      y = Reproduction,
      color = Condition
    )
  )+
  geom_point(
    data = df_dens_repro_mean_cond |> filter(!(Condition == "D2b")),
    aes(
      x = t,
      y = Reproduction,
      color = Condition
    ),
    size = 2,
    shape = shape_EPX
  )+
  facet_wrap(
    ~ Condition, ncol=4
  )+
  scale_x_continuous(     
    breaks = seq(0, t_max, by = 28),        
    minor_breaks = seq(0, t_max, by = 14)
  ) +
  labs(x = "Time (days)", y = "Cumulated reproduction (#)")+
  scale_color_manual(values = pal_dens[-3])+
  theme_minimal()+
  theme(
    legend.position = "none",
    strip.text = element_blank()
    )

p <- p_G / p_R
p
```

```{r, include=FALSE}
ggsave(
  filename = "DENS_summary_1.png",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
```

```{r}
#| fig-cap: Comparison of growth curves and cumulative reproduction of earthworms under standard (D2, grey) and increased food supply (D2b, blue) at constant density. Small points correspond to the mean weight of earthworm at the replicate level, bigger plain squares correspond to the mean weight at the condition level.
#| label: fig-summaryfood
#| fig-height: 3
#| fig-width: 6

t_max <- max((df_dens_growth_mean_rep |> filter((Condition %in% c("D2","D2b"))))$t)
t_D2b <- 112

p_G <- ggplot()+
  geom_point(
    data = df_dens_growth_mean_rep |> filter((Condition %in% c("D2","D2b"))),
    aes(
      x = t,
      y = Weight,
      color = Condition
    ),
    alpha = 0.6,
    size = 1.4
  )+
  geom_line(
    data = df_dens_growth_mean_cond |> filter((Condition %in% c("D2","D2b"))&(!(Condition == "D2b" & t > t_D2b))),
    aes(
      x = t,
      y = Weight,
      color = Condition
    )
  )+
  geom_point(
    data = df_dens_growth_mean_cond |> filter((Condition %in% c("D2","D2b"))&(!(Condition == "D2b" & t > t_D2b))),
    aes(
      x = t,
      y = Weight,
      color = Condition
    ),
    size = 2,
    shape = shape_EPX
  )+
  scale_x_continuous(     
    breaks = seq(0, t_max, by = 28),        
    minor_breaks = seq(0, t_max, by = 14)
  ) +
  labs(x = "Time (days)", y = "Weight (mg)")+
  scale_color_manual(values = c(Nord_snow[1], pal_dens[3]))+
  theme_minimal()+
  theme(legend.position = "none")

p_R <- ggplot()+
  geom_point(
    data = df_dens_repro |> filter((Condition %in% c("D2","D2b"))),
    aes(
      x = t,
      y = Reproduction,
      color = Condition
    ),
    alpha = 0.6,
    size = 1.4
  )+
  geom_line(
    data = df_dens_repro_mean_cond |> filter((Condition %in% c("D2","D2b"))&(!(Condition == "D2b" & t > t_D2b))),
    aes(
      x = t,
      y = Reproduction,
      color = Condition
    )
  )+
  geom_point(
    data = df_dens_repro_mean_cond |> filter((Condition %in% c("D2","D2b"))&(!(Condition == "D2b" & t > t_D2b))),
    aes(
      x = t,
      y = Reproduction,
      color = Condition
    ),
    size = 2,
    shape = shape_EPX
  )+
  scale_x_continuous(     
    breaks = seq(0, t_max, by = 28),        
    minor_breaks = seq(0, t_max, by = 14)
  ) +
  labs(x = "Time (days)", y = "Cumulated reproduction (#)")+
  scale_color_manual(values = c(Nord_snow[1], pal_dens[3]))+
  theme_minimal()+
  theme(legend.position = "none")

p <- p_G + p_R
p
```

```{r, include=FALSE}
ggsave(
  filename = "DENS_summary_2.png",
  plot = p,
  width = 6, height = 3,
  path = path_fig
)
```
