```{r, include = F}
library(here)
source(file=here::here("functions/fun.R"))
f_load_libraries_colors()
```

# Model formulation

## Classication DEB standard formulation

**Reserve energy dynamic**

$$
\frac{\mathrm{d}E}{\mathrm d t} = \frac{\{\dot p_{Am}\}_t}{L} \ \left(f - \frac{E\ \nu_t}{\{\dot p_{Am}\}_t}\right)
$$

With :
- $E$ : Energy in the reserve ($J$)
- $\nu_t$ : Energy conductance at temperature $T_{exp}$  ($cm.d^{-1}$)

**Growth**

$$
\begin{aligned}
\frac{\mathrm d L}{\mathrm d t} &= \frac{\nu_t}{3\ (\frac{E}{E_m} + g)} \left(\frac{E}{E_m} - \frac{L}{L_m}\right) \\ \\
K_m &= \frac{[\dot p_{M,t}]}{[E_G]} \\
E_m &= \frac{\{\dot p_{Am}\}_t}{\nu_t}\\
g &= \frac{[E_G]}{\kappa_{\text{real}}\ E_m}\\
L_m &= \frac{\nu_t}{K_m\ g}
\end{aligned}
$$

With :
- $L$ : Structural volumetric length ($cm$)
- $[\dot p_{M,t}]$ : Volume-specific maintenance rate ($J.d^{-1}.cm^{-3}$)
- $[E_G]$ : Volume-specific cost for structure ($J.cm^{-3}$)

$$
W_W = L^3 \left(1+\frac{E}{E_m}w\right)
$$

With :
- $W_W$ : Wet weight of the earthworm ($g$)
- $w$ : Contribution of reserve to body weight ($g.cm^{-3}$)

**Maturity and reproduction**

$$
\dot p_C = \frac{g\ E}{g + \frac{E}{E_m}} (\nu_t\ L^2 + K_m\ L^3)
$$

With : 
- $\dot p_C$ :  Mobilized energy flux from reserve ($J.d^{-1}$)

$$
\dot p_R = (1-\kappa_{\text{real}})\ \dot p_C - \dot k_{J,t}\ E_h
$$

With :
- $\dot p_R$ : Allocated energy flux to reproduction ($J.d^{-1}$)
- $\dot k_{J,t}$ : Maturity maintenance rate ($d^{-1}$)

$$
\frac{\mathrm{d}E_H}{\mathrm{d}t}= 
\begin{cases}
E_H \leq E_H^p,\ & \dot{p}_R\\
E_H > E_H^p,\ & 0
\end{cases}
$$

With :
- $E_h$ : Maturity ($J$)
- $E_h^p$ : Maturity at puberty ($J$)

$$
\frac{\mathrm{d}R}{\mathrm{d}t}= 
\begin{cases}
E_H \leq E_H^p,\ & 0 \\
E_H > E_H^p,\ & \kappa_R\ \frac{\dot{p}_R}{E_{0}}
\end{cases}
$$

With :
- $R$ : Cumulated reproduction (#)
- $\kappa_R$ : Reproduction efficiency (-)
- $E_0$ : Energy cost for an egg ($J$)

**Effect of temperature on rates**

$$
\begin{aligned}
s_A &= \exp(\frac{T_A}{T_{ref}-\frac{T_A}{T_{exp}+273.15}})\\
s_{rH} &= \frac{1 + \exp (\frac{T_A^H}{T^H}-\frac{T_A^H}{T_{ref}+ 273.15})}{1 + \exp (\frac{T_A^H}{T^H}-\frac{T_A^H}{T_{exp}+273.15})}\\
T_c &= s_A (T_{exp}+273.15 \geq T_{ref}) s_{rH} + (T_{exp} + 273.15 < T_{ref})\\ \\

\{\dot p_{Am}\}_t &= \{\dot p_{Am}\}\ T_c\\
[\dot p_{M,t}] &= [\dot p_{M}]\ T_c \\
\nu_t &= \nu \ T_c \\
\dot k_{J,t} &= \dot k_{J} \ T_c
\end{aligned}
$$

## Energy assimilation in the case of earthworms

$$
\dot Q_{f,max} = \frac{\{\dot p_{Am}\}_t\ L^2}{\kappa_X}
$$

With : 
- $\dot Q_{f,max}$ :  Maximal rate of energy ingested by the earthworm ($J.d^{-1}$)
- $\{\dot p_{Am}\}_t$ : Surface-area-specific maximum assimilation rate at temperature $T_{exp}$ ($J.d^{-1}.cm^{-2}$)
- $L$ : Structural volumetric length ($cm$)
- $\kappa_X$ : Fraction of food energy fixed in reserve (digestion efficiency) (-)

$$
\begin{aligned}
\dot Q_{f,soil} &= [\dot{F}_m]\ L^2 \times (\mu_{OM}\ r_{OM}^{clx, horse}\ \frac{OM_{soil}}{Nb_{ind}}) \\
\dot Q_{f,horse} &= [\dot{F}_m]\ L^2 \times (\mu_{OM}\ \frac{OM_{horse}}{Nb_{ind}}) \\
\dot Q_{f,tot} &= \dot Q_{f,horse} + \dot Q_{f,soil}
\end{aligned}
$$

- $\dot Q_{f,soil}$ :  Rate of energy ingested from the organic matter in the soil by the earthworm ($J.d^{-1}$)
- $\dot Q_{f,horse}$ :  Rate of energy ingested from the organic matter in the horse dung by the earthworm ($J.d^{-1}$)
- $\dot Q_{f,tot}$ :  Rate of energy ingested from organic matter by the earthworm ($J.d^{-1}$)
- $[\dot{F}_m]$ : Maximum volume-specific searching rate ($g.d^{-1}.cm^{-3}$)
- $W_w$ : Wet weight of the earthworm ($g$)
- $\mu_{OM}$ : Horse dung organic matter energy content ($J.g^{-1}$)
- $r_{OM}^{clx, horse}$ : Ratio between soil organic matter energy content and horse dung organic matter energy content (-)
- $OM_{soil}$ : Organic matter from soil in a cosm (g)
- $OM_{horse}$ : Organic matter from horse dung in a cosm (g)
- $Nb_{ind}$ : Number of individual in the cosm (#)

$$
\begin{aligned}
\dot{OM}_{out}^{soil} &= \frac{\dot Q_{f,soil}}{\mu_{OM}\ r_{OM}^{clx, horse}}\ Nb_{ind} \\
\dot{OM}_{out}^{horse} &= \frac{\dot Q_{f,horse}}{\mu_{OM}} \ Nb_{ind}
\end{aligned}
$$

With :
- $\dot{OM}_{out}^{soil}$ : Rate of consumption of soil organic matter by all earthworms of the cosm ($g.d^{-1}$)
- $\dot{OM}_{out}^{horse}$ : Rate of consumption of horse dung organic matter by all earthworms of the cosm ($g.d^{-1}$)

$$
f=\frac{X}{X+1}, \ \ \text{with }\ X = \frac{\dot Q_{f,tot}}{\frac 1 2 \dot Q_{f,max}} 
$$

With : 
- $f$ : Functional response to organic matter (-)

## Different model versions tested

### Kappa

The standard DEB model supposes a fixed $\kappa$ throughout the organism life (model F). But because of the observations of a switch in growth when earthworms are adult and able to reproduce with another individual, we tested a switch in energy allocation when earthworms are adults and not alone in a cosm, and therefore able to reproduce (model S). 

$$
\begin{aligned}
&{\text{Model F: }}\ \kappa_{\text{real}} = \kappa \\
&{\text{Model S: }}\ \kappa_{real} = 
\begin{cases}
E_h < E_h^p, & \kappa  & (\text{Juveniles})\\
E_h \geq E_h^p\ \&\ Nb_{ind} = 1, & \kappa & (\text{Adult alone})\\
E_h \geq E_h^p\ \&\ Nb_{ind} > 1, & 1-\kappa & (\text{Grouped adults})
\end{cases}
\end{aligned}
$$

### Soil ingestion

Ingestion is often considered to be proportional to the structural surface of the individual (L$^2$, model L) but we tested the possibility of it being proportional to structural volume and therefore to weight (L$^3$, model W). 

$$
\begin{aligned}
\text{Model L:}\\
\dot Q_{f,soil} &= [\dot{F}_m]\ L^2 \times (\mu_{OM}\ r_{OM}^{clx, horse}\ \frac{OM_{soil}}{Nb_{ind}}) \\
\dot Q_{f,horse} &= [\dot{F}_m]\ L^2 \times (\mu_{OM}\ \frac{OM_{horse}}{Nb_{ind}}) \\ \\
\text{Model W:}\\
\dot Q_{f,soil} &= [\dot{F}_m]\ L^3 \times (\mu_{OM}\ r_{OM}^{clx, horse}\ \frac{OM_{soil}}{Nb_{ind}}) \\
\dot Q_{f,horse} &= [\dot{F}_m]\ L^3 \times (\mu_{OM}\ \frac{OM_{horse}}{Nb_{ind}})
\end{aligned}
$$

### Functional response to organic matter

**Hyperbolic function (Model Y)**

$$
f=\frac{X}{X+1}, \ \ \text{with }\ X = \frac{\dot Q_{f,tot}}{\frac 1 2 \dot Q_{f,max}} 
$$

**Hill function (Model I)**

$$
f=\frac{X^{\text{Slope}}}{0.5^{\text{Slope}}+X^{\text{Slope}}}, \ \ \text{with }\ X = \frac{\dot Q_{f,tot}}{\dot Q_{f,max}} 
$$

```{r}
Slope <- 2
x_hy <- seq(0,1,0.01)
x_hi <- seq(0,1,0.01)

f_hyperbolic <- function(x){
  res <- 2*x/(1+2*x)
  return(res)
}

f_hill <- function(x, Slope){
  res <- x^(Slope)/(0.5^(Slope) + x^(Slope))
  return(res)
}

y_hy <- f_hyperbolic(x_hy)
y_hi <- f_hill(x_hi, Slope)

df <- data.frame(
  x = c(x_hy, x_hi),
  y = c(y_hy, y_hi),
  type = c(rep("Hyperbolic", length(x_hy)), rep("Hill", length(x_hi)))
)

p <- ggplot(
  data = df,
  aes(
    x=x,
    y=y,
    color = type
  )
)+
  geom_line()+
  labs(x = "Qf/Qfmax", y = "f")+
  scale_color_manual(values = c(Nord_frost[2], Nord_frost[4]))+
  theme_minimal()
p

```


