```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# Model comparison

## Data importation

```{r expfit, message=F, warning=F}

path_fig <- here::here("fig/DEB_Models")

path_A_FLYw <- here::here("mod/FINAL/A_DEB_FLYw")
path_B_FLYe <- here::here("mod/FINAL/B_DEB_FLYe")
path_C_AWYe <- here::here("mod/FINAL/C_DEB_AWYe")
path_D_AWKe <- here::here("mod/FINAL/D_DEB_AWKe")
path_E_ALYe <- here::here("mod/FINAL/E_DEB_ALYe")
path_F_ALKe <- here::here("mod/FINAL/F_DEB_ALKe")

l_Experiments_fit <- c(
  "Bart2019_XP1_1",  
  "Bart2019_XP1_2",  
  #"Bart2019_XP2",
  "Bart2019_XP3",   
  "Bart2019_XP4_1",
  "Bart2019_XP4_2",
  "Bart2019_XP5", 
  "Bart2020",
  #"Gollot2026_lufa"
  "Gollot2026_dens_D1",
  "Gollot2026_dens_D2",
  "Gollot2026_dens_D2b",
  "Gollot2026_dens_D5",
  "Gollot2026_dens_D7"
  )

Adults_alone <- FALSE

df_data_fit <- f_import_data_DEB(l_Experiments_fit, Adults_alone)

Experiments_carac <- f_get_experiments()
l_Experiments_tot <- Experiments_carac$l_Experiments_tot
l_carac <- Experiments_carac$l_carac
df_carc_exp <- Experiments_carac$df_carc_exp

```

## Model fits

```{r writeIn, message=F, warning=F}
NbIter <- 100000
OM_diff <- TRUE
RTOL <- 1e-7
ATOL <- 1e-6

######### A FLYw ###############################################################

seeds <- c(C1 = 3303, C2 = 3666, C3 = 2212)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kap,          Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (wE,           LogUniform,              1,      1000);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_A_FLYw, l_Experiments, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### B FLYe ###############################################################

seeds <- c(C1 = 3313, C2 = 6666, C3 = 1212)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kap,          Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,    0.000000001,      0.1);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_B_FLYe, l_Experiments, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### C AWYe ###############################################################

seeds <- c(C1 = 3333, C2 = 6669, C3 = 1210)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_C_AWYe, l_Experiments, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### D AWKe ###############################################################

seeds <- c(C1 = 3303, C2 = 6636, C3 = 2929)

text_priors <- '
Distrib (Fm,           LogUniform,         0.0001,      0.3);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (K,            Uniform,            0.0001,        1);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_D_AWKe, l_Experiments, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### E ALYe ###############################################################

seeds <- c(C1 = 3333, C2 = 7880, C3 = 1210)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_E_ALYe, l_Experiments, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### F ALKe ###############################################################

seeds <- c(C1 = 3330, C2 = 6646, C3 = 1212)

text_priors <- '
Distrib (Fm,           TruncNormal_cv,     0.1,      0.2,      0.0001,    0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (K,            Uniform,           0.00001,        2);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,    Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_F_ALKe, l_Experiments, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

```

## Estimates results

```{r getres, echo=F, message=F, warning=F}

######### A FLYw ###############################################################

MCMC_out_A_FLYw <- f_MCSim(path_A_FLYw)

NC_A_FLYw <- MCMC_out_A_FLYw$NC
Nb_param_A_FLYw <- MCMC_out_A_FLYw$Nb_param
Nb_experiment_A_FLYw <- MCMC_out_A_FLYw$Nb_experiment
Nb_iter_kept_A_FLYw <- MCMC_out_A_FLYw$Nb_iter_kept
N_iter_setpoint_A_FLYw <- MCMC_out_A_FLYw$N_iter_setpoint
L_parameters_A_FLYw <- unique(MCMC_out_A_FLYw$Priors$Nom)

LL_A_FLYw <- f_get_mode(MCMC_out$df_LnData$LnData)
n_A_FLYw <- length(na.omit(df_data$Weight)) + 
  length(na.omit(df_data$Reproduction))
k_A_FLYw <- Nb_param - 1 # On enlève le Sigma_W

BIC_A_FLYw <- -2*LL_A_FLYw+k_A_FLYw*log(n_A_FLYw)

Summary_res_A_FLYw <- 
  as.data.frame(MCMC_out_A_FLYw$Summary_res)[1:length(L_parameters_A_FLYw)] |> 
  mutate(Model = "A_FLYw")

######### B FLYe ###############################################################

MCMC_out_B_FLYe <- f_MCSim(path_B_FLYe)

NC_B_FLYe <- MCMC_out_B_FLYe$NC
Nb_param_B_FLYe <- MCMC_out_B_FLYe$Nb_param
Nb_experiment_B_FLYe <- MCMC_out_B_FLYe$Nb_experiment
Nb_iter_kept_B_FLYe <- MCMC_out_B_FLYe$Nb_iter_kept
N_iter_setpoint_B_FLYe <- MCMC_out_B_FLYe$N_iter_setpoint
L_parameters_B_FLYe <- unique(MCMC_out_B_FLYe$Priors$Nom)

LL_B_FLYe <- f_get_mode(MCMC_out$df_LnData$LnData)
n_B_FLYe <- length(na.omit(df_data$Weight)) + 
  length(na.omit(df_data$Reproduction))
k_B_FLYe <- Nb_param - 1 # On enlève le Sigma_W

BIC_B_FLYe <- -2*LL_B_FLYe+k_B_FLYe*log(n_B_FLYe)

Summary_res_B_FLYe <- 
  as.data.frame(MCMC_out_B_FLYe$Summary_res)[1:length(L_parameters_B_FLYe)] |> 
  mutate(Model = "B_FLYe")

######### C AWYe ###############################################################

MCMC_out_C_AWYe <- f_MCSim(path_C_AWYe)

NC_C_AWYe <- MCMC_out_C_AWYe$NC
Nb_param_C_AWYe <- MCMC_out_C_AWYe$Nb_param
Nb_experiment_C_AWYe <- MCMC_out_C_AWYe$Nb_experiment
Nb_iter_kept_C_AWYe <- MCMC_out_C_AWYe$Nb_iter_kept
N_iter_setpoint_C_AWYe <- MCMC_out_C_AWYe$N_iter_setpoint
L_parameters_C_AWYe <- unique(MCMC_out_C_AWYe$Priors$Nom)

LL_C_AWYe <- f_get_mode(MCMC_out$df_LnData$LnData)
n_C_AWYe <- length(na.omit(df_data$Weight)) + 
  length(na.omit(df_data$Reproduction))
k_C_AWYe <- Nb_param - 1 # On enlève le Sigma_W

BIC_C_AWYe <- -2*LL_C_AWYe+k_C_AWYe*log(n_C_AWYe)

Summary_res_C_AWYe <- 
  as.data.frame(MCMC_out_C_AWYe$Summary_res)[1:length(L_parameters_C_AWYe)] |> 
  mutate(Model = "C_AWYe")

######### D AWKe ###############################################################

MCMC_out_D_AWKe <- f_MCSim(path_D_AWKe)

NC_D_AWKe <- MCMC_out_D_AWKe$NC
Nb_param_D_AWKe <- MCMC_out_D_AWKe$Nb_param
Nb_experiment_D_AWKe <- MCMC_out_D_AWKe$Nb_experiment
Nb_iter_kept_D_AWKe <- MCMC_out_D_AWKe$Nb_iter_kept
N_iter_setpoint_D_AWKe <- MCMC_out_D_AWKe$N_iter_setpoint
L_parameters_D_AWKe <- unique(MCMC_out_D_AWKe$Priors$Nom)

LL_D_AWKe <- f_get_mode(MCMC_out$df_LnData$LnData)
n_D_AWKe <- length(na.omit(df_data$Weight)) + 
  length(na.omit(df_data$Reproduction))
k_D_AWKe <- Nb_param - 1 # On enlève le Sigma_W

BIC_D_AWKe <- -2*LL_D_AWKe+k_D_AWKe*log(n_D_AWKe)

Summary_res_D_AWKe <- 
  as.data.frame(MCMC_out_D_AWKe$Summary_res)[1:length(L_parameters_D_AWKe)] |> 
  mutate(Model = "D_AWKe")

######### E ALYe ###############################################################

MCMC_out_E_ALYe <- f_MCSim(path_E_ALYe)

NC_E_ALYe <- MCMC_out_E_ALYe$NC
Nb_param_E_ALYe <- MCMC_out_E_ALYe$Nb_param
Nb_experiment_E_ALYe <- MCMC_out_E_ALYe$Nb_experiment
Nb_iter_kept_E_ALYe <- MCMC_out_E_ALYe$Nb_iter_kept
N_iter_setpoint_E_ALYe <- MCMC_out_E_ALYe$N_iter_setpoint
L_parameters_E_ALYe <- unique(MCMC_out_E_ALYe$Priors$Nom)

LL_E_ALYe <- f_get_mode(MCMC_out$df_LnData$LnData)
n_E_ALYe <- length(na.omit(df_data$Weight)) + 
  length(na.omit(df_data$Reproduction))
k_E_ALYe <- Nb_param - 1 # On enlève le Sigma_W

BIC_E_ALYe <- -2*LL_E_ALYe+k_E_ALYe*log(n_E_ALYe)

Summary_res_E_ALYe <- 
  as.data.frame(MCMC_out_E_ALYe$Summary_res)[1:length(L_parameters_E_ALYe)] |> 
  mutate(Model = "E_ALYe")

######### F ALKe ###############################################################

MCMC_out_F_ALKe <- f_MCSim(path_F_ALKe)

NC_F_ALKe <- MCMC_out_F_ALKe$NC
Nb_param_F_ALKe <- MCMC_out_F_ALKe$Nb_param
Nb_experiment_F_ALKe <- MCMC_out_F_ALKe$Nb_experiment
Nb_iter_kept_F_ALKe <- MCMC_out_F_ALKe$Nb_iter_kept
N_iter_setpoint_F_ALKe <- MCMC_out_F_ALKe$N_iter_setpoint
L_parameters_F_ALKe <- unique(MCMC_out_F_ALKe$Priors$Nom)

LL_F_ALKe <- f_get_mode(MCMC_out$df_LnData$LnData)
n_F_ALKe <- length(na.omit(df_data$Weight)) + length(na.omit(df_data$Reproduction))
k_F_ALKe <- Nb_param - 1 # On enlève le Sigma_W

BIC_F_ALKe <- -2*LL_F_ALKe+k_F_ALKe*log(n_F_ALKe)

Summary_res_F_ALKe <- 
  as.data.frame(MCMC_out_F_ALKe$Summary_res)[1:length(L_parameters_F_ALKe)] |> 
  mutate(Model = "F_ALKe")

```

```{r resall}
#| tbl-cap: Estimation results from all models. 

param_order <- c(
  "pAm", "r_pAm_pM", "Fm", "rOM_ClxHorse", "K", "v", "kap", "kapJ", "kapA", "tau",
  "Ehp", "E_coc", "dv", "de", "wE", "Sigma_W"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = str_c(
        round(Result_mode, 3),
        " [", round(`2.5%`, 3),
        " ; ", round(`97.5%`, 3), "]"
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_models %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  )

df_result

```

## Chains

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_A_FLYw
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_A_FLYw$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsA_FLYw, include = F}
ggsave(
  filename="A_FLYw_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_B_FLYe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_B_FLYe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsB_FLYe, include = F}
ggsave(
  filename="B_FLYe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_AWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_C_AWYe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_C_AWYe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC_AWYe, include = F}
ggsave(
  filename="C_AWYe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_AWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_D_AWKe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_D_AWKe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsD_AWKe, include = F}
ggsave(
  filename="D_AWKe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## E_ALYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_E_ALYe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_E_ALYe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsE_ALYe, include = F}
ggsave(
  filename="E_ALYe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## F_ALKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_F_ALKe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_F_ALKe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsF_ALKe, include = F}
ggsave(
  filename="F_ALKe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

## Likelihoods

::: panel-tabset
## A_FLYw

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_A_FLYw
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_A_FLYw$df_LnPost_start |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_A_FLYw$df_LnPost |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_FLYw$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_A_FLYw$df_Devc |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_FLYw$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r savechainsA_FLYw, include = F}
ggsave(
  filename="A_FLYw_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_FLYe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_B_FLYe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_B_FLYe$df_LnPost_start |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_B_FLYe$df_LnPost |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_B_FLYe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_B_FLYe$df_Devc |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_B_FLYe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r savechainsB_FLYe, include = F}
ggsave(
  filename="B_FLYe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_AWYe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_C_AWYe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_C_AWYe$df_LnPost_start |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_C_AWYe$df_LnPost |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_C_AWYe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_C_AWYe$df_Devc |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_C_AWYe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r savechainsC_AWYe, include = F}
ggsave(
  filename="C_AWYe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_AWKe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_D_AWKe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_D_AWKe$df_LnPost_start |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_D_AWKe$df_LnPost |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_D_AWKe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_D_AWKe$df_Devc |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_D_AWKe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r savechainsD_AWKe, include = F}
ggsave(
  filename="D_AWKe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 8, 
  path=path_fig
  )
```

## E_ALYe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_E_ALYe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_E_ALYe$df_LnPost_start |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_E_ALYe$df_LnPost |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_E_ALYe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_E_ALYe$df_Devc |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_E_ALYe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r savechainsE_ALYe, include = F}
ggsave(
  filename="E_ALYe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 8, 
  path=path_fig
  )
```

## F_ALKe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_F_ALKe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_F_ALKe$df_LnPost_start |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_F_ALKe$df_LnPost |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_F_ALKe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_F_ALKe$df_Devc |> 
      filter(Iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_F_ALKe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r savechainsF_ALKe, include = F}
ggsave(
  filename="F_ALKe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

## Chains convergence

```{r, echo=F, message=F, warning=F}

####### A_FLYw #################################################################

# Large format per chain
mcmc_list_A_FLYw <- lapply(
  split(
    MCMC_out_A_FLYw$Chains, 
    MCMC_out_A_FLYw$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_A_FLYw <- as.mcmc.list(mcmc_list_A_FLYw)

####### B_FLYe #################################################################

# Large format per chain
mcmc_list_B_FLYe <- lapply(
  split(
    MCMC_out_B_FLYe$Chains, 
    MCMC_out_B_FLYe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_B_FLYe <- as.mcmc.list(mcmc_list_B_FLYe)

####### C_AWYe #################################################################

# Large format per chain
mcmc_list_C_AWYe <- lapply(
  split(
    MCMC_out_C_AWYe$Chains, 
    MCMC_out_C_AWYe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_C_AWYe <- as.mcmc.list(mcmc_list_C_AWYe)

####### D_AWKe #################################################################

# Large format per chain
mcmc_list_D_AWKe <- lapply(
  split(
    MCMC_out_D_AWKe$Chains, 
    MCMC_out_D_AWKe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_D_AWKe <- as.mcmc.list(mcmc_list_D_AWKe)

####### E_ALYe #################################################################

# Large format per chain
mcmc_list_E_ALYe <- lapply(
  split(
    MCMC_out_E_ALYe$Chains, 
    MCMC_out_E_ALYe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_E_ALYe <- as.mcmc.list(mcmc_list_E_ALYe)

####### F_ALKe #################################################################

# Large format per chain
mcmc_list_F_ALKe <- lapply(
  split(
    MCMC_out_F_ALKe$Chains, 
    MCMC_out_F_ALKe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_F_ALKe <- as.mcmc.list(mcmc_list_F_ALKe)

```

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_A_FLYw
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_A_FLYw,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_A_FLYw, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_A_FLYw
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_A_FLYw <- mcmc.list(
  lapply(mcmc_list_A_FLYw, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

png("fig/DEB_Models/A_FLYw_ipairs_plot.png", width = 3000, height = 3000, res = 300)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(
  as.matrix(mcmc_list_corr_A_FLYw), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

dev.off()
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_B_FLYe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_B_FLYe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_B_FLYe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_B_FLYe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_B_FLYe <- mcmc.list(
  lapply(mcmc_list_B_FLYe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

png("fig/DEB_Models/B_FLYe_ipairs_plot.png", width = 3000, height = 3000, res = 300)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(
  as.matrix(mcmc_list_corr_B_FLYe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

dev.off()
```

## C_AWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_C_AWYe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_C_AWYe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_C_AWYe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_C_AWYe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_C_AWYe <- mcmc.list(
  lapply(mcmc_list_C_AWYe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

png("fig/DEB_Models/C_AWYe_ipairs_plot.png", width = 3000, height = 3000, res = 300)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(
  as.matrix(mcmc_list_corr_C_AWYe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

dev.off()
```

## D_AWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_D_AWKe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_D_AWKe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_D_AWKe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_D_AWKe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_D_AWKe <- mcmc.list(
  lapply(mcmc_list_D_AWKe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

png("fig/DEB_Models/D_AWKe_ipairs_plot.png", width = 3000, height = 3000, res = 300)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(
  as.matrix(mcmc_list_corr_D_AWKe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

dev.off()
```

## E_ALYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_E_ALYe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_E_ALYe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_E_ALYe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_E_ALYe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_E_ALYe <- mcmc.list(
  lapply(mcmc_list_E_ALYe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

png("fig/DEB_Models/E_ALYe_ipairs_plot.png", width = 3000, height = 3000, res = 300)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(
  as.matrix(mcmc_list_corr_E_ALYe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

dev.off()
```

## F_ALKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_F_ALKe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_F_ALKe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_F_ALKe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_F_ALKe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_F_ALKe <- mcmc.list(
  lapply(mcmc_list_F_ALKe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

png("fig/DEB_Models/F_ALKe_ipairs_plot.png", width = 3000, height = 3000, res = 300)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(
  as.matrix(mcmc_list_corr_F_ALKe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

dev.off()
```
:::

## Posterior distributions

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_A_FLYw
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_A_FLYw$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_A_FLYw$Chains_plot <- MCMC_out_A_FLYw$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_A_FLYw$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostA_FLYw, include = F}
ggsave(
  filename="A_FLYw_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_B_FLYe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_B_FLYe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_B_FLYe$Chains_plot <- MCMC_out_B_FLYe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_B_FLYe$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostB_FLYe, include = F}
ggsave(
  filename="B_FLYe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_AWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_C_AWYe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_C_AWYe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_C_AWYe$Chains_plot <- MCMC_out_C_AWYe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_C_AWYe$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostC_AWYe, include = F}
ggsave(
  filename="C_AWYe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_AWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_D_AWKe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_D_AWKe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_D_AWKe$Chains_plot <- MCMC_out_D_AWKe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_D_AWKe$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostD_AWKe, include = F}
ggsave(
  filename="D_AWKe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## E_ALYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_E_ALYe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_E_ALYe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_E_ALYe$Chains_plot <- MCMC_out_E_ALYe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_E_ALYe$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostE_ALYe, include = F}
ggsave(
  filename="E_ALYe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## F_ALKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_F_ALKe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_F_ALKe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_F_ALKe$Chains_plot <- MCMC_out_F_ALKe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_F_ALKe$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostF_ALKe, include = F}
ggsave(
  filename="F_ALKe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

## Experiment simulations

```{r, message=F, warning=F}

l_Experiments <- c(
  "Bart2019_XP1_1",  
  "Bart2019_XP1_2",  
  "Bart2019_XP2",
  "Bart2019_XP3",   
  "Bart2019_XP4_1",
  "Bart2019_XP4_2",
  "Bart2019_XP5", 
  "Bart2020",
  #"Gollot2026_lufa"
  "Gollot2026_dens_D1",
  "Gollot2026_dens_D2",
  "Gollot2026_dens_D2b",
  "Gollot2026_dens_D5",
  "Gollot2026_dens_D7"
  )

Adults_alone <- TRUE

df_data <- f_import_data_DEB(l_Experiments, Adults_alone)







text_param <- Summary_res["Result_mode", , drop = FALSE] %>%
  t() %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  rename(val = 2) %>%
  mutate(
    param = gsub("\\.1\\.$|\\.1\\.", "", param),
    line  = glue("{param} = {val};")
  ) %>%
  pull(line) %>%
  paste(collapse = "\n")

Endpoints_print <- "Weight,
    Length_struct,
    Reproduction,
    Energy,
    Organic_matter,
    kapreal,
    freal,
    Qf_soil,
    Qf_horse,
    X"

step_sim <- 0.01

f_In_simulations(file_path, l_Experiments, Adults_alone, OM_diff, text_param, Endpoints_print, step_sim)
# ./mcsim.DEBcali DEB_sim_full.in


```

## Predicted vs. Observed

```{r}
l_param_name <- names(Summary_res) |>
  stringr::str_remove_all("\\.1\\.")

f_In_predobs(file_path, l_Experiments, Adults_alone, OM_diff, l_param_name)
```

```{bash, eval=F, execute=F}
for j in $(seq 1 12); do
./mcsim.DEBcali DEB_setpoint_predobs_${j}.in
done
```

```{r}

Nb_experiment <- 12

df_data_obs <- df_data |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

######## A_FLYw ###############################################################

df_pred_A_FLYw <- f_read_predobs(path_A_FLYw, Nb_experiment, df_data_obs)

df_pred_Weight_A_FLYw <- subset(df_pred_A_FLYw, Endpt == "Weight" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
df_pred_Reproduction_A_FLYw <- subset(df_pred_A_FLYw, Endpt == "Reproduction" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )

df_predobs_Reproduction_A_FLYw <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_A_FLYw, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_A_FLYw <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_A_FLYw, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## B_FLYe ###############################################################

df_pred_B_FLYe <- f_read_predobs(path_B_FLYe, Nb_experiment, df_data_obs)

df_pred_Weight_B_FLYe <- subset(df_pred_B_FLYe, Endpt == "Weight" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
df_pred_Reproduction_B_FLYe <- subset(df_pred_B_FLYe, Endpt == "Reproduction" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )

df_predobs_Reproduction_B_FLYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_B_FLYe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_B_FLYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_B_FLYe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## C_AWYe ###############################################################

df_pred_C_AWYe <- f_read_predobs(path_C_AWYe, Nb_experiment, df_data_obs)

df_pred_Weight_C_AWYe <- subset(df_pred_C_AWYe, Endpt == "Weight" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
df_pred_Reproduction_C_AWYe <- subset(df_pred_C_AWYe, Endpt == "Reproduction" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )

df_predobs_Reproduction_C_AWYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_C_AWYe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_C_AWYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_C_AWYe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## D_AWKe ###############################################################

df_pred_D_AWKe <- f_read_predobs(path_D_AWKe, Nb_experiment, df_data_obs)

df_pred_Weight_D_AWKe <- subset(df_pred_D_AWKe, Endpt == "Weight" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
df_pred_Reproduction_D_AWKe <- subset(df_pred_D_AWKe, Endpt == "Reproduction" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )

df_predobs_Reproduction_D_AWKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_D_AWKe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_D_AWKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_D_AWKe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## E_ALYe ###############################################################

df_pred_E_ALYe <- f_read_predobs(path_E_ALYe, Nb_experiment, df_data_obs)

df_pred_Weight_E_ALYe <- subset(df_pred_E_ALYe, Endpt == "Weight" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
df_pred_Reproduction_E_ALYe <- subset(df_pred_E_ALYe, Endpt == "Reproduction" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )

df_predobs_Reproduction_E_ALYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_E_ALYe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_E_ALYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_E_ALYe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## F_ALKe ###############################################################

df_pred_F_ALKe <- f_read_predobs(path_F_ALKe, Nb_experiment, df_data_obs)

df_pred_Weight_F_ALKe <- subset(df_pred_F_ALKe, Endpt == "Weight" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
df_pred_Reproduction_F_ALKe <- subset(df_pred_F_ALKe, Endpt == "Reproduction" & Time !=0)|>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )

df_predobs_Reproduction_F_ALKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_F_ALKe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_F_ALKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_F_ALKe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

::: panel-tabset
## A_FLYw

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_A_FLYw
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_A_FLYw,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_A_FLYw,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsA_FLYw, include = F}
ggsave(
  filename = "A_FLYw_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## B_FLYe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_B_FLYe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_B_FLYe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_B_FLYe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsB_FLYe, include = F}
ggsave(
  filename = "B_FLYe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## C_AWYe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_C_AWYe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_C_AWYe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_C_AWYe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsC_AWYe, include = F}
ggsave(
  filename = "C_AWYe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## D_AWKe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_D_AWKe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_D_AWKe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_D_AWKe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsD_AWKe, include = F}
ggsave(
  filename = "D_AWKe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## E_ALYe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_E_ALYe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_E_ALYe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_E_ALYe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsE_ALYe, include = F}
ggsave(
  filename = "E_ALYe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## F_ALKe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_F_ALKe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_F_ALKe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_F_ALKe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsF_ALKe, include = F}
ggsave(
  filename = "F_ALKe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```
:::

```{r countfold, warning=F}

No_round <- 1

f_count_fold <- function(df_predobs_Weight, df_predobs_Reproduction, No_round) {
  Weight_count_fold2 <- round(length(subset(df_predobs_Weight, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight$Weight_obs) * 100, No_round)

  Weight_count_fold5 <- round(length(subset(df_predobs_Weight, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight$Weight_obs) * 100, No_round)
  
  Repro_count_fold2 <- round(length(subset(df_predobs_Reproduction, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Reproduction_obs) / length(df_predobs_Reproduction$Reproduction_obs) * 100, No_round)
  
  Repro_count_fold5 <- round(length(subset(df_predobs_Reproduction, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Reproduction_obs) / length(df_predobs_Reproduction$Reproduction_obs) * 100, No_round)
  
  df_predobs_Reproduction_0 <- df_predobs_Reproduction |>
    filter(Reproduction_obs > 0) 
  
  Repro0_count_fold2 <- round(length(subset(df_predobs_Reproduction_0, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Reproduction_obs) / length(df_predobs_Reproduction_0$Reproduction_obs) * 100, No_round)
  
  Repro0_count_fold5 <- round(length(subset(df_predobs_Reproduction_0, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Reproduction_obs) / length(df_predobs_Reproduction_0$Reproduction_obs) * 100, No_round)
  
  df_fold <- data.frame(
    Endpoint = c("Weight", "Reproduction", "Observed reproduction above 0"),
    '% of predictions in fold 2' = c(Weight_count_fold2, Repro_count_fold2, Repro0_count_fold2),
    '% of predictions in fold 5' = c(Weight_count_fold5, Repro_count_fold5, Repro0_count_fold5)
  )
  
  return(df_fold)

}

list_weight <- mget(paste0("df_predobs_Weight_", list_models))
list_repro  <- mget(paste0("df_predobs_Reproduction_", list_models))

df_fold <- purrr::map2_dfr(
  list_weight,
  list_repro,
  f_count_fold,
  .id = "Model"
)

df_fold <- df_fold %>%
  dplyr::mutate(Model = model_names[as.integer(Model)])

df_fold |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

```
