```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# Model comparison

## Data importation

```{r expfit, message=F, warning=F}

path_fig <- here::here("fig/DEB_Models")

path_A_FLYw <- here::here("mod/A_DEB_FLYw")
path_B_FLYe <- here::here("mod/B_DEB_FLYe")
path_C_CWYe <- here::here("mod/C_DEB_CWYe")
path_D_CWKe <- here::here("mod/D_DEB_CWKe")
path_E_CLYe <- here::here("mod/E_DEB_CLYe")
path_F_CLKe <- here::here("mod/F_DEB_CLKe")

l_Experiments_fit <- c(
  "Bart2019_XP1_1",  
  "Bart2019_XP1_2",  
  #"Bart2019_XP2",
  "Bart2019_XP3",   
  "Bart2019_XP4_1",
  "Bart2019_XP4_2",
  "Bart2019_XP5", 
  "Bart2020",
  #"Gollot2026_lufa"
  "Gollot2026_dens_D1",
  "Gollot2026_dens_D2",
  "Gollot2026_dens_D2b",
  "Gollot2026_dens_D5",
  "Gollot2026_dens_D7"
  )

Adults_alone <- FALSE

df_data_fit <- f_import_data_DEB(l_Experiments_fit, Adults_alone)

Experiments_carac <- f_get_experiments()
l_Experiments_tot <- Experiments_carac$l_Experiments_tot
l_carac <- Experiments_carac$l_carac
df_carc_exp <- Experiments_carac$df_carc_exp

```

## Model fits

```{r writeIn, message=F, warning=F}
NbIter <- 100000
OM_diff <- TRUE
RTOL <- 1e-7
ATOL <- 1e-6

######### A FLYw ###############################################################

seeds <- c(C1 = 3303, C2 = 3666, C3 = 2212)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kap,          Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (wE,           LogUniform,              1,      1000);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_A_FLYw, l_Experiments_fit, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### B FLYe ###############################################################

seeds <- c(C1 = 3313, C2 = 6666, C3 = 1212)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kap,          Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,    0.000000001,      0.1);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_B_FLYe, l_Experiments_fit, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### C CWYe ###############################################################

seeds <- c(C1 = 3333, C2 = 6669, C3 = 1210)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_C_CWYe, l_Experiments_fit, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### D CWKe ###############################################################

seeds <- c(C1 = 3303, C2 = 6636, C3 = 2929)

text_priors <- '
Distrib (Fm,           LogUniform,         0.0001,      0.3);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (K,            Uniform,            0.0001,        1);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_D_CWKe, l_Experiments_fit, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### E CLYe ###############################################################

seeds <- c(C1 = 3333, C2 = 7880, C3 = 1210)

text_priors <- '
Distrib (Fm,           TruncNormal,           0.1,      0.2,  0.0001,     0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_E_CLYe, l_Experiments_fit, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######### F CLKe ###############################################################

seeds <- c(C1 = 3330, C2 = 6646, C3 = 1212)

text_priors <- '
Distrib (Fm,           TruncNormal_cv,     0.1,      0.2,      0.0001,    0.8);
Distrib (pAm,          TruncNormal_cv,        100,      0.2,      40,    2000);
Distrib (r_pAm_pM,     TruncNormal_cv,        0.8,      0.1,     0.1,       2);
Distrib (v,            TruncNormal_cv,    0.18505,      0.1,   0.001,       2);
Distrib (kapJ,         Uniform,                 0,        1);
Distrib (kapA,         Uniform,                 0,        1);
Distrib (Ehp,          TruncNormal_cv,        100,      0.2,      20,     300);
Distrib (E_coc,        TruncNormal_cv,         30,      0.2,       1,     300);
Distrib (rOM_ClxHorse, LogUniform,        0.00001,      0.3);
Distrib (K,            Uniform,           0.00001,        2);
Distrib (dv,           TruncNormal_cv,          2,      0.5,       0,      10);
Distrib (de,           LogUniform,     0.000000001,     0.1);
Distrib (tau,          TruncNormal_cv,          7,      0.5,       0,      50);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,    Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_tot(path_F_CLKe, l_Experiments_fit, Adults_alone, OM_diff, 
         text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

```

## Estimates results

```{r getres, echo=F, message=F, warning=F}

######### A FLYw ###############################################################

MCMC_out_A_FLYw <- f_MCSim(path_A_FLYw)

NC_A_FLYw <- MCMC_out_A_FLYw$NC
Nb_param_A_FLYw <- MCMC_out_A_FLYw$Nb_param
Nb_experiment_A_FLYw <- MCMC_out_A_FLYw$Nb_experiment
Nb_iter_kept_A_FLYw <- MCMC_out_A_FLYw$Nb_iter_kept
N_iter_setpoint_A_FLYw <- MCMC_out_A_FLYw$N_iter_setpoint
L_parameters_A_FLYw <- unique(MCMC_out_A_FLYw$Priors$Nom)

LL_A_FLYw <- f_get_mode(MCMC_out_A_FLYw$df_LnData$LnData)
n_A_FLYw <- length(na.omit(df_data_fit$Weight)) + 
  length(na.omit(df_data_fit$Reproduction))
k_A_FLYw <- Nb_param_A_FLYw - 1 # On enlève le Sigma_W

BIC_A_FLYw <- -2*LL_A_FLYw+k_A_FLYw*log(n_A_FLYw)

Summary_res_A_FLYw <- 
  as.data.frame(MCMC_out_A_FLYw$Summary_res)[1:length(L_parameters_A_FLYw)] |> 
  mutate(Model = "A_FLYw") 

######### B FLYe ###############################################################

MCMC_out_B_FLYe <- f_MCSim(path_B_FLYe)

NC_B_FLYe <- MCMC_out_B_FLYe$NC
Nb_param_B_FLYe <- MCMC_out_B_FLYe$Nb_param
Nb_experiment_B_FLYe <- MCMC_out_B_FLYe$Nb_experiment
Nb_iter_kept_B_FLYe <- MCMC_out_B_FLYe$Nb_iter_kept
N_iter_setpoint_B_FLYe <- MCMC_out_B_FLYe$N_iter_setpoint
L_parameters_B_FLYe <- unique(MCMC_out_B_FLYe$Priors$Nom)

LL_B_FLYe <- f_get_mode(MCMC_out_B_FLYe$df_LnData$LnData)
n_B_FLYe <- length(na.omit(df_data_fit$Weight)) + 
  length(na.omit(df_data_fit$Reproduction))
k_B_FLYe <- Nb_param_B_FLYe - 1 # On enlève le Sigma_W

BIC_B_FLYe <- -2*LL_B_FLYe+k_B_FLYe*log(n_B_FLYe)

Summary_res_B_FLYe <- 
  as.data.frame(MCMC_out_B_FLYe$Summary_res)[1:length(L_parameters_B_FLYe)] |> 
  mutate(Model = "B_FLYe") 

######### C CWYe ###############################################################

MCMC_out_C_CWYe <- f_MCSim(path_C_CWYe)

NC_C_CWYe <- MCMC_out_C_CWYe$NC
Nb_param_C_CWYe <- MCMC_out_C_CWYe$Nb_param
Nb_experiment_C_CWYe <- MCMC_out_C_CWYe$Nb_experiment
Nb_iter_kept_C_CWYe <- MCMC_out_C_CWYe$Nb_iter_kept
N_iter_setpoint_C_CWYe <- MCMC_out_C_CWYe$N_iter_setpoint
L_parameters_C_CWYe <- unique(MCMC_out_C_CWYe$Priors$Nom)

LL_C_CWYe <- f_get_mode(MCMC_out_C_CWYe$df_LnData$LnData)
n_C_CWYe <- length(na.omit(df_data_fit$Weight)) + 
  length(na.omit(df_data_fit$Reproduction))
k_C_CWYe <- Nb_param_C_CWYe - 1 # On enlève le Sigma_W

BIC_C_CWYe <- -2*LL_C_CWYe+k_C_CWYe*log(n_C_CWYe)

Summary_res_C_CWYe <- 
  as.data.frame(MCMC_out_C_CWYe$Summary_res)[1:length(L_parameters_C_CWYe)] |> 
  mutate(Model = "C_CWYe") 

######### D CWKe ###############################################################

MCMC_out_D_CWKe <- f_MCSim(path_D_CWKe)

NC_D_CWKe <- MCMC_out_D_CWKe$NC
Nb_param_D_CWKe <- MCMC_out_D_CWKe$Nb_param
Nb_experiment_D_CWKe <- MCMC_out_D_CWKe$Nb_experiment
Nb_iter_kept_D_CWKe <- MCMC_out_D_CWKe$Nb_iter_kept
N_iter_setpoint_D_CWKe <- MCMC_out_D_CWKe$N_iter_setpoint
L_parameters_D_CWKe <- unique(MCMC_out_D_CWKe$Priors$Nom)

LL_D_CWKe <- f_get_mode(MCMC_out_D_CWKe$df_LnData$LnData)
n_D_CWKe <- length(na.omit(df_data_fit$Weight)) + 
  length(na.omit(df_data_fit$Reproduction))
k_D_CWKe <- Nb_param_D_CWKe - 1 # On enlève le Sigma_W

BIC_D_CWKe <- -2*LL_D_CWKe+k_D_CWKe*log(n_D_CWKe)

Summary_res_D_CWKe <- 
  as.data.frame(MCMC_out_D_CWKe$Summary_res)[1:length(L_parameters_D_CWKe)] |> 
  mutate(Model = "D_CWKe") 

######### E CLYe ###############################################################

MCMC_out_E_CLYe <- f_MCSim(path_E_CLYe)

NC_E_CLYe <- MCMC_out_E_CLYe$NC
Nb_param_E_CLYe <- MCMC_out_E_CLYe$Nb_param
Nb_experiment_E_CLYe <- MCMC_out_E_CLYe$Nb_experiment
Nb_iter_kept_E_CLYe <- MCMC_out_E_CLYe$Nb_iter_kept
N_iter_setpoint_E_CLYe <- MCMC_out_E_CLYe$N_iter_setpoint
L_parameters_E_CLYe <- unique(MCMC_out_E_CLYe$Priors$Nom)

LL_E_CLYe <- f_get_mode(MCMC_out_E_CLYe$df_LnData$LnData)
n_E_CLYe <- length(na.omit(df_data_fit$Weight)) + 
  length(na.omit(df_data_fit$Reproduction))
k_E_CLYe <- Nb_param_E_CLYe - 1 # On enlève le Sigma_W

BIC_E_CLYe <- -2*LL_E_CLYe+k_E_CLYe*log(n_E_CLYe)

Summary_res_E_CLYe <- 
  as.data.frame(MCMC_out_E_CLYe$Summary_res)[1:length(L_parameters_E_CLYe)] |> 
  mutate(Model = "E_CLYe") 

######### F CLKe ###############################################################

MCMC_out_F_CLKe <- f_MCSim(path_F_CLKe)

NC_F_CLKe <- MCMC_out_F_CLKe$NC
Nb_param_F_CLKe <- MCMC_out_F_CLKe$Nb_param
Nb_experiment_F_CLKe <- MCMC_out_F_CLKe$Nb_experiment
Nb_iter_kept_F_CLKe <- MCMC_out_F_CLKe$Nb_iter_kept
N_iter_setpoint_F_CLKe <- MCMC_out_F_CLKe$N_iter_setpoint
L_parameters_F_CLKe <- unique(MCMC_out_F_CLKe$Priors$Nom)

LL_F_CLKe <- f_get_mode(MCMC_out_F_CLKe$df_LnData$LnData)
n_F_CLKe <- length(na.omit(df_data_fit$Weight)) + 
  length(na.omit(df_data_fit$Reproduction))
k_F_CLKe <- Nb_param_F_CLKe - 1 # On enlève le Sigma_W

BIC_F_CLKe <- -2*LL_F_CLKe+k_F_CLKe*log(n_F_CLKe)

Summary_res_F_CLKe <- 
  as.data.frame(MCMC_out_F_CLKe$Summary_res)[1:length(L_parameters_F_CLKe)] |> 
  mutate(Model = "F_CLKe") 

list_models <- c("A_FLYw", "B_FLYe", "C_CWYe", "D_CWKe", "E_CLYe", "F_CLKe")
df_LL_BIC <- data.frame(
  Model = list_models,
  LL = round(unlist(mget(paste0("LL_", list_models))), 2),
  BIC = round(unlist(mget(paste0("BIC_", list_models))), 2)
)

```

```{r resall}
#| tbl-cap: Estimation results from all models. 

list_models <- c("A_FLYw", "B_FLYe", "C_CWYe", "D_CWKe", "E_CLYe", "F_CLKe")
list_model_summary <- mget(paste0("Summary_res_", list_models))

param_order <- c(
  "pAm", "r_pAm_pM", "Fm", "rOM_ClxHorse", "K", "v", "kap", "kapJ", "kapA", "tau",
  "Ehp", "E_coc", "dv", "de", "wE", "Sigma_W"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = str_c(
        round(Result_mode, 3),
        " [", round(`2.5%`, 3),
        " ; ", round(`97.5%`, 3), "]"
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_model_summary %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  ) |> 
  left_join(df_LL_BIC)

df_result |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )
```

## Chains

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_A_FLYw
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_A_FLYw$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsA_FLYw, include = F}
ggsave(
  filename="A_FLYw_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_B_FLYe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_B_FLYe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsB_FLYe, include = F}
ggsave(
  filename="B_FLYe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_CWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_C_CWYe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_C_CWYe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC_CWYe, include = F}
ggsave(
  filename="C_CWYe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_CWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_D_CWKe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_D_CWKe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsD_CWKe, include = F}
ggsave(
  filename="D_CWKe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## E_CLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_E_CLYe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_E_CLYe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsE_CLYe, include = F}
ggsave(
  filename="E_CLYe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## F_CLKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_F_CLKe
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_F_CLKe$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsF_CLKe, include = F}
ggsave(
  filename="F_CLKe_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

## Likelihoods

::: panel-tabset
## A_FLYw

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_A_FLYw
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_A_FLYw$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_A_FLYw$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_FLYw$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_A_FLYw$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_FLYw$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLA_FLYw, include = F}
ggsave(
  filename="A_FLYw_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## B_FLYe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_B_FLYe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_B_FLYe$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_B_FLYe$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_B_FLYe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_B_FLYe$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_B_FLYe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLB_FLYe, include = F}
ggsave(
  filename="B_FLYe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## C_CWYe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_C_CWYe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_C_CWYe$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_C_CWYe$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_C_CWYe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_C_CWYe$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_C_CWYe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLC_CWYe, include = F}
ggsave(
  filename="C_CWYe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## D_CWKe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_D_CWKe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_D_CWKe$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_D_CWKe$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_D_CWKe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_D_CWKe$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_D_CWKe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLD_CWKe, include = F}
ggsave(
  filename="D_CWKe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## E_CLYe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_E_CLYe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_E_CLYe$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_E_CLYe$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_E_CLYe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_E_CLYe$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_E_CLYe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLE_CLYe, include = F}
ggsave(
  filename="E_CLYe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## F_CLKe

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_F_CLKe
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_F_CLKe$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_F_CLKe$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_F_CLKe$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_F_CLKe$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_F_CLKe$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLF_CLKe, include = F}
ggsave(
  filename="F_CLKe_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```
:::

## Chains convergence

```{r, echo=F, message=F, warning=F}

####### A_FLYw #################################################################

# Large format per chain
mcmc_list_A_FLYw <- lapply(
  split(
    MCMC_out_A_FLYw$Chains, 
    MCMC_out_A_FLYw$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_A_FLYw <- as.mcmc.list(mcmc_list_A_FLYw)

####### B_FLYe #################################################################

# Large format per chain
mcmc_list_B_FLYe <- lapply(
  split(
    MCMC_out_B_FLYe$Chains, 
    MCMC_out_B_FLYe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_B_FLYe <- as.mcmc.list(mcmc_list_B_FLYe)

####### C_CWYe #################################################################

# Large format per chain
mcmc_list_C_CWYe <- lapply(
  split(
    MCMC_out_C_CWYe$Chains, 
    MCMC_out_C_CWYe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_C_CWYe <- as.mcmc.list(mcmc_list_C_CWYe)

####### D_CWKe #################################################################

# Large format per chain
mcmc_list_D_CWKe <- lapply(
  split(
    MCMC_out_D_CWKe$Chains, 
    MCMC_out_D_CWKe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_D_CWKe <- as.mcmc.list(mcmc_list_D_CWKe)

####### E_CLYe #################################################################

# Large format per chain
mcmc_list_E_CLYe <- lapply(
  split(
    MCMC_out_E_CLYe$Chains, 
    MCMC_out_E_CLYe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_E_CLYe <- as.mcmc.list(mcmc_list_E_CLYe)

####### F_CLKe #################################################################

# Large format per chain
mcmc_list_F_CLKe <- lapply(
  split(
    MCMC_out_F_CLKe$Chains, 
    MCMC_out_F_CLKe$Chains$Chain
    ),
  function(d) {
    wide <- d %>%
      dplyr::select(Iteration, Parameter, value) %>%
      pivot_wider(names_from = Parameter, values_from = value) %>%
      arrange(Iteration)
   mcmc(as.matrix(wide[,-1]))
})

mcmc_list_F_CLKe <- as.mcmc.list(mcmc_list_F_CLKe)

```

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_A_FLYw
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_A_FLYw,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_A_FLYw, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_A_FLYw
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_A_FLYw <- mcmc.list(
  lapply(mcmc_list_A_FLYw, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))

file_rds <- here::here("fig/DEB_Models/A_FLYw_ipairs_plot.png")

if (!file.exists(file_rds)) {
  
  png(here::here("fig/DEB_Models/A_FLYw_ipairs_plot.png"), width = 3000, height = 3000, res = 300)
  
  ipairs(
    as.matrix(mcmc_list_corr_A_FLYw), 
    colramp = colramp_aurora, 
    pixs=0.25, 
    cex.diag = 0.5
    )
  dev.off()
}

ipairs(
  as.matrix(mcmc_list_corr_A_FLYw), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_B_FLYe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_B_FLYe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_B_FLYe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_B_FLYe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_B_FLYe <- mcmc.list(
  lapply(mcmc_list_B_FLYe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))

file_rds <- here::here("fig/DEB_Models/B_FLYe_ipairs_plot.png")

if (!file.exists(file_rds)) {
  
  png(here::here("fig/DEB_Models/B_FLYe_ipairs_plot.png"), width = 3000, height = 3000, res = 300)
  
  ipairs(
    as.matrix(mcmc_list_corr_B_FLYe), 
    colramp = colramp_aurora, 
    pixs=0.25, 
    cex.diag = 0.5
    )
  dev.off()
}

ipairs(
  as.matrix(mcmc_list_corr_B_FLYe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )
```

## C_CWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_C_CWYe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_C_CWYe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_C_CWYe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_C_CWYe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_C_CWYe <- mcmc.list(
  lapply(mcmc_list_C_CWYe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))

file_rds <- here::here("fig/DEB_Models/C_CWYe_ipairs_plot.png")

if (!file.exists(file_rds)) {
  
  png(here::here("fig/DEB_Models/C_CWYe_ipairs_plot.png"), width = 3000, height = 3000, res = 300)
  
  ipairs(
    as.matrix(mcmc_list_corr_C_CWYe), 
    colramp = colramp_aurora, 
    pixs=0.25, 
    cex.diag = 0.5
    )
  dev.off()
}

ipairs(
  as.matrix(mcmc_list_corr_C_CWYe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )
```

## D_CWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_D_CWKe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_D_CWKe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_D_CWKe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_D_CWKe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_D_CWKe <- mcmc.list(
  lapply(mcmc_list_D_CWKe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))

file_rds <- here::here("fig/DEB_Models/D_CWKe_ipairs_plot.png")

if (!file.exists(file_rds)) {
  
  png(here::here("fig/DEB_Models/D_CWKe_ipairs_plot.png"), width = 3000, height = 3000, res = 300)
  
  ipairs(
    as.matrix(mcmc_list_corr_D_CWKe), 
    colramp = colramp_aurora, 
    pixs=0.25, 
    cex.diag = 0.5
    )
  dev.off()
}

ipairs(
  as.matrix(mcmc_list_corr_D_CWKe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )
```

## E_CLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_E_CLYe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_E_CLYe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_E_CLYe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_E_CLYe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_E_CLYe <- mcmc.list(
  lapply(mcmc_list_E_CLYe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))

file_rds <- here::here("fig/DEB_Models/E_CLYe_ipairs_plot.png")

if (!file.exists(file_rds)) {
  
  png(here::here("fig/DEB_Models/E_CLYe_ipairs_plot.png"), width = 3000, height = 3000, res = 300)
  
  ipairs(
    as.matrix(mcmc_list_corr_E_CLYe), 
    colramp = colramp_aurora, 
    pixs=0.25, 
    cex.diag = 0.5
    )
  dev.off()
}

ipairs(
  as.matrix(mcmc_list_corr_E_CLYe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )

```

## F_CLKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_F_CLKe
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_F_CLKe,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(
    mcmc_list_F_CLKe, 
    confidence = 0.95, 
    transform=FALSE, 
    autoburnin=TRUE, 
    multivariate=TRUE
    )
  
  print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_F_CLKe
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr_F_CLKe <- mcmc.list(
  lapply(mcmc_list_F_CLKe, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))

file_rds <- here::here("fig/DEB_Models/F_CLKe_ipairs_plot.png")

if (!file.exists(file_rds)) {
  
  png(here::here("fig/DEB_Models/F_CLKe_ipairs_plot.png"), width = 3000, height = 3000, res = 300)
  
  ipairs(
    as.matrix(mcmc_list_corr_F_CLKe), 
    colramp = colramp_aurora, 
    pixs=0.25, 
    cex.diag = 0.5
    )
  dev.off()
}

ipairs(
  as.matrix(mcmc_list_corr_F_CLKe), 
  colramp = colramp_aurora, 
  pixs=0.25, 
  cex.diag = 0.5
  )
```
:::

## Posterior distributions

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_A_FLYw
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_A_FLYw$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_A_FLYw$Chains_plot <- MCMC_out_A_FLYw$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_A_FLYw$Chains_plot, Nom %in% L_parameters_A_FLYw),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostA_FLYw, include = F}
ggsave(
  filename="A_FLYw_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_B_FLYe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_B_FLYe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_B_FLYe$Chains_plot <- MCMC_out_B_FLYe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_B_FLYe$Chains_plot, Nom %in% L_parameters_B_FLYe),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostB_FLYe, include = F}
ggsave(
  filename="B_FLYe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_CWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_C_CWYe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_C_CWYe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_C_CWYe$Chains_plot <- MCMC_out_C_CWYe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_C_CWYe$Chains_plot, Nom %in% L_parameters_C_CWYe),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostC_CWYe, include = F}
ggsave(
  filename="C_CWYe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_CWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_D_CWKe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_D_CWKe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_D_CWKe$Chains_plot <- MCMC_out_D_CWKe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_D_CWKe$Chains_plot, Nom %in% L_parameters_D_CWKe),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostD_CWKe, include = F}
ggsave(
  filename="D_CWKe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## E_CLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_E_CLYe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_E_CLYe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_E_CLYe$Chains_plot <- MCMC_out_E_CLYe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_E_CLYe$Chains_plot, Nom %in% L_parameters_E_CLYe),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostE_CLYe, include = F}
ggsave(
  filename="E_CLYe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

## F_CLKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_F_CLKe
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_F_CLKe$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_F_CLKe$Chains_plot <- MCMC_out_F_CLKe$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_F_CLKe$Chains_plot, Nom %in% L_parameters_F_CLKe),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostF_CLKe, include = F}
ggsave(
  filename="F_CLKe_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

## Predicted vs. Observed

```{r}
l_param_name_A_FLYw <- names(Summary_res_A_FLYw) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.") 

f_In_predobs(path_A_FLYw, l_Experiments_fit, Adults_alone, OM_diff, l_param_name_A_FLYw)

l_param_name_B_FLYe <- names(Summary_res_B_FLYe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_predobs(path_B_FLYe, l_Experiments_fit, Adults_alone, OM_diff, l_param_name_B_FLYe)

l_param_name_C_CWYe <- names(Summary_res_C_CWYe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_predobs(path_C_CWYe, l_Experiments_fit, Adults_alone, OM_diff, l_param_name_C_CWYe)

l_param_name_D_CWKe <- names(Summary_res_D_CWKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_predobs(path_D_CWKe, l_Experiments_fit, Adults_alone, OM_diff, l_param_name_D_CWKe)

l_param_name_E_CLYe <- names(Summary_res_E_CLYe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_predobs(path_E_CLYe, l_Experiments_fit, Adults_alone, OM_diff, l_param_name_E_CLYe)

l_param_name_F_CLKe <- names(Summary_res_F_CLKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_predobs(path_F_CLKe, l_Experiments_fit, Adults_alone, OM_diff, l_param_name_F_CLKe)
```

```{bash, eval=F, execute=F}
for j in $(seq 1 12); do
./mcsim.DEBcali DEB_setpoint_predobs_${j}.in
done
```

```{r, results=F, message=F, warning=F}

Nb_experiment <- 12

df_data_obs <- df_data_fit |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

######## A_FLYw ###############################################################

df_pred_A_FLYw <- f_read_predobs(path_A_FLYw, Nb_experiment, df_data_obs)

df_pred_Weight_A_FLYw <- subset(df_pred_A_FLYw, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_A_FLYw <- subset(df_pred_A_FLYw, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_A_FLYw <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_A_FLYw, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_A_FLYw <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_A_FLYw, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## B_FLYe ###############################################################

df_pred_B_FLYe <- f_read_predobs(path_B_FLYe, Nb_experiment, df_data_obs)

df_pred_Weight_B_FLYe <- subset(df_pred_B_FLYe, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_B_FLYe <- subset(df_pred_B_FLYe, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_B_FLYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_B_FLYe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_B_FLYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_B_FLYe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## C_CWYe ###############################################################

df_pred_C_CWYe <- f_read_predobs(path_C_CWYe, Nb_experiment, df_data_obs)

df_pred_Weight_C_CWYe <- subset(df_pred_C_CWYe, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_C_CWYe <- subset(df_pred_C_CWYe, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_C_CWYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_C_CWYe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_C_CWYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_C_CWYe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## D_CWKe ###############################################################

df_pred_D_CWKe <- f_read_predobs(path_D_CWKe, Nb_experiment, df_data_obs)

df_pred_Weight_D_CWKe <- subset(df_pred_D_CWKe, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_D_CWKe <- subset(df_pred_D_CWKe, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_D_CWKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_D_CWKe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_D_CWKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_D_CWKe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## E_CLYe ###############################################################

df_pred_E_CLYe <- f_read_predobs(path_E_CLYe, Nb_experiment, df_data_obs)

df_pred_Weight_E_CLYe <- subset(df_pred_E_CLYe, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_E_CLYe <- subset(df_pred_E_CLYe, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_E_CLYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_E_CLYe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_E_CLYe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_E_CLYe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

######## F_CLKe ###############################################################

df_pred_F_CLKe <- f_read_predobs(path_F_CLKe, Nb_experiment, df_data_obs)

df_pred_Weight_F_CLKe <- subset(df_pred_F_CLKe, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_F_CLKe <- subset(df_pred_F_CLKe, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_F_CLKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_F_CLKe, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_F_CLKe <- df_data_obs |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_F_CLKe, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

::: panel-tabset
## A_FLYw

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_A_FLYw
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[2], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_A_FLYw,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_A_FLYw,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsA_FLYw, include = F}
ggsave(
  filename = "A_FLYw_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## B_FLYe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_B_FLYe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[2], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_B_FLYe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_B_FLYe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsB_FLYe, include = F}
ggsave(
  filename = "B_FLYe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## C_CWYe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_C_CWYe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[2], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_C_CWYe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_C_CWYe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsC_CWYe, include = F}
ggsave(
  filename = "C_CWYe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## D_CWKe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_D_CWKe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[2], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_D_CWKe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_D_CWKe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsD_CWKe, include = F}
ggsave(
  filename = "D_CWKe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## E_CLYe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_E_CLYe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[2], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_E_CLYe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_E_CLYe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsE_CLYe, include = F}
ggsave(
  filename = "E_CLYe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## F_CLKe

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_F_CLKe
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[2], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )

seq_line <- seq(0.01, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_F_CLKe,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = ID_experiment
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.01, 100, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_F_CLKe,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = ID_experiment
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect")

p_predobs

```

```{r savepredobsF_CLKe, include = F}
ggsave(
  filename = "F_CLKe_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```
:::

### Folds

```{r countfold, warning=F}
#| tbl-cap: Folds for Weight and Reproduction for each model.

No_round <- 1

f_count_fold <- function(df_predobs_Weight, df_predobs_Reproduction, No_round) {
  
  df_predobs_Weight <- df_predobs_Weight  |>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )
  df_predobs_Reproduction <- df_predobs_Reproduction  |>
  mutate(
    Ratio_predobs = predict.endpoint / Reproduction_obs,
    Residuals = predict.endpoint - Reproduction_obs
  )
  
  Weight_count_fold2 <- round(length(subset(df_predobs_Weight, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight$Weight_obs) * 100, No_round)

  Weight_count_fold5 <- round(length(subset(df_predobs_Weight, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight$Weight_obs) * 100, No_round)
  
  Repro_count_fold2 <- round(length(subset(df_predobs_Reproduction, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Reproduction_obs) / length(df_predobs_Reproduction$Reproduction_obs) * 100, No_round)
  
  Repro_count_fold5 <- round(length(subset(df_predobs_Reproduction, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Reproduction_obs) / length(df_predobs_Reproduction$Reproduction_obs) * 100, No_round)
  
  df_predobs_Reproduction_0 <- df_predobs_Reproduction |>
    filter(Reproduction_obs > 0) 
  
  Repro0_count_fold2 <- round(length(subset(df_predobs_Reproduction_0, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Reproduction_obs) / length(df_predobs_Reproduction_0$Reproduction_obs) * 100, No_round)
  
  Repro0_count_fold5 <- round(length(subset(df_predobs_Reproduction_0, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Reproduction_obs) / length(df_predobs_Reproduction_0$Reproduction_obs) * 100, No_round)
  
  df_fold <- data.frame(
    Endpoint = c("Weight", "Reproduction", "Observed reproduction above 0"),
    '% of predictions in fold 2' = c(Weight_count_fold2, Repro_count_fold2, Repro0_count_fold2),
    '% of predictions in fold 5' = c(Weight_count_fold5, Repro_count_fold5, Repro0_count_fold5),
  check.names = FALSE
  )
  
  return(df_fold)

}

list_weight <- mget(paste0("df_predobs_Weight_", list_models))
list_repro  <- mget(paste0("df_predobs_Reproduction_", list_models))

df_fold <- purrr::map2_dfr(
  list_weight,
  list_repro,
  f_count_fold,
  .id = "Model"
)

df_fold <- df_fold %>%
  dplyr::mutate(Model = str_remove(Model, "df_predobs_(Weight|Reproduction)_"))

df_fold |> datatable(
  options = list(
    dom = 't',
    pageLength = nrow(df_fold),
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
    )
  ),
  class = "hover"
)

```

### RMSE per experiment

```{r RMSE, message=F, warning=F}
#| tbl-cap: RMSE for Weight and Reproduction per experiment for each model.


f_RMSE_experiment <- function(df_predobs_Weight, df_predobs_Reproduction){
  
  df_rmse_W <- df_predobs_Weight %>%
    group_by(ID_experiment) %>%
    summarise(
      RMSE_Weight = sqrt(mean((predict.endpoint - Weight_obs)^2, na.rm = TRUE))
    )
  
  df_rmse_R <- df_predobs_Reproduction %>%
    group_by(ID_experiment) %>%
    summarise(
      RMSE_Reproduction = sqrt(mean((predict.endpoint - Reproduction_obs)^2, na.rm = TRUE))
    )
  
  df_rmse <- left_join(df_rmse_W, df_rmse_R)
  
  return(df_rmse)
}


df_rmse <- purrr::map2_dfr(
  list_weight,
  list_repro,
  f_RMSE_experiment,
  .id = "Model"
)

df_rmse <- df_rmse %>%
  dplyr::mutate(Model = str_remove(Model, "df_predobs_(Weight|Reproduction)_")) %>%
  pivot_longer(
    cols = starts_with("RMSE"),
    names_to = "Metric",
    values_to = "RMSE"
  )

df_rmse |>
  pivot_wider(
    names_from = Metric,
    values_from = RMSE
  ) |> 
  datatable(
  options = list(
    dom = 't',
    pageLength = nrow(df_rmse),
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
    )
  ),
  class = "hover"
)

```

```{r}
#| fig-cap: RMSE per experiment.
#| label: fig-rmse
#| fig-height: 10
#| fig-width: 12

ID_exp_plot_1 <- unique(df_rmse$ID_experiment)[1:6]
ID_exp_plot_2 <- unique(df_rmse$ID_experiment)[7:12]

ylim_metric <- df_rmse |>
  group_by(Metric) |>
  summarise(
    ymin = min(RMSE, na.rm = TRUE),
    ymax = max(RMSE, na.rm = TRUE),
    .groups = "drop"
  )

make_plot <- function(data, ids, metric_name) {
  
  lims <- ylim_metric |>
    filter(Metric == metric_name)
  
  ggplot(
    subset(data, ID_experiment %in% ids & Metric == metric_name),
    aes(
      x = Model,
      y = RMSE,
      color = Model
    )
  ) +
    geom_point(size = 2) +
    facet_grid(
      . ~ ID_experiment
    ) +
    coord_cartesian(
      ylim = c(lims$ymin, lims$ymax)
    ) +
    scale_color_manual(
      name = "Models",
      values = c(Nord_aurora, Nord_frost)
    ) +
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
      strip.text = element_text(size = 8)
    ) +
    labs(
      x = "Model",
      y = "RMSE"
    )
}

p1_metric1 <- make_plot(df_rmse, ID_exp_plot_1, unique(df_rmse$Metric)[1]) +
  labs(title = "RMSE Weight") +
  theme(
    axis.title.x = element_blank()
  )
p2_metric1 <- make_plot(df_rmse, ID_exp_plot_2, unique(df_rmse$Metric)[1])

p1_metric2 <- make_plot(df_rmse, ID_exp_plot_1, unique(df_rmse$Metric)[2]) +
  labs(title = "RMSE Reproduction") +
  theme(
    axis.title.x = element_blank()
  )
p2_metric2 <- make_plot(df_rmse, ID_exp_plot_2, unique(df_rmse$Metric)[2])

p <- (
  p1_metric1 / p2_metric1 /
  p1_metric2 / p2_metric2
) +
  plot_layout(guides = "collect")

p

```

```{r saveRMSE, include = F}
ggsave(
  filename = "RMSE_per_experiment.png",
  plot = p,
  width = 12, height = 10,
  path = path_fig
) 
```

## Predicted trajectories for Weight and Reproduction

```{r setpointfullin}

Nb_experiment <- 12
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Reproduction"


l_param_name_A_FLYw <- names(Summary_res_A_FLYw) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_A_FLYw, l_Experiments_fit, 
  Adults_alone, OM_diff, 
  l_param_name_A_FLYw, step_sim, Endpoints_print
  )

l_param_name_B_FLYe <- names(Summary_res_B_FLYe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_B_FLYe, l_Experiments_fit, 
  Adults_alone, OM_diff, 
  l_param_name_B_FLYe, step_sim, Endpoints_print
  )

l_param_name_C_CWYe <- names(Summary_res_C_CWYe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_C_CWYe, l_Experiments_fit, 
  Adults_alone, OM_diff, 
  l_param_name_C_CWYe, step_sim, Endpoints_print
  )

l_param_name_D_CWKe <- names(Summary_res_D_CWKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_D_CWKe, l_Experiments_fit, 
  Adults_alone, OM_diff, 
  l_param_name_D_CWKe, step_sim, Endpoints_print
  )

l_param_name_E_CLYe <- names(Summary_res_E_CLYe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_E_CLYe, l_Experiments_fit, 
  Adults_alone, OM_diff, 
  l_param_name_E_CLYe, step_sim, Endpoints_print
  )

l_param_name_F_CLKe <- names(Summary_res_F_CLKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_F_CLKe, l_Experiments_fit, 
  Adults_alone, OM_diff, 
  l_param_name_F_CLKe, step_sim, Endpoints_print
  )

```

```{bash, eval=F, execute=F}
for j in $(seq 1 12); do
./mcsim.DEBcali DEB_setpoint_full_${j}.in
done
```

```{r}

width_plot <- 12
height_plot <- 12

file_rds_A_FLYw <- file.path(path_A_FLYw, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_A_FLYw)) {
  df_pred_full_A_FLYw <- readRDS(file_rds_A_FLYw)
} else {
  df_pred_full_A_FLYw <- f_read_Setpoint_full(path_A_FLYw, Nb_experiment, select_times, step_sim)
}

file_rds_B_FLYe <- file.path(path_B_FLYe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_B_FLYe)) {
  df_pred_full_B_FLYe <- readRDS(file_rds_B_FLYe)
} else {
  df_pred_full_B_FLYe <- f_read_Setpoint_full(path_B_FLYe, Nb_experiment, select_times, step_sim)
}

file_rds_C_CWYe <- file.path(path_C_CWYe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_C_CWYe)) {
  df_pred_full_C_CWYe <- readRDS(file_rds_C_CWYe)
} else {
  df_pred_full_C_CWYe <- f_read_Setpoint_full(path_C_CWYe, Nb_experiment, select_times, step_sim)
}

file_rds_D_CWKe <- file.path(path_D_CWKe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_D_CWKe)) {
  df_pred_full_D_CWKe <- readRDS(file_rds_D_CWKe)
} else {
  df_pred_full_D_CWKe <- f_read_Setpoint_full(path_D_CWKe, Nb_experiment, select_times, step_sim)
}

file_rds_E_CLYe <- file.path(path_E_CLYe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_E_CLYe)) {
  df_pred_full_E_CLYe <- readRDS(file_rds_E_CLYe)
} else {
  df_pred_full_E_CLYe <- f_read_Setpoint_full(path_E_CLYe, Nb_experiment, select_times, step_sim)
}

file_rds_F_CLKe <- file.path(path_F_CLKe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_F_CLKe)) {
  df_pred_full_F_CLKe <- readRDS(file_rds_F_CLKe)
} else {
  df_pred_full_F_CLKe <- f_read_Setpoint_full(path_F_CLKe, Nb_experiment, select_times, step_sim)
}

```

::: panel-tabset
## A_FLYw

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_A_FLYw
#| fig-height: 12
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
  col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )
  
  pW <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_A_FLYw, Endpt == "Weight"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_FLYw, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()
  
  pR <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_A_FLYw, Endpt == "Reproduction"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_FLYw, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRA_FLYw, include = F}
ggsave(
  filename="A_FLYw_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## B_FLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_B_FLYe
#| fig-height: 12
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
  col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )
  
  pW <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_B_FLYe, Endpt == "Weight"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_B_FLYe, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()
  
  pR <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_B_FLYe, Endpt == "Reproduction"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_B_FLYe, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRB_FLYe, include = F}
ggsave(
  filename="B_FLYe_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## C_CWYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_C_CWYe
#| fig-height: 12
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
  col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )
  
  pW <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_C_CWYe, Endpt == "Weight"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_C_CWYe, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()
  
  pR <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_C_CWYe, Endpt == "Reproduction"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_C_CWYe, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRC_CWYe, include = F}
ggsave(
  filename="C_CWYe_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## D_CWKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_D_CWKe
#| fig-height: 12
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
  col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )
  
  pW <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_D_CWKe, Endpt == "Weight"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_D_CWKe, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()
  
  pR <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_D_CWKe, Endpt == "Reproduction"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_D_CWKe, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRD_CWKe, include = F}
ggsave(
  filename="D_CWKe_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## E_CLYe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_E_CLYe
#| fig-height: 12
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
  col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )
  
  pW <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_E_CLYe, Endpt == "Weight"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_E_CLYe, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()
  
  pR <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_E_CLYe, Endpt == "Reproduction"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_E_CLYe, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRE_CLYe, include = F}
ggsave(
  filename="E_CLYe_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## F_CLKe

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_F_CLKe
#| fig-height: 12
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
  col_experiment <- c(
  Nord_aurora[1], Nord_aurora[1], Nord_polar[1],
  Nord_aurora[2],
  Nord_aurora[3], Nord_aurora[3],
  Nord_aurora[4], 
  Nord_aurora[5], rev(Nord_frost)
  )
  
  pW <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_F_CLKe, Endpt == "Weight"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_CLKe, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()
  
  pR <- ggplot()+
    
    geom_ribbon(
      data = subset(df_pred_full_F_CLKe, Endpt == "Reproduction"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_CLKe, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col,
      scales = "free"
      )+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRF_CLKe, include = F}
ggsave(
  filename="F_CLKe_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```
:::

## Sensitivity analysis - CWKe

```{r ASparam}

seed       <- 361224
Sobol_type <- "Jansen"
Nb_sim     <- 50000 # (p + 2) * Nb_sim simulations
CV         <- 0.1
processors <- 2
Nboot      <- 1000 # nb replicat
NOut       <- 3    # number of outputs
Temperature_bol <- TRUE

l_params_median <- c(
  # Environment
  muOM = 11700, rOM_ClxHorse = 0.0087741,
  # Energy assimilation
  Fm = 0.0006748850, kapX = 0.258, K = 0.00611915, pAm = 160.85200, v = 0.212075, 
  kapJ  = 0.913533, kapA = 0.494191, tau = 12.9371,
  # Maintenance and growth
  r_pAm_pM = 0.75549700, Eg = 4183, dv = 4.47722, de = 1.849940e-09,         
  # Maturity
  kJ = 0.002793, Ehb = 0.5, Ehp = 97.5249,
  # Reproduction
  E_coc = 27.4525, kapR = 0.475,   
  # Metabolic response to T
  TAH = 28750, TH = 293.2, TA = 7976, Tref = 293.15   
)

# Sobol_design <- f_AS_Sobol_design(Sobol_type, seed, Nb_sim, CV, Processors, Nboot, Nout, l_params_median, Temperature_bol)
# 
# l_Sobol_param <- Sobol_design$Sobol_param
# Sobol_info <- Sobol_design$Sobol

path_AS <- here::here("mod/Z_AS")
file_rds_AS <- file.path(path_AS, paste0("df_Sobol_param.rds"))

# if (file.exists(file_rds_AS)) {
#   df_Sobol_param <- readRDS(file_rds_AS)
# } else {
#   # Long to generate
#   df_Sobol_param <- do.call(rbind, lapply(l_Sobol_param, as.data.frame)) 
#   df_Sobol_param <- cbind(id = seq_len(nrow(df_Sobol_param)), df_Sobol_param)
#   saveRDS(df_Sobol_param, file_rds_AS)
#   write.table(df_Sobol_param, file = here::here(paste0("mod/FINAL/Z_AS/Param_sobol_", Sobol_type,".txt")), sep = "\t", row.names = FALSE, quote = FALSE)
# }



# tmp <- read.table(here::here(paste0("mod/FINAL/Z_AS/Param_sobol_", Sobol_type,".txt")), sep = "\t")

# In the AS folder in the terminal :
# makemcsim DEBcali.model
# ./mcsim.DEBcali DEB_AS.in

```

```{r}
Names_AS_outputs <- c("Weight_Juv", "Weight_Adult", "Energy_Juv", "Energy_Adult", "Maturity_Juv", "Maturity_Adult", "Reproduction", "Organic_matter")

# df_AS_sim_T <- read_tsv(file.path(path_AS, paste0("Sobol_", Sobol_type,"_T.out"))) |> 
#   dplyr::select(-(1:(length(l_params_median)+1))) |> 
#   setNames(Names_AS_outputs)
# 
# df_AS_sim_noT <- read_tsv(file.path(path_AS, paste0("Sobol_", Sobol_type,".out"))) |> 
#   dplyr::select(-(1:(length(l_params_median)+1-4))) |> 
#   setNames(Names_AS_outputs)
# 
# df_Sobol_results_T <- f_AS_Sobol_index(df_AS_sim_T, Sobol_info)
# df_Sobol_results_noT <- f_AS_Sobol_index(df_AS_sim_noT, Sobol_info)
```
