```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# Case of isolated adults

The case of isolated adults was therefore explored only through simulations to investigate the resulting patterns of energy allocation in the absence of reproductive opportunities. Two alternative formulations were considered: (i) maintaining the juvenile allocation fraction throughout adulthood ($\kappa_J$), and (ii) introducing a transition toward the adult allocation fraction ($\kappa_A$) after maturation, as implemented for grouped adults.

## Load data

```{r}
path_fig   <- here::here("fig/DEB_Models")
path_files <- here::here("mod/Y_DEB_IsolatedAdultes")

col_experiment <- c(
  Nord_aurora[1], 
  Nord_aurora[2], 
  Nord_aurora[5]
  )

l_Experiments_IsolatedAdults <- c(
  "Bart2019_XP1_1",    
  "Bart2019_XP4_1",
  "Gollot2026_dens_D1"
  )

Adults_alone <- TRUE
OM_diff      <- TRUE

df_data_obs <- f_import_data_DEB(l_Experiments_IsolatedAdults, Adults_alone)
```

## Simulations

```{r setpointfullin}

# We use the tab_setpoint file produced by 
# the generation of the W.K.C.e model results

Nb_experiment <- length(l_Experiments_IsolatedAdults)
step_sim <- 0.05 # Must be small enough to not fail the integration

# We keep a limited set of times for the graphics
select_times <- seq(0,400, 0.1)

# Endpoints to simulate
Endpoints_print <- "Weight,
    Reproduction"

# List of the parameters in the same order as in the tab_setpoint
l_param_name <- c("Fm", "pAm", "r_pAm_pM", "v", 
                  "kapJ", "kapA", "Ehp", "E_coc", 
                  "rOM_ClxHorse", "K", "dv", "de", "tau", 
                  "Sigma_W")

# Generate the .in simulation files for MCSim

f_In_Setpoint_full(
  file.path(path_files, "kapJ"), l_Experiments_IsolatedAdults, 
  Adults_alone, OM_diff, 
  l_param_name, step_sim, Endpoints_print
  )

f_In_Setpoint_full(
  file.path(path_files, "kapA"), l_Experiments_IsolatedAdults, 
  Adults_alone, OM_diff, 
  l_param_name, step_sim, Endpoints_print
  )

```

```{bash, eval=F, execute=F}

# Put the tab_setpoint.out from the best model in each folder : 
# "mod/Y_DEB_IsolatedAdultes/kapA"
# "mod/Y_DEB_IsolatedAdultes/kapJ"

# Run the simulations

for j in $(seq 1 3); do
./mcsim.DEBcali_A DEB_setpoint_full_${j}.in
done

for j in $(seq 1 3); do
./mcsim.DEBcali_J DEB_setpoint_full_${j}.in
done
```

```{r, message=F, warning=F}

# Read results

file_rds_kapA <- file.path(file.path(path_files, "kapA"), paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_kapA)) {
  df_pred_full_kapA <- readRDS(file_rds_kapA)
} else {
  df_pred_full_kapA <- f_read_Setpoint_full(file.path(path_files, "kapA"), l_Experiments_IsolatedAdults, Adults_alone = TRUE, Nb_experiment, select_times, step_sim)
}

file_rds_kapJ <- file.path(file.path(path_files, "kapJ"), paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_kapJ)) {
  df_pred_full_kapJ <- readRDS(file_rds_kapJ)
} else {
  df_pred_full_kapJ <- f_read_Setpoint_full(file.path(path_files, "kapJ"), l_Experiments_IsolatedAdults, Adults_alone = TRUE, Nb_experiment, select_times, step_sim)
}

# Times where earthworm are first observed as adults
df_time_adult <- data.frame(
  ID_experiment = unique(df_data_obs$ID_experiment),
  Time_adult = c(98, 126, 84)
)

df_data_obs <- df_data_obs |> 
  left_join(df_time_adult) |> 
  mutate(
    Adult = case_when(
      Time >= Time_adult ~ "Yes",
      .default = "No"
    )
  )

# Type of model
df_pred_full_kapJ$kappa <- "J"
df_pred_full_kapA$kappa <- "A"

df_pred_full <- bind_rows(df_pred_full_kapJ, df_pred_full_kapA) |> 
  mutate(kappa = fct_relevel(kappa, c("J", "A")))

df_data_obs_kapJ <- df_data_obs |> mutate(kappa = "J")
df_data_obs_kapA <- df_data_obs |> mutate(kappa = "A")

df_data_obs_full <- bind_rows(df_data_obs_kapJ, df_data_obs_kapA) |> 
  mutate(kappa = fct_relevel(kappa, c("J", "A")))
```

```{r}
#| fig-cap: Predicted Weight for each experiment.
#| label: fig-predkapW
#| fig-height: 4
#| fig-width: 8

alpha_ribbon  <- 0.15
line_width    <- 1.1
point_stroke  <- 0.9
alpha_line    <- 0.7
wrap_nb_col   <- 2
size_subtitle <- 8

col_kappa <- c(Nord_frost[2], Nord_frost[4], Nord_frost[4])
col_data <- Nord_polar[4]

ID_exp_plot <- "Bart2019_XP1_1"

p_XP11 <- ggplot()+
  
  geom_ribbon(
    data = subset(df_pred_full, Endpt == "Weight" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = kappa
    ),
    alpha = alpha_ribbon
  )+
  
  geom_line(
    data = subset(df_pred_full, Endpt == "Weight" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      y = predict.endpoint,
      color = kappa
    ),
    linewidth = line_width,
    alpha = alpha_line
  )+
  
  geom_point(
    data = df_data_obs_full |> filter(ID_experiment == ID_exp_plot),    
    aes(  
      x = Time, 
      y = Weight, 
      alpha = Adult
    ),
    color = col_data,
    stroke = point_stroke
  )+
  
  scale_color_manual(
    name = "Kappa\nfor adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_fill_manual(
    name = "Kappa\nfor adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_alpha_manual(
    name = "Status",
    values = c(0.2, 0.7),
    labels = c("Juvenile", "Adult")
  )+
  labs(
    x = "Time (days)", 
    y = "Weight (g)",
    title = ID_exp_plot,
    subtitle = "Food: 3 g/ind/14d\nSoil: 400 g | T: 15°C"
  )+
  
  theme_minimal()+
  theme(
    plot.title = element_text(face="bold", size = 10),
    plot.subtitle = element_text(size = size_subtitle),
    legend.text = element_text(size = 11)
  )


ID_exp_plot <- "Bart2019_XP4_1"

p_XP41 <- ggplot()+
  
  geom_ribbon(
    data = subset(df_pred_full, Endpt == "Weight" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = kappa
    ),
    alpha = alpha_ribbon
  )+
  
  geom_line(
    data = subset(df_pred_full, Endpt == "Weight" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      y = predict.endpoint,
      color = kappa
    ),
    linewidth = line_width,
    alpha = alpha_line
  )+
  
  geom_point(
    data = df_data_obs_full |> filter(ID_experiment == ID_exp_plot),    
    aes(  
      x = Time, 
      y = Weight, 
      alpha = Adult
    ),
    color = col_data,
    stroke = point_stroke
  )+
  
  scale_color_manual(
    name = "Kappa\nfor adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_fill_manual(
    name = "Kappa\nfor adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_alpha_manual(
    name = "Status",
    values = c(0.2, 0.7),
    labels = c("Juvenile", "Adult")
  )+
  labs(
    x = "Time (days)", 
    y = "Weight (g)",
    title = ID_exp_plot,
    subtitle = "Food: 1 g/ind/14d\nSoil: 400 g | T: 15°C"
  )+
  
  theme_minimal()+
  theme(
    plot.title = element_text(face="bold", size = 10),
    plot.subtitle = element_text(size = size_subtitle),
    legend.text = element_text(size = 11)
  )

ID_exp_plot <- "Gollot2026_dens_D1"

p_D1 <- ggplot()+
  
  geom_ribbon(
    data = subset(df_pred_full, Endpt == "Weight" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = kappa
    ),
    alpha = alpha_ribbon
  )+
  
  geom_line(
    data = subset(df_pred_full, Endpt == "Weight" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      y = predict.endpoint,
      color = kappa
    ),
    linewidth = line_width,
    alpha = alpha_line
  )+
  
  geom_point(
    data = df_data_obs_full |> filter(ID_experiment == ID_exp_plot),    
    aes(  
      x = Time, 
      y = Weight, 
      alpha = Adult
    ),
    color = col_data,
    stroke = point_stroke
  )+
  
  scale_color_manual(
    name = "Kappa\nfor adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_fill_manual(
    name = "Kappa\nfor adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_alpha_manual(
    name = "Status",
    values = c(0.2, 0.7),
    labels = c("Juvenile", "Adult")
  )+
  labs(
    x = "Time (days)", 
    y = "Weight (g)",
    title = ID_exp_plot,
    subtitle = "Food: 3 g/ind/14d\nSoil: 200 g | T: 18°C"
  )+
  
  theme_minimal()+
  theme(
    plot.title = element_text(face="bold", size = 10),
    plot.subtitle = element_text(size = size_subtitle),
    legend.text = element_text(size = 11)
  )

pW <- p_XP11 + p_XP41 + p_D1 + 
  plot_layout(ncol=3, guides = "collect")
pW
```

```{r savetrajW, include = F}
ggsave(
  filename = "Y_IsolatedAdults_trajW.png",
  plot = pW,
  width = 8, height = 4,
  path = path_fig
)
```

```{r}
#| fig-cap: Predicted Reproduction for each experiment.
#| label: fig-predkapR
#| fig-height: 4
#| fig-width: 8

alpha_ribbon <- 0.15
line_width   <- 1.1
point_stroke <- 0.9
alpha_line   <- 0.7
wrap_nb_col  <- 2

col_kappa <- c(Nord_frost[2], Nord_frost[4])
col_data <- Nord_polar[4]

ID_exp_plot <- "Bart2019_XP1_1"

p_XP11 <- ggplot()+
  
  geom_ribbon(
    data = subset(df_pred_full, Endpt == "Reproduction" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = kappa
    ),
    alpha = alpha_ribbon
  )+
  
  geom_line(
    data = subset(df_pred_full, Endpt == "Reproduction" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      y = predict.endpoint,
      color = kappa
    ),
    linewidth = line_width,
    alpha = alpha_line
  )+
  
  geom_point(
    data = df_data_obs_full |> filter(ID_experiment == ID_exp_plot),    
    aes(  
      x = Time, 
      y = Reproduction, 
      alpha = Adult
    ),
    color = col_data,
    stroke = point_stroke
  )+
  
  scale_color_manual(
    name = "Kappa for adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_fill_manual(
    name = "Kappa for adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_alpha_manual(
    name = "Status",
    values = c(0.2, 0.7),
    labels = c("Juvenile", "Adult")
  )+
  labs(
    x = "Time (days)", 
    y = "Reproduction (#)",
    title = ID_exp_plot
  )+
  
  theme_minimal()+
  theme(
    plot.title = element_text(face="bold", size = 10),
    legend.text = element_text(size = 11)
  )


ID_exp_plot <- "Bart2019_XP4_1"

p_XP41 <- ggplot()+
  
  geom_ribbon(
    data = subset(df_pred_full, Endpt == "Reproduction" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = kappa
    ),
    alpha = alpha_ribbon
  )+
  
  geom_line(
    data = subset(df_pred_full, Endpt == "Reproduction" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      y = predict.endpoint,
      color = kappa
    ),
    linewidth = line_width,
    alpha = alpha_line
  )+
  
  geom_point(
    data = df_data_obs_full |> filter(ID_experiment == ID_exp_plot),    
    aes(  
      x = Time, 
      y = Reproduction, 
      alpha = Adult
    ),
    color = col_data,
    stroke = point_stroke
  )+
  
  scale_color_manual(
    name = "Kappa for adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_fill_manual(
    name = "Kappa for adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_alpha_manual(
    name = "Status",
    values = c(0.2, 0.7),
    labels = c("Juvenile", "Adult")
  )+
  labs(
    x = "Time (days)", 
    y = "Reproduction (#)",
    title = ID_exp_plot
  )+
  
  theme_minimal()+
  theme(
    plot.title = element_text(face="bold", size = 10),
    legend.text = element_text(size = 11)
  )

ID_exp_plot <- "Gollot2026_dens_D1"

p_D1 <- ggplot()+
  
  geom_ribbon(
    data = subset(df_pred_full, Endpt == "Reproduction" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = kappa
    ),
    alpha = alpha_ribbon
  )+
  
  geom_line(
    data = subset(df_pred_full, Endpt == "Reproduction" & ID_experiment == ID_exp_plot),
    aes(
      x = Time,
      y = predict.endpoint,
      color = kappa
    ),
    linewidth = line_width,
    alpha = alpha_line
  )+
  
  geom_point(
    data = df_data_obs_full |> filter(ID_experiment == ID_exp_plot),    
    aes(  
      x = Time, 
      y = Reproduction, 
      alpha = Adult
    ),
    color = col_data,
    stroke = point_stroke
  )+
  
  scale_color_manual(
    name = "Kappa for adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_fill_manual(
    name = "Kappa for adults",
    labels = expression(kappa[J], kappa[A]),
    values = col_kappa
  )+
  scale_alpha_manual(
    name = "Status",
    values = c(0.2, 0.7),
    labels = c("Juvenile", "Adult")
  )+
  labs(
    x = "Time (days)", 
    y = "Reproduction (#)",
    title = ID_exp_plot
  )+
  
  theme_minimal()+
  theme(
    plot.title = element_text(face="bold", size = 10),
    legend.text = element_text(size = 11)
  )

pR <- p_XP11 + p_XP41 + p_D1 + 
  plot_layout(ncol=3, guides = "collect")
pR
```

```{r savetrajR, include = F}
ggsave(
  filename = "Y_IsolatedAdults_trajR.png",
  plot = pR,
  width = 8, height = 4,
  path = path_fig
)
```

The formulation maintaining the juvenile allocation fraction throughout adulthood ($\kappa_J$) reproduced the observed growth trajectories of isolated adults more accurately than the formulation including a transition toward the adult allocation fraction ($\kappa_A$), which systematically underestimated growth after maturation (@fig-predkapW). This result suggests that isolated adults maintain growth patterns closer to those of juveniles than to those of grouped reproducing adults.

However, despite the absence of observed cocoon production in isolated adults, both formulations still predicted a non-zero allocation of energy toward reproduction after maturation (@fig-predkapR). This discrepancy indicates that the energetic fate of the reproductive flux remains inadequately represented in the current model formulations and must be further investigated.
