```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# Data and adjustments

## Available data

Toxicodynamic calibration of the DEB-TKTD models relies on experimental data previously reported in @gollot_2026 presented [here](https://lisagllt.github.io/Ew-Mix-TD/quarto/B_TD_Single/BB_Effect_single.html). The dataset includes juvenile growth, adult growth, and cocoon production under single-substance exposure conditions for epoxiconazole and imidacloprid, while mixture reproduction data are retained for subsequent model evaluation rather than parameter calibration.

To remain consistent with the deterministic formulation of the DEB model and previous calibration procedures, observed responses are aggregated as mean values at the treatment-condition level before model fitting. This aggregation reduces the influence of inter-individual variability and experimental noise while preserving treatment-level temporal trajectories relevant to DEB processes.

```{r, warning=F, message=FALSE}
# Import data
df_data_obs <- f_import_data_DEBTKTD()
df_data_obs_EPX <- df_data_obs |>
  filter(Molecule == "EPX")
df_data_obs_IMD <- df_data_obs |>
  filter(Molecule == "IMD")

####### EPX ########################

# Generate labels for each conditions
Condition_order <- c(
  "Control", "C1", "C2", "C3", "C4", "C5",
  "C6", "C7", "C8"
)

df_Exp_type_Dose_Condition_G <- df_data_obs_EPX |>
  filter(Experiment_type == "Growth") |>
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |>
  distinct() |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

df_Exp_type_Dose_Condition_R <- df_data_obs_EPX |>
  filter(Experiment_type == "Repro") |>
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |>
  distinct() |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

ID_levels_growth <- df_Exp_type_Dose_Condition_G |>
  filter(Experiment_type == "Growth") |>
  arrange(Condition) |>
  pull(ID_experiment)

Facet_levels_growth <- df_Exp_type_Dose_Condition_G |>
  filter(Experiment_type == "Growth") |>
  arrange(Condition) |>
  mutate(Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg")) |>
  pull(Facet_label)

ID_levels_repro <- df_Exp_type_Dose_Condition_R |>
  filter(Experiment_type == "Repro") |>
  arrange(Condition) |>
  pull(ID_experiment)

Facet_levels_repro <- df_Exp_type_Dose_Condition_R |>
  filter(Experiment_type == "Repro") |>
  arrange(Condition) |>
  mutate(Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg")) |>
  pull(Facet_label)

# Data from juvenile growth experiment
df_data_obs_EPX_G <- df_data_obs_EPX |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

# Data from adult reproduction experiment
df_data_obs_EPX_R <- df_data_obs_EPX |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  ) |>
  filter(!(Time == 14))

###### IMD ############################

# Generate labels for each conditions
Condition_order <- c(
  "Control", "C1", "C2", "C3", "C4", "C5",
  "C6", "C7", "C8", "C9", "C10"
)

df_Exp_type_Dose_Condition_G <- df_data_obs_IMD |>
  filter(Experiment_type == "Growth") |>
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |>
  distinct() |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

df_Exp_type_Dose_Condition_R <- df_data_obs_IMD |>
  filter(Experiment_type == "Repro") |>
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |>
  distinct() |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

ID_levels_growth <- df_Exp_type_Dose_Condition_G |>
  filter(Experiment_type == "Growth") |>
  arrange(Condition) |>
  pull(ID_experiment)

Facet_levels_growth <- df_Exp_type_Dose_Condition_G |>
  filter(Experiment_type == "Growth") |>
  arrange(Condition) |>
  mutate(Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg")) |>
  pull(Facet_label)

ID_levels_repro <- df_Exp_type_Dose_Condition_R |>
  filter(Experiment_type == "Repro") |>
  arrange(Condition) |>
  pull(ID_experiment)

Facet_levels_repro <- df_Exp_type_Dose_Condition_R |>
  filter(Experiment_type == "Repro") |>
  arrange(Condition) |>
  mutate(Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg")) |>
  pull(Facet_label)

# Data from juvenile growth experiment
df_data_obs_IMD_G <- df_data_obs_IMD |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

# Data from adult reproduction experiment
df_data_obs_IMD_R <- df_data_obs_IMD |>
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose / 1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  ) |>
  filter(!(Time == 14))
```

::: panel-tabset
## IMD

```{r, echo=F, message=F, warning=F}
#| fig-cap: Available data on the toxicity of imidacloprid on earthworm growth and reproduction.
#| label: fig-DataIMD
#| fig-height: 12
#| fig-width: 12

# Plot
alpha_ribbon <- 0.15
line_width <- 1.1
point_stroke <- 0.9
alpha_line <- 0.7
wrap_nb_col <- 2
point_size <- 2

col_exp1 <- c(
  Nord_aurora[4],
  rev(nord("aurora", 12)[1:10])
)
col_experiment <- rep(col_exp1, 2)

pW_G_IMD <- ggplot(
  data = subset(df_data_obs_IMD_G, Experiment_type == "Growth"),
  mapping =
    aes(
      x = Time,
      y = Weight,
      color = ID_experiment
    )
) +
  geom_point(
    alpha = 0.7,
    stroke = point_stroke,
    size = point_size
  ) +
  geom_line() +
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  scale_fill_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  facet_wrap(
    ~Facet_label,
    ncol = wrap_nb_col
  ) +
  labs(
    x = "Time (days)",
    y = "Weight (g)",
    title = "Effect of imidacloprid on juvenile growth"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

pW_R_IMD <- ggplot(
  data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),
  mapping =
    aes(
      x = Time,
      y = Weight,
      color = ID_experiment
    )
) +
  geom_point(
    alpha = 0.7,
    stroke = point_stroke,
    size = point_size
  ) +
  geom_line() +
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  scale_fill_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  facet_wrap(
    ~Facet_label,
    ncol = wrap_nb_col
  ) +
  labs(
    x = "Time (days)",
    y = "Weight (g)",
    title = "Effect of imidacloprid on adult growth"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

pR_R_IMD <- ggplot(
  data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),
  mapping =
    aes(
      x = Time,
      y = Reproduction,
      color = ID_experiment
    )
) +
  geom_point(
    alpha = 0.7,
    stroke = point_stroke,
    size = point_size
  ) +
  geom_line() +
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  scale_fill_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  facet_wrap(
    ~Facet_label,
    ncol = wrap_nb_col
  ) +
  labs(
    x = "Time (days)",
    y = "Cumulated reproduction (#)",
    title = "Effect of imidacloprid on reproduction"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

p_WR_summary_IMD <- pW_G_IMD + pW_R_IMD + pR_R_IMD +
  plot_layout(ncol = 3)
p_WR_summary_IMD

```

## EPX

```{r, echo=F, message=F, warning=F}
#| fig-cap: Available data on the toxicity of epoxiconazole on earthworm growth and reproduction.
#| label: fig-DataEPX
#| fig-height: 10
#| fig-width: 12

# Plot
alpha_ribbon <- 0.15
line_width <- 1.1
point_stroke <- 0.9
alpha_line <- 0.7
wrap_nb_col <- 2
col_exp1 <- c(
  Nord_aurora[4],
  rev(nord("aurora", 12)[1:10])
)

col_experiment <- rep(col_exp1, 2)

pW_G_EPX <- ggplot(
  data = subset(df_data_obs_EPX_G, Experiment_type == "Growth"),
  mapping =
    aes(
      x = Time,
      y = Weight,
      color = ID_experiment
    )
) +
  geom_point(
    alpha = 0.7,
    stroke = point_stroke,
    size = point_size
  ) +
  geom_line() +
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  scale_fill_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  facet_wrap(
    ~Facet_label,
    ncol = wrap_nb_col
  ) +
  labs(
    x = "Time (days)",
    y = "Weight (g)",
    title = "Effect of epoxiconazole on juvenile growth"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

pW_R_EPX <- ggplot(
  data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),
  mapping =
    aes(
      x = Time,
      y = Weight,
      color = ID_experiment
    )
) +
  geom_point(
    alpha = 0.7,
    stroke = point_stroke,
    size = point_size
  ) +
  geom_line() +
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  scale_fill_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  facet_wrap(
    ~Facet_label,
    ncol = wrap_nb_col
  ) +
  labs(
    x = "Time (days)",
    y = "Weight (g)",
    title = "Effect of epoxiconazole on adult growth"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

pR_R_EPX <- ggplot(
  data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),
  mapping =
    aes(
      x = Time,
      y = Reproduction,
      color = ID_experiment
    )
) +
  geom_point(
    alpha = 0.7,
    stroke = point_stroke,
    size = point_size
  ) +
  geom_line() +
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  scale_fill_manual(
    name = "Experiments",
    values = col_experiment
  ) +
  facet_wrap(
    ~Facet_label,
    ncol = wrap_nb_col
  ) +
  labs(
    x = "Time (days)",
    y = "Cumulated reproduction (#)",
    title = "Effect of epoxiconazole on reproduction"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

p_WR_summary_EPX <- pW_G_EPX + pW_R_EPX + pR_R_EPX +
  plot_layout(ncol = 3)
p_WR_summary_EPX

```
:::

## Adjustment of the DEB model

### Relationship between W, Eh and E for juveniles

The juvenile growth experiments were conducted with juvenile individuals housed individually in cosms containing 200 g of Closeaux soil, maintained at 18°C, and fed 3 g of horse dung per individual every 14 days. Individuals were exposed to a range of concentrations of either imidacloprid or epoxiconazole. In the DEB-TKTD model, the initial maturity of these individuals must be specified, although it was not and can not be directly measured. We therefore use a proxy based on the relationship between predicted body mass and predicted maturity obtained from the DEB model for the Gollot2026_dens_D5 experiment, which was conducted under the same experimental conditions as the culture from which these earthworms came from.

```{r}
# Put the selected model in this folder :
path_D_CWKe <- here::here("mod/D_DEB_CWKe/WEh_relationship")

# Put also the MCMC .in, .out, .out.kernel and the tab_setpoint 
# files generated with the best model results

# Get results

MCMC_out_D_CWKe <- f_MCSim(path_D_CWKe)
L_parameters_D_CWKe <- unique(MCMC_out_D_CWKe$Priors$Nom)

Summary_res_D_CWKe <-
  as.data.frame(MCMC_out_D_CWKe$Summary_res)[1:length(L_parameters_D_CWKe)] |>
  mutate(Model = "D_CWKe")

# Run the simulations with the new parameter values

Nb_experiment <- 1
step_sim <- 0.05 # Must be small enough to not fail the integration

# Selection of a limited set of times for graphics
select_times <- seq(0, 400, 0.1)

Endpoints_print <- "Weight,
    Maturity,
    Energy"

# Used experiment
l_Experiment_D5 <- c("Gollot2026_dens_D5")

l_param_name_D_CWKe <- names(Summary_res_D_CWKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

# Generation of the .in files for simulations
f_In_Setpoint_full(
  path_D_CWKe, l_Experiment_D5,
  Adults_alone = FALSE, OM_diff = TRUE,
  l_param_name_D_CWKe, step_sim, Endpoints_print
)

# Run simulations in MCSim
# ./mcsim.DEBcali DEB_setpoint_full_1.in

# Read simulations results

file_rds_D_CWKe <- file.path(path_D_CWKe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_D_CWKe)) {
  df_pred_full_D_CWKe <- readRDS(file_rds_D_CWKe)
} else {
  df_pred_full_D_CWKe <- f_read_Setpoint_full(path_D_CWKe, Adults_alone = FALSE, l_Experiment_D5, Nb_experiment, select_times, step_sim, bol_Eh = TRUE)
}

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe |>
  pivot_wider(
    id_cols = Time,
    names_from = Endpt,
    values_from = predict.endpoint
  )

```

```{r}

# Linear model for the relationship btw Weight and Maturity

mod_RWEh <- lm(
  Maturity ~ Weight + I(Weight^2),
  data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.5)
)
# This model is run only for Weights < 0.5 because 
# we need the relatioship for juveniles only

summary(mod_RWEh)

c <- coef(mod_RWEh)[["(Intercept)"]]
b <- coef(mod_RWEh)[["Weight"]]
a <- coef(mod_RWEh)[["I(Weight^2)"]]

equation <- paste0(
  "Maturity = ", round(a, 3), " Weight² + ",
  round(b, 3), " Weight + ",
  round(c, 3)
)

equation
```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Relationship between weight and maturity in the Gollot2026_dens_D5 experiment.
#| label: fig-RWEhD5
#| fig-height: 4
#| fig-width: 6

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe_wide |>
  mutate(
    Maturity_pred = predict(
      mod_RWEh, 
      newdata = df_pred_full_D_CWKe_wide
      )
    )

col_mod <- Nord_frost[4]

p <- ggplot() +
  geom_line(
    data = df_pred_full_D_CWKe_wide,
    aes(
      x = Weight,
      y = Maturity
    ),
    linewidth = 2,
    linetype = "dotted",
    color = Nord_polar[1]
  )+
  geom_line(
    data = df_pred_full_D_CWKe_wide,
    aes(
      x = Weight,
      y = Maturity_pred
    ),
    color = col_mod,
    linewidth = 1
  )+
  labs(
    x = "Weight (g)",
    y = "Maturity (J)",
    title = "Relationship between Weight and Maturity",
    subtitle = equation,
    caption = "Experiment : Gollot2026_dens_D5"
  )+
  theme_minimal()+
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = col_mod)
  )

p

```

As the initial weight in this dataset range from 0.055 to 0.141 g, a relationship established for weights under 0.5 g is enough.

For the initialisation of the energy in the reserve, we assume individuals were well fed in the culture and therefore the energy can be assumed to equal Em at the start of the experiment.

### Re-estimations of $\{\dot{p}_{Am}\}$, $E_{coc}$ and $\kappa_A$

DEB parameter values were initially fixed at the modes of their posterior distributions obtained during the original model calibration (@sec-DEB). Because discrepancies were observed between model predictions and the control data from the single-substance experiments, three DEB parameters associated with the biological processes requiring adjustment were recalibrated: the maximum surface-area-specific assimilation rate, $\{\dot p_{Am}\}$, the cocoon energy content, $E_{coc}$, and the adult allocation fraction, $\kappa_A$. These parameters were selected based on their mechanistic relationships with the affected responses, while limiting the number of re-estimated parameters to preserve identifiability. Prior distributions were defined within $\pm 30%$ of the values obtained during the initial DEB calibration. The posterior mode estimates of $\{\dot p_{Am}\}$, $E_{coc}$, and $\kappa_A$ were subsequently fixed during the calibration of the DEB-TKTD models.

```{r, warning=F, message=F}
path_fig <- here::here("fig/DEBTKTD_Models")

# Put the best model file in this folder with the estimated
# parameter values from the DEB part
# Put also the tab_setpoint file generated 
# and rename it as tab_setpoint_old_raw.out
path_DEB_refit <- here::here("mod/Z_DEB-TKTD/DEB_refit")

# Run the MCMC chains with the control individuals
# ./mcsim.DEBcali DEB_TKTD_C1.in

# Read results

MCMC_out_DEB_refit        <- f_MCSim(path_DEB_refit)

NC_DEB_refit              <- MCMC_out_DEB_refit$NC
Nb_param_DEB_refit        <- MCMC_out_DEB_refit$Nb_param
Nb_experiment_DEB_refit   <- MCMC_out_DEB_refit$Nb_experiment
Nb_iter_kept_DEB_refit    <- MCMC_out_DEB_refit$Nb_iter_kept
N_iter_setpoint_DEB_refit <- MCMC_out_DEB_refit$N_iter_setpoint
L_parameters_DEB_refit    <- unique(MCMC_out_DEB_refit$Priors$Nom)

Summary_res_DEB_refit <-
  as.data.frame(MCMC_out_DEB_refit$Summary_res)[1:length(L_parameters_DEB_refit)] |>
  mutate(Model = "DEB_refit")

Summary_res_DEB_refit

```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_DEB_refit
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_DEB_refit)
p_chains
  
```

```{r savechainsDEBrefit, include = F}
ggsave(
  filename="DEB_refit_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_DEB_refit
#| fig-height: 8
#| fig-width: 8

gelman <- f_Plot_Convergence(MCMC_out_DEB_refit)
print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corrDEBrefitipairs
#| fig-height: 5
#| fig-width: 6

file_rds <- here::here("fig/DEBTKTD_Models/DEB_refit_ipairs_plot.png")
f_Plot_ipairs(MCMC_out_DEB_refit, file_rds, 1)

```

```{r, include = F}

col_corr <- colorRampPalette(c(
  "#BF616A",  # corrélations négatives
  "white",
  "#5E81AC"   # corrélations positives
))(200)

params_keep <- c("pAm.1.", "E_coc.1.", "kapA.1.")

mcmc_list_corr_DEB_refit <- f_mcmc_list_corr(MCMC_out_DEB_refit)

df_corr_DEB_refit <- cor(as.matrix(mcmc_list_corr_DEB_refit)[, params_keep])

dimnames(df_corr_DEB_refit) <- lapply(
  dimnames(df_corr_DEB_refit),
  \(x) gsub("\\.1\\.$", "", x)
)

png(file.path(path_fig, "DEB_refit_corrplot_article.png"), width = 2000, height = 2000, res = 300)

op <- par(font = 2)

corrplot.mixed(
  df_corr_DEB_refit,
  lower = "ellipse",
  upper = "number",
  tl.col = "#2E3440",
  tl.cex = 0.6,
  tl.pos = "d",
  number.cex = 0.7,
  tl.srt = 45,
  lower.col = col_corr,
  upper.col = col_corr
)

par(op)

dev.off()

```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_DEB_refit
#| fig-height: 6
#| fig-width: 8

p_post <- f_Plot_Posteriors(MCMC_out_DEB_refit)
p_post
```

```{r savepostDEBrefit, include = F}
ggsave(
  filename="DEB_refit_post.png", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig
  )
```

```{r tabsetold}

# We only need the tab_setpoint_old_raw.out for the re-estimated parameters 
# to be able to compare the old and the new parameter values.

path_DEB_refit <- here::here("mod/Z_DEB-TKTD/DEB_refit")

df_tab_setpoint_old_raw <- f_Read_fichier2(
  file.path(path_DEB_refit, "tab_setpoint_old_raw.out")
  )

df_tab_setpoint_old <- df_tab_setpoint_old_raw |>
  dplyr::select(c("pAm.1.", "kapA.1.", "E_coc.1.")) |>
  mutate(
    Iter = dplyr::row_number(), .before = 1
  )

entete <- paste(names(df_tab_setpoint_old)[-1], collapse = " ")

lignes <- apply(
  df_tab_setpoint_old,
  1,
  function(x) paste(x, collapse = " ")
)

writeLines(
  c(entete, lignes),
  con = file.path(path_DEB_refit, "tab_setpoint_old.out"),
  useBytes = TRUE
)

```

```{r simDEBrefit, results=FALSE, message=F}

# Run the simulations with the control individuals for both 
# the old and the new values

# ./mcsim.DEBcali DEB_setpoint_full_new_1.in
# ./mcsim.DEBcali DEB_setpoint_full_new_2.in
# 
# ./mcsim.DEBcali DEB_setpoint_full_old_1.in
# ./mcsim.DEBcali DEB_setpoint_full_old_2.in

step_sim <- 0.05
max_time <- 28

df_pred_old <- f_Read_setpoint_DEB_refit(path_DEB_refit, step_sim, max_time, "old")
df_pred_new <- f_Read_setpoint_DEB_refit(path_DEB_refit, step_sim, max_time, "new")

df_pred_old_G <- df_pred_old |>
  filter(Endpt == "Weight") |>
  mutate(
    Name_experiment = factor(case_when(
      No_sim == 1 ~ "Juveniles controles",
      No_sim == 2 ~ "Adult controles",
    ), c("Juveniles controles", "Adult controles")),
    DEB_type = "Old"
  )

df_pred_new_G <- df_pred_new |>
  filter(Endpt == "Weight") |>
  mutate(
    Name_experiment = factor(case_when(
      No_sim == 1 ~ "Juveniles controles",
      No_sim == 2 ~ "Adult controles",
    ), c("Juveniles controles", "Adult controles")),
    DEB_type = "New"
  )

df_pred_old_R <- df_pred_old |>
  filter(Endpt == "Reproduction") |>
  filter(No_sim == 2) |>
  mutate(
    Name_experiment = factor(case_when(
      No_sim == 1 ~ "Juveniles controles",
      No_sim == 2 ~ "Adult controles",
    ), c("Juveniles controles", "Adult controles")),
    DEB_type = "Old"
  )
df_pred_new_R <- df_pred_new |>
  filter(Endpt == "Reproduction") |>
  filter(No_sim == 2) |>
  mutate(
    Name_experiment = factor(case_when(
      No_sim == 1 ~ "Juveniles controles",
      No_sim == 2 ~ "Adult controles",
    ), c("Juveniles controles", "Adult controles")),
    DEB_type = "New"
  )

df_pred_G <- rbind(df_pred_old_G, df_pred_new_G)
df_pred_R <- rbind(df_pred_old_R, df_pred_new_R)


df_data_Ctrl <- f_import_data_DEBTKTD() |>
  filter(Condition == "Ctrl" & Molecule == "IMD") |>
  mutate(
    No_sim = case_when(
      Molecule == "IMD" & Experiment_type == "Growth" ~ 1,
      Molecule == "IMD" & Experiment_type == "Repro" ~ 2
    )
  ) |>
  mutate(
    Name_experiment = factor(case_when(
      No_sim == 1 ~ "Juveniles controles",
      No_sim == 2 ~ "Adult controles",
    ), c("Juveniles controles", "Adult controles"))
  )

```

```{r, warning=F, message=F}
#| fig-cap: Observed growth and reproduction responses of control *Aporrectodea caliginosa* and corresponding predictions from the baseline DEB model before and after parameter recalibration. Points represent experimental treatment means. The original trajectories were generated using the posterior mode parameter values from the initial DEB calibration, whereas the recalibrated trajectories used the newly estimated values of the allocation energy fraction to soma in adults ($\kappa_A$).
#| label: fig-refitrib
#| fig-height: 4
#| fig-width: 8

alpha_ribbon <- 0.2

pW <- ggplot() +
  geom_ribbon(
    data = df_pred_G,
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = DEB_type
    ),
    alpha = alpha_ribbon
  ) +
  geom_line(
    data = df_pred_G,
    aes(
      x = Time,
      y = predict.endpoint,
      color = DEB_type
    )
  ) +
  geom_point(
    data = df_data_Ctrl,
    aes(
      x = Time,
      y = Weight
    ),
    color = Nord_polar[1]
  ) +
  scale_color_manual(values = c(Nord_frost[4], Nord_frost[2]), name = "DEB") +
  scale_fill_manual(values = c(Nord_frost[4], Nord_frost[2]), name = "DEB") +
  facet_wrap(~Name_experiment) +
  labs(
    x = "Time (days)", 
    y = "Weight (g)"
    ) +
  theme_minimal() +
  theme(
    strip.text = element_text(face = "bold")
  )

pR <- ggplot() +
  geom_ribbon(
    data = df_pred_R,
    aes(
      x = Time,
      ymax = up,
      ymin = low,
      fill = DEB_type
    ),
    alpha = alpha_ribbon
  ) +
  geom_line(
    data = df_pred_R,
    aes(
      x = Time,
      y = predict.endpoint,
      color = DEB_type
    )
  ) +
  geom_point(
    data = df_data_Ctrl |> filter(Name_experiment == "Adult controles"),
    aes(
      x = Time,
      y = Reproduction
    ),
    color = Nord_polar[1]
  ) +
  scale_color_manual(values = c(Nord_frost[4], Nord_frost[2]), name = "DEB") +
  scale_fill_manual(values = c(Nord_frost[4], Nord_frost[2]), name = "DEB") +
  facet_wrap(~Name_experiment) +
  labs(
    x = "Time (days)",
    y = "Reproduction (#)"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(face = "bold")
  )

p <- pW + pR +
  plot_layout(
    ncol = 2,
    guides = "collect",
    widths = c(2, 1)
  )
p

```

```{r saveRefit, include = F}
ggsave(
  filename="DEB_refit.png", 
  plot=p, 
  width=8, height = 4, 
  path=path_fig
  )
```

Predictions obtained with the original DEB parameterization showed a slight underestimation of both juvenile and adult growth, together with an overestimation of cocoon production (@fig-refitrib). To improve the description of the control trajectories before estimating toxicodynamic effects, three DEB parameters were therefore re-estimated: the maximum surface-area-specific assimilation rate, $\{\dot{p}_{Am}\}$, the cocoon energy content, $E_{coc}$, and the adult allocation fraction, $\kappa_A$.

The posterior mode of $\{\dot{p}_{Am}\}$ increased from 259.9 \[234.8 ; 285.7\] to 341.8 \[267.5; 377.2\] J$\cdot$cm$^{-2}\cdot$d$^{-1}$, while $E_{coc}$ increased from 57.8 \[51.2 ; 70.0\] to 75.0 \[51.8; 114.2\] J. The posterior mode of $\kappa_A$ also increased slightly, from 0.71 \[0.63 ; 0.76\] to 0.73 \[0.69; 0.77\]. The substantial overlap between the original and recalibrated credible intervals indicates that the updated estimates remained broadly consistent with the initial DEB parameterization. The posterior correlation between the parameters was weak, indicating that the parameters were estimated independently (@fig-corrDEBrefitipairs).

Using the recalibrated parameter values improved the agreement between predicted and observed juvenile and adult growth trajectories. Reproduction was also more closely reproduced than with the original parameterization, although cocoon production remained slightly overestimated. However, the recalibration also resulted in wider 95% credible intervals, indicating greater uncertainty in the predicted responses. The posterior mode estimates of $\{\dot{p}_{Am}\}$, $E_{coc}$, and $\kappa_A$ were nevertheless retained and fixed for all subsequent DEB-TKTD analyses.

## Construction of the DEB-TKTD models

### Toxicokinetic models

Internal concentrations of epoxiconazole and imidacloprid are simulated using previously developed toxicokinetic models (more details [here](https://lisagllt.github.io/Ew-Mix-TK/)). For both compounds, two-compartment TK formulations were retained and parameterized using the median of posterior parameter distributions estimated from dedicated bioaccumulation experiments. External exposure concentrations corresponded to analytically measured soil concentrations rather than nominal concentrations. The TK models were originally calibrated under nominal exposure conditions of 100 ng.g$^{-1}$ dry soil for imidacloprid and 1000 ng.g$^{-1}$ dry soil for epoxiconazole.

Because previous toxicokinetic analyses found no evidence for mixture-related TK interactions between epoxiconazole and imidacloprid, single-substance TK models are used unchanged to simulate internal concentrations under co-exposure scenarios. Consequently, each compound is assumed to follow independent uptake and elimination dynamics in mixture conditions.

Previous toxicokinetic analyses identified concentration-dependent deviations for imidacloprid, with evidence of saturation occurring at internal concentrations around 1676 ng.g$^{-1}$. Under the original first-order formulation, this saturation implied a restricted application domain, corresponding to external concentrations below approximately 80 ng.g$^{-1}$ dry soil assuming a bioaccumulation factor of 21. However, because several exposure concentrations used in the toxicity experimental data exceeded the external concentration range over which the initial TK model could be applied, this saturation process is explicitly incorporated into the imidacloprid toxicokinetic module. The TK model for imidacloprid is therefore modified to account for a plateau in internal concentrations at high exposure levels, preventing unrealistic linear increases in internal exposure beyond the observed saturation range. This extended formulation is used for all imidacloprid-related simulations and parameter inferences in the DEB-TKTD model.

### Toxicodynamic model and physiological modes of action

Toxicodynamic processes is modeled following a standard DEB-TKTD formulation in which internal concentrations generate a damage variable that translates into physiological stress affecting DEB energetic fluxes [@jager_2006; @baas_2018; @jager_2023] (@eq-chap4TKTD). Because no toxicokinetic interactions are assumed, separate damage dynamics are modeled for epoxiconazole and imidacloprid, each compound being characterized by its own toxicodynamic parameters.

$$
\begin{aligned}
\frac{\mathrm d D}{\mathrm d t} &= k_r (C_{\mathrm{int}} - D) \\ \\
s &= b(D−c_0)
\end{aligned}
$$ {#eq-chap4TKTD}

\noindent with :

-   $C_{\mathrm{int}}$ : the internal concentration,
-   $D$ : the internal damage scaled in the same unit as $C_{\mathrm{int}}$,
-   $k_r$ : Recuperation or repair constant of damage.\$,
-   $s$ : the stress factor,
-   $b$ : damage sensitivity ($b = 1/c_T$ with $c_T$ the tolerance concentration),
-   $c_0$ : the no-effect concentration.

To reduce parameter identifiability issues, the damage recovery constant ($k_r$) was fixed to 1, so that damage instantaneously followed the internal concentration ($D=C_{\mathrm{int}}$).

For each pesticide, multiple physiological modes of action (pMoA) are evaluated individually by allowing toxic stress to alter different DEB processes, including assimilation, maintenance, growth, maturation, and reproduction (@tbl-chap4pMoA).

| Physiological mode of action (pMoA) | Affected parameters | Effect on parameters |
|----|----|----|
| Ingestion and/or assimilation | $\{\dot{p}_{Am}\}$: Surface-area-specific assimilation flux (J d$^{-1}$ cm$^{-2}$) | $\{\dot{p}_{Am}\} \rightarrow (1-s)\{\dot{p}_{Am}\}$ |
|  | or |  |
|  | $f$: Functional response (-) | $f \rightarrow f_0 \max(0,1-s)$ |
| Maintenance costs | $[\dot{p}_M]$: Volume-specific somatic maintenance flux (J d$^{-1}$ cm$^{-3}$) | $[\dot{p}_M] \rightarrow (1+s)[\dot{p}_M]$ |
|  | $\dot{k}_J$: Maturity maintenance rate coefficient (d$^{-1}$) | $\dot{k}_J \rightarrow (1+s)\dot{k}_J$ |
| Growth and maturity costs | $E_G$: Volume-specific cost of structure (J g$^{-1}$) | $E_G \rightarrow (1+s)E_G$ |
|  | $\kappa_H$: Maturation efficiency (= 1 in the standard DEB model) | $\kappa_H \rightarrow \kappa_H/(1+s)$ |
| Reproduction costs | $\kappa_R$: Reproduction efficiency | $\kappa_R \rightarrow \kappa_R/(1+s)$ |
| Embryo damage | $\kappa_R$: Reproduction efficiency | $\kappa_R \rightarrow \exp(-s)\kappa_R$ |

: **Accounting for the different possible physiological modes of action in a DEB model.** The stress factor $s$ is defined as a linear threshold damage function based on a no-effect concentration ($c_0$), whose inverse slope is commonly referred to as the tolerance concentration ($c_T$) [@kooijman_2009b]. Adapted from Table 2 in @jager_2023. {#tbl-chap4pMoA}

Candidate pMoAs are first evaluated independently for each compound and subsequently combined for the most supported hypotheses. Competing models are compared using the Bayesian Information Criterion (BIC), allowing comparison among alternative physiological hypotheses while penalizing model complexity.

Models are designated in the code with combinaison of letters corresponding to the pMoA(s) considered in a given model :

-   A : Ingestion and/or Assimilation costs,
-   M : Maintenance costs,
-   G : Growth and maturity costs,
-   R : Reproduction costs.

Both the DEB recalibration and the DEB-TKTD calibration on the single substances data @gollot_2026 were performed using Bayesian inference implemented in MCSim [@bois_2009]. Three independent Markov chain Monte Carlo chains of 30,000 iterations were run, and the final 10,000 iterations of each chain were retained to characterize the posterior distributions. Growth endpoints were modeled assuming normally distributed residuals, whereas cocoon production was modeled using a Poisson likelihood. Convergence was assessed by inspecting chain mixing and the agreement of posterior distributions among chains. Point estimates were defined as the modes of the posterior distributions with their 95% credibility intervals.

```{r writeTKTDmodels}

# Automatically writes the different TKTD models 

KapChange <- "C"
FmType    <- "W"
fType     <- "K"
RLWType   <- "e"

f_write_DEBTKTD_models(KapChange, FmType, fType, RLWType)
```
