```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# DEB-TKTD

## Available data

```{r}
Condition_order <- c("Ctrl", "C1", "C2", "C3", "C4", "C5", "C6", "C7", "C8", "C9", "C10")

df_data_EC50 <- f_import_data_DEBTKTD() |> 
  mutate(
    #Condition = fct_reorder(Condition, Dose)
    Condition = fct_relevel(Condition, Condition_order)
  ) |> 
  filter(!(Experiment_type == "Repro" & Time == 14))

pWg <- ggplot(
    data = df_data_EC50 |> filter(Experiment_type == "Growth"),
    aes(
      x = Time,
      y = Weight,
      color = Molecule
    )
  )+
  geom_point(alpha = 0.7)+
  geom_line(alpha = 0.5)+
  facet_wrap(~Condition)+
  scale_color_manual(
    values = col_Molecule
  )+
  theme_minimal()

pWr <- ggplot(
    data = df_data_EC50 |> filter(Experiment_type == "Repro"),
    aes(
      x = Time,
      y = Weight,
      color = Molecule
    )
  )+
  geom_point(alpha = 0.7)+
  geom_line(alpha = 0.5)+
  facet_wrap(~Condition)+
  scale_color_manual(
    values = col_Molecule
  )+
  theme_minimal()

pRr <- ggplot(
    data = df_data_EC50 |> filter(Experiment_type == "Repro"),
    aes(
      x = Time,
      y = Reproduction,
      color = Molecule
    )
  )+
  geom_point(alpha = 0.7)+
  geom_line(alpha = 0.5)+
  facet_wrap(~Condition)+
  scale_color_manual(
    values = col_Molecule
  )+
  theme_minimal()

```

```{r}

# faire des panels
pWg
pWr
pRr
```

## Relationship between W, E, and Eh for juveniles

The juvenile growth experiments were conducted with juvenile individuals housed individually in cosms containing 200 g of Closeaux soil, maintained at 18°C, and fed 3 g of horse dung per individual every 14 days. Individuals were exposed to a range of concentrations of either imidacloprid or epoxiconazole. In the DEB-TKTD model, the initial maturity of these individuals must be specified, although it was not and can not be directly measured. We therefore used a proxy based on the relationship between predicted body mass and predicted maturity obtained from the DEB model for the Gollot2026_dens_D5 experiment, which was conducted under the same experimental conditions as the culture from which these earthworms came from.

```{r}
path_D_CWKe <- here::here("mod/D_DEB_CWKe/W_Eh_relationship")

MCMC_out_D_CWKe <- f_MCSim(path_D_CWKe)
L_parameters_D_CWKe <- unique(MCMC_out_D_CWKe$Priors$Nom)

Summary_res_D_CWKe <- 
  as.data.frame(MCMC_out_D_CWKe$Summary_res)[1:length(L_parameters_D_CWKe)] |> 
  mutate(Model = "D_CWKe") 

Nb_experiment <- 1
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Maturity,
    Energy"

l_Experiment_D5 <- c("Gollot2026_dens_D5")

l_param_name_D_CWKe <- names(Summary_res_D_CWKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_D_CWKe, l_Experiment_D5, 
  Adults_alone = FALSE, OM_diff = TRUE, 
  l_param_name_D_CWKe, step_sim, Endpoints_print
  )

# ./mcsim.DEBcali DEB_setpoint_full_1.in


file_rds_D_CWKe <- file.path(path_D_CWKe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_D_CWKe)) {
  df_pred_full_D_CWKe <- readRDS(file_rds_D_CWKe)
} else {
  df_pred_full_D_CWKe <- f_read_Setpoint_full(path_D_CWKe, Adults_alone = FALSE, l_Experiment_D5, Nb_experiment, select_times, step_sim, bol_Eh = TRUE)
}

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe |> 
  pivot_wider(
    id_cols = Time,
    names_from = Endpt, 
    values_from = predict.endpoint
    )

```

```{r}
mod_RWEh <- lm(
  Maturity ~ Weight + I(Weight^2), 
  data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.5)
  )
summary(mod_RWEh)

c <- coef(mod_RWEh)[["(Intercept)"]]
b <- coef(mod_RWEh)[["Weight"]]
a <- coef(mod_RWEh)[["I(Weight^2)"]]

equation <- paste0(
  "Maturity = ", round(a, 3), " Weight² + ",
  round(b, 3), " Weight + ",
  round(c, 3)
)

equation
```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Relationship between weight and maturity in the Gollot2026_dens_D1 experiment.
#| label: fig-RWEh
#| fig-height: 4
#| fig-width: 6

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe_wide |>
  mutate(
    Maturity_pred = predict(
      mod_RWEh, 
      newdata = df_pred_full_D_CWKe_wide
      )
    )

col_mod <- Nord_frost[4]

p <- ggplot() +
  geom_line(
    data = df_pred_full_D_CWKe_wide,
    aes(
      x = Weight,
      y = Maturity
    ),
    linewidth = 2,
    linetype = "dotted",
    color = Nord_polar[1]
  )+
  geom_line(
    data = df_pred_full_D_CWKe_wide,
    aes(
      x = Weight,
      y = Maturity_pred
    ),
    color = col_mod,
    linewidth = 1
  )+
  labs(
    x = "Weight (g)",
    y = "Maturity (J)",
    title = "Relationship between Weight and Maturity",
    subtitle = equation,
    caption = "Experiment : Gollot2026_dens_D5"
  )+
  theme_minimal()+
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = col_mod)
  )

p

```

As the initial weight in this dataset range from 0.055 to 0.141 g, a relationship established for weights under 0.5 g is enough.

```{r}
mod_RWEn <- lm(
  Energy ~ Weight + I(Weight^2) + I(Weight^3), 
  data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.2 & Weight > 0.05)
  )
summary(mod_RWEn)
coef(mod_RWEn)

c <- coef(mod_RWEn)[["(Intercept)"]]
b <- coef(mod_RWEn)[["Weight"]]
a <- coef(mod_RWEn)[["I(Weight^2)"]]

equation <- paste0(
  "Energy = ", round(a, 3), " Weight² + ",
  round(b, 3), " Weight + ",
  round(c, 3)
)

equation
```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Relationship between weight and maturity in the Gollot2026_dens_D1 experiment.
#| label: fig-RWEh
#| fig-height: 4
#| fig-width: 6

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe_wide |>
  mutate(
    Energy_pred = predict(
      mod_RWEn, 
      newdata = df_pred_full_D_CWKe_wide
      )
    )

col_mod <- Nord_frost[4]

p <- ggplot() +
  geom_line(
    data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.2 & Weight > 0.05),
    aes(
      x = Weight,
      y = Energy
    ),
    linewidth = 2,
    linetype = "dotted",
    color = Nord_polar[1]
  )+
  geom_line(
    data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.2 & Weight > 0.05),
    aes(
      x = Weight,
      y = Energy_pred
    ),
    color = col_mod,
    linewidth = 1
  )+
  labs(
    x = "Weight (g)",
    y = "Energy in the reserve (J)",
    title = "Relationship between Weight and Energy",
    subtitle = equation,
    caption = "Experiment : Gollot2026_dens_D5"
  )+
  theme_minimal()+
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = col_mod)
  )

p

```

For the initialisation of the energy in the reserve, we assume individuals were well fed in the culture and therefore the energy can be assumed to equal Em at the start of the experiment.

## Effect of EPX

### Model fit

```{r}
Molec <- "EPX"
path_fig <- here::here("fig/DEBTKTD_Models")

path_A_EPX_A <- here::here("mod/Z_DEB-TKTD/A_EPX_A")
path_B_EPX_M <- here::here("mod/Z_DEB-TKTD/B_EPX_M")
path_C_EPX_G <- here::here("mod/Z_DEB-TKTD/C_EPX_G")
path_D_EPX_R <- here::here("mod/Z_DEB-TKTD/D_EPX_R")

df_data_fit_EPX <- f_import_data_DEBTKTD() |> 
  filter(Molecule == Molec) |> 
  mutate(No_sim = case_when(
    Experiment_type == "Repro" ~ No_sim+9,
    .default = No_sim
  ))

```

```{r fit_A_EPX_A, message=F, warning=F}

path_fig <- here::here("fig/DEBTKTD_Models")
Molec <- "EPX"
df_data_fit_EPX <- f_import_data_DEBTKTD() |> filter(Molecule == Molec)

NbIter <- 30000
OM_diff <- TRUE
RTOL <- 1e-10
ATOL <- 1e-9

text_priors <- '
Distrib (nec,          TruncNormal,  10000, 0.5,               1,     1000000);
Distrib (b,            LogUniform,                0.000000000001,          10);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

######## A_EPX_A ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_A_EPX_A, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## B_EPX_M ##############################################################
seeds <- c(C1 = 3345, C2 = 6636, C3 = 2212)
f_In_TKTD_tot(path_B_EPX_M, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## C_EPX_G ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_C_EPX_G, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## D_EPX_R ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_D_EPX_R, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

# ./mcsim.DEB-EPX DEB_TKTD_C1.in

```

### Estimates results

```{r}
n_data_Weight <- length(na.omit(df_data_fit_EPX$Weight))
n_data_Reproduction <- length(na.omit(df_data_fit_EPX$Reproduction))
n_data_fit <- n_data_Weight + n_data_Reproduction

######### A_EPX_A ###############################################################

MCMC_out_A_EPX_A <- f_MCSim(path_A_EPX_A)

NC_A_EPX_A <- MCMC_out_A_EPX_A$NC
Nb_param_A_EPX_A <- MCMC_out_A_EPX_A$Nb_param
Nb_experiment_A_EPX_A <- MCMC_out_A_EPX_A$Nb_experiment
Nb_iter_kept_A_EPX_A <- MCMC_out_A_EPX_A$Nb_iter_kept
N_iter_setpoint_A_EPX_A <- MCMC_out_A_EPX_A$N_iter_setpoint
L_parameters_A_EPX_A <- unique(MCMC_out_A_EPX_A$Priors$Nom)

LL_A_EPX_A <- f_get_mode(MCMC_out_A_EPX_A$df_LnData$LnData)
k_A_EPX_A <- Nb_param_A_EPX_A - 1 # On enlève le Sigma_W

BIC_A_EPX_A <- -2*LL_A_EPX_A+k_A_EPX_A*log(n_data_fit)

Summary_res_A_EPX_A <- 
  as.data.frame(MCMC_out_A_EPX_A$Summary_res)[1:length(L_parameters_A_EPX_A)] |> 
  mutate(Model = "A_EPX_A")

Summary_res_A_EPX_A

######### B_EPX_M ###############################################################

MCMC_out_B_EPX_M <- f_MCSim(path_B_EPX_M)

NC_B_EPX_M <- MCMC_out_B_EPX_M$NC
Nb_param_B_EPX_M <- MCMC_out_B_EPX_M$Nb_param
Nb_experiment_B_EPX_M <- MCMC_out_B_EPX_M$Nb_experiment
Nb_iter_kept_B_EPX_M <- MCMC_out_B_EPX_M$Nb_iter_kept
N_iter_setpoint_B_EPX_M <- MCMC_out_B_EPX_M$N_iter_setpoint
L_parameters_B_EPX_M <- unique(MCMC_out_B_EPX_M$Priors$Nom)

LL_B_EPX_M <- f_get_mode(MCMC_out_B_EPX_M$df_LnData$LnData)
k_B_EPX_M <- Nb_param_B_EPX_M - 1 # On enlève le Sigma_W

BIC_B_EPX_M <- -2*LL_B_EPX_M+k_B_EPX_M*log(n_data_fit)

Summary_res_B_EPX_M <- 
  as.data.frame(MCMC_out_B_EPX_M$Summary_res)[1:length(L_parameters_B_EPX_M)] |> 
  mutate(Model = "B_EPX_M")

Summary_res_B_EPX_M

######### C_EPX_G ###############################################################

MCMC_out_C_EPX_G <- f_MCSim(path_C_EPX_G)

NC_C_EPX_G <- MCMC_out_C_EPX_G$NC
Nb_param_C_EPX_G <- MCMC_out_C_EPX_G$Nb_param
Nb_experiment_C_EPX_G <- MCMC_out_C_EPX_G$Nb_experiment
Nb_iter_kept_C_EPX_G <- MCMC_out_C_EPX_G$Nb_iter_kept
N_iter_setpoint_C_EPX_G <- MCMC_out_C_EPX_G$N_iter_setpoint
L_parameters_C_EPX_G <- unique(MCMC_out_C_EPX_G$Priors$Nom)

LL_C_EPX_G <- f_get_mode(MCMC_out_C_EPX_G$df_LnData$LnData)
k_C_EPX_G <- Nb_param_C_EPX_G - 1 # On enlève le Sigma_W

BIC_C_EPX_G <- -2*LL_C_EPX_G+k_C_EPX_G*log(n_data_fit)

Summary_res_C_EPX_G <- 
  as.data.frame(MCMC_out_C_EPX_G$Summary_res)[1:length(L_parameters_C_EPX_G)] |> 
  mutate(Model = "C_EPX_G")

Summary_res_C_EPX_G

######### D_EPX_R ###############################################################

MCMC_out_D_EPX_R <- f_MCSim(path_D_EPX_R)

NC_D_EPX_R <- MCMC_out_D_EPX_R$NC
Nb_param_D_EPX_R <- MCMC_out_D_EPX_R$Nb_param
Nb_experiment_D_EPX_R <- MCMC_out_D_EPX_R$Nb_experiment
Nb_iter_kept_D_EPX_R <- MCMC_out_D_EPX_R$Nb_iter_kept
N_iter_setpoint_D_EPX_R <- MCMC_out_D_EPX_R$N_iter_setpoint
L_parameters_D_EPX_R <- unique(MCMC_out_D_EPX_R$Priors$Nom)

LL_D_EPX_R <- f_get_mode(MCMC_out_D_EPX_R$df_LnData$LnData)
k_D_EPX_R <- Nb_param_D_EPX_R - 1 # On enlève le Sigma_W

BIC_D_EPX_R <- -2*LL_D_EPX_R+k_D_EPX_R*log(n_data_fit)

Summary_res_D_EPX_R <- 
  as.data.frame(MCMC_out_D_EPX_R$Summary_res)[1:length(L_parameters_D_EPX_R)] |> 
  mutate(Model = "D_EPX_R")

Summary_res_D_EPX_R

list_models <- c("A_EPX_A", "B_EPX_M", "C_EPX_G", "D_EPX_R")
df_LL_BIC <- data.frame(
  Model = list_models,
  LL = round(unlist(mget(paste0("LL_", list_models))), 2),
  BIC = round(unlist(mget(paste0("BIC_", list_models))), 2)
)
```

```{r resall}
#| tbl-cap: Estimation results from all models. 

list_models <- c("A_EPX_A", "B_EPX_M", "C_EPX_G", "D_EPX_R")
list_model_summary <- mget(paste0("Summary_res_", list_models))

param_order <- c(
  "nec", "b"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = str_c(
        round(Result_mode, 3),
        " [", round(`2.5%`, 3),
        " ; ", round(`97.5%`, 3), "]"
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_model_summary %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  ) |> 
  left_join(df_LL_BIC)

df_result |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )
```

### Chains

::: panel-tabset
## A_EPX_A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_A_EPX_A
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_A_EPX_A$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_EPX_M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_B_EPX_M
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_B_EPX_M$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsB_EPX_M, include = F}
ggsave(
  filename="B_EPX_M_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_EPX_G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_C_EPX_G
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_C_EPX_G$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC_EPX_G, include = F}
ggsave(
  filename="C_EPX_G_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_EPX_R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_D_EPX_R
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_D_EPX_R$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsD_EPX_R, include = F}
ggsave(
  filename="D_EPX_R_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

### Likelihood

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_A_EPX_A
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_A_EPX_A$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_A_EPX_A$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_EPX_A$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_A_EPX_A$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_EPX_A$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

### Posterior distributions

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_A_EPX_A
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_A_EPX_A$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_A_EPX_A$Chains_plot <- MCMC_out_A_EPX_A$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_A_EPX_A$Chains_plot, Nom %in% L_parameters_A_EPX_A),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

### Predicted vs. Obs

```{r}
l_param_name_A_EPX_A <- names(Summary_res_A_EPX_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.") 

f_In_predobs_TKTD(path_A_EPX_A, Molec, l_param_name_A_EPX_A)
```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-EPX DEB_setpoint_predobs_${j}.in
done
```

```{r, results=F, message=F, warning=F}

Nb_experiment <- 18

df_data_obs_EPX <- df_data_fit_EPX |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

######## A_EPX_A ###############################################################

df_pred_A_EPX_A <- f_read_predobs(path_A_EPX_A, Nb_experiment, df_data_obs_EPX)

df_pred_Weight_A_EPX_A <- subset(df_pred_A_EPX_A, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_A_EPX_A <- subset(df_pred_A_EPX_A, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_A_EPX_A <- df_data_obs_EPX |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_A_EPX_A, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_A_EPX_A <- df_data_obs_EPX |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_A_EPX_A, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_A_EPX_A
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)

seq_line <- seq(0.05, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_A_EPX_A,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Condition
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(5, 30, 0.1)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_A_EPX_A,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Condition
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs

```

```{r savepredobsA_EPX_A, include = F}

ggsave(
  filename = "A_EPX_A_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

### Predicted trajectories for Weight and Reproduction

```{r setpointfullin}

Nb_experiment <- 18
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Reproduction"


l_param_name_A_EPX_A <- names(Summary_res_A_EPX_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_A_EPX_A, Molec, 
  l_param_name_A_EPX_A, step_sim, Endpoints_print
  )


l_param_name_B_EPX_M <- names(Summary_res_B_EPX_M) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_B_EPX_M, Molec, 
  l_param_name_B_EPX_M, step_sim, Endpoints_print
  )

l_param_name_C_EPX_G <- names(Summary_res_C_EPX_G) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_C_EPX_G, Molec, 
  l_param_name_C_EPX_G, step_sim, Endpoints_print
  )

l_param_name_D_EPX_R <- names(Summary_res_D_EPX_R) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_D_EPX_R, Molec, 
  l_param_name_D_EPX_R, step_sim, Endpoints_print
  )


```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-EPX DEB_setpoint_full_${j}.in
done
```

```{r, message = F, warning = F}

width_plot <- 12
height_plot <- 12

file_rds_A_EPX_A <- file.path(path_A_EPX_A, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_A_EPX_A)) {
  df_pred_full_A_EPX_A <- readRDS(file_rds_A_EPX_A)
} else {
  df_pred_full_A_EPX_A <- f_read_Setpoint_full_TKTD(path_A_EPX_A, Molec, select_times, step_sim)
}

file_rds_B_EPX_M <- file.path(path_B_EPX_M, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_B_EPX_M)) {
  df_pred_full_B_EPX_M <- readRDS(file_rds_B_EPX_M)
} else {
  df_pred_full_B_EPX_M <- f_read_Setpoint_full_TKTD(path_B_EPX_M, Molec, select_times, step_sim)
}

file_rds_C_EPX_G <- file.path(path_C_EPX_G, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_C_EPX_G)) {
  df_pred_full_C_EPX_G <- readRDS(file_rds_C_EPX_G)
} else {
  df_pred_full_C_EPX_G <- f_read_Setpoint_full_TKTD(path_C_EPX_G, Molec, select_times, step_sim)
}

file_rds_D_EPX_R <- file.path(path_D_EPX_R, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_D_EPX_R)) {
  df_pred_full_D_EPX_R <- readRDS(file_rds_D_EPX_R)
} else {
  df_pred_full_D_EPX_R <- f_read_Setpoint_full_TKTD(path_D_EPX_R, Molec, select_times, step_sim)
}

```

## A_EPX_A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_A_EPX_A
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_A_EPX_A, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_A_EPX_A, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pA <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pA
```

```{r savetrajWRA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_trajWR.png", 
  plot=pA, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## B_EPX_M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_B_EPX_M
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_B_EPX_M, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_B_EPX_M, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_B_EPX_M, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_B_EPX_M, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pB <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pB
```

```{r savetrajWRB_EPX_M, include = F}
ggsave(
  filename="B_EPX_M_trajWR.png", 
  plot=pB, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## C_EPX_G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_C_EPX_G
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_C_EPX_G, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_C_EPX_G, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_C_EPX_G, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_C_EPX_G, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pC <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pC
```

```{r savetrajWRC_EPX_G, include = F}
ggsave(
  filename="C_EPX_G_trajWR.png", 
  plot=pC, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## D_EPX_R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_D_EPX_R
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_D_EPX_R, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_D_EPX_R, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_D_EPX_R, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_D_EPX_R, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pD <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pD
```

```{r savetrajWRD_EPX_R, include = F}
ggsave(
  filename="D_EPX_R_trajWR.png", 
  plot=pD, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## Effect of IMD

### Model fit

```{r}
Molec <- "IMD"
path_fig <- here::here("fig/DEBTKTD_Models")

path_E_IMD_A <- here::here("mod/Z_DEB-TKTD/E_IMD_A")
path_F_IMD_M <- here::here("mod/Z_DEB-TKTD/F_IMD_M")
path_G_IMD_G <- here::here("mod/Z_DEB-TKTD/G_IMD_G")
path_H_IMD_R <- here::here("mod/Z_DEB-TKTD/H_IMD_R")

df_data_fit_IMD <- f_import_data_DEBTKTD() |> 
  filter(Molecule == Molec) |> 
  mutate(No_sim = case_when(
    Experiment_type == "Repro" ~ No_sim+9,
    .default = No_sim
  ))

```

```{r fit_E_IMD_A, message=F, warning=F}

path_fig <- here::here("fig/DEBTKTD_Models")
Molec <- "IMD"
df_data_fit_IMD <- f_import_data_DEBTKTD() |> filter(Molecule == Molec)

NbIter <- 300000
OM_diff <- TRUE
RTOL <- 1e-10
ATOL <- 1e-9

text_priors <- '
Distrib (nec,          LogUniform,                 0.001,     1000000);
Distrib (b,            LogUniform,                0.000000000001,          10);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

######## E_IMD_A ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_E_IMD_A, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## F_IMD_M ##############################################################
seeds <- c(C1 = 3345, C2 = 6636, C3 = 2212)
f_In_TKTD_tot(path_F_IMD_M, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## G_IMD_G ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_G_IMD_G, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## H_IMD_R ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_H_IMD_R, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

# ./mcsim.DEB-IMD DEB_TKTD_C1.in

```

### Estimates results

```{r}
n_data_Weight <- length(na.omit(df_data_fit_IMD$Weight))
n_data_Reproduction <- length(na.omit(df_data_fit_IMD$Reproduction))
n_data_fit <- n_data_Weight + n_data_Reproduction

######### E_IMD_A ###############################################################

MCMC_out_E_IMD_A <- f_MCSim(path_E_IMD_A)

NC_E_IMD_A <- MCMC_out_E_IMD_A$NC
Nb_param_E_IMD_A <- MCMC_out_E_IMD_A$Nb_param
Nb_experiment_E_IMD_A <- MCMC_out_E_IMD_A$Nb_experiment
Nb_iter_kept_E_IMD_A <- MCMC_out_E_IMD_A$Nb_iter_kept
N_iter_setpoint_E_IMD_A <- MCMC_out_E_IMD_A$N_iter_setpoint
L_parameters_E_IMD_A <- unique(MCMC_out_E_IMD_A$Priors$Nom)

LL_E_IMD_A <- f_get_mode(MCMC_out_E_IMD_A$df_LnData$LnData)
k_E_IMD_A <- Nb_param_E_IMD_A - 1 # On enlève le Sigma_W

BIC_E_IMD_A <- -2*LL_E_IMD_A+k_E_IMD_A*log(n_data_fit)

Summary_res_E_IMD_A <- 
  as.data.frame(MCMC_out_E_IMD_A$Summary_res)[1:length(L_parameters_E_IMD_A)] |> 
  mutate(Model = "E_IMD_A")

Summary_res_E_IMD_A

######### F_IMD_M ###############################################################

MCMC_out_F_IMD_M <- f_MCSim(path_F_IMD_M)

NC_F_IMD_M <- MCMC_out_F_IMD_M$NC
Nb_param_F_IMD_M <- MCMC_out_F_IMD_M$Nb_param
Nb_experiment_F_IMD_M <- MCMC_out_F_IMD_M$Nb_experiment
Nb_iter_kept_F_IMD_M <- MCMC_out_F_IMD_M$Nb_iter_kept
N_iter_setpoint_F_IMD_M <- MCMC_out_F_IMD_M$N_iter_setpoint
L_parameters_F_IMD_M <- unique(MCMC_out_F_IMD_M$Priors$Nom)

LL_F_IMD_M <- f_get_mode(MCMC_out_F_IMD_M$df_LnData$LnData)
k_F_IMD_M <- Nb_param_F_IMD_M - 1 # On enlève le Sigma_W

BIC_F_IMD_M <- -2*LL_F_IMD_M+k_F_IMD_M*log(n_data_fit)

Summary_res_F_IMD_M <- 
  as.data.frame(MCMC_out_F_IMD_M$Summary_res)[1:length(L_parameters_F_IMD_M)] |> 
  mutate(Model = "F_IMD_M")

Summary_res_F_IMD_M

######### G_IMD_G ###############################################################

MCMC_out_G_IMD_G <- f_MCSim(path_G_IMD_G)

NC_G_IMD_G <- MCMC_out_G_IMD_G$NC
Nb_param_G_IMD_G <- MCMC_out_G_IMD_G$Nb_param
Nb_experiment_G_IMD_G <- MCMC_out_G_IMD_G$Nb_experiment
Nb_iter_kept_G_IMD_G <- MCMC_out_G_IMD_G$Nb_iter_kept
N_iter_setpoint_G_IMD_G <- MCMC_out_G_IMD_G$N_iter_setpoint
L_parameters_G_IMD_G <- unique(MCMC_out_G_IMD_G$Priors$Nom)

LL_G_IMD_G <- f_get_mode(MCMC_out_G_IMD_G$df_LnData$LnData)
k_G_IMD_G <- Nb_param_G_IMD_G - 1 # On enlève le Sigma_W

BIC_G_IMD_G <- -2*LL_G_IMD_G+k_G_IMD_G*log(n_data_fit)

Summary_res_G_IMD_G <- 
  as.data.frame(MCMC_out_G_IMD_G$Summary_res)[1:length(L_parameters_G_IMD_G)] |> 
  mutate(Model = "G_IMD_G")

Summary_res_G_IMD_G

######### H_IMD_R ###############################################################

MCMC_out_H_IMD_R <- f_MCSim(path_H_IMD_R)

NC_H_IMD_R <- MCMC_out_H_IMD_R$NC
Nb_param_H_IMD_R <- MCMC_out_H_IMD_R$Nb_param
Nb_experiment_H_IMD_R <- MCMC_out_H_IMD_R$Nb_experiment
Nb_iter_kept_H_IMD_R <- MCMC_out_H_IMD_R$Nb_iter_kept
N_iter_setpoint_H_IMD_R <- MCMC_out_H_IMD_R$N_iter_setpoint
L_parameters_H_IMD_R <- unique(MCMC_out_H_IMD_R$Priors$Nom)

LL_H_IMD_R <- f_get_mode(MCMC_out_H_IMD_R$df_LnData$LnData)
k_H_IMD_R <- Nb_param_H_IMD_R - 1 # On enlève le Sigma_W

BIC_H_IMD_R <- -2*LL_H_IMD_R+k_H_IMD_R*log(n_data_fit)

Summary_res_H_IMD_R <- 
  as.data.frame(MCMC_out_H_IMD_R$Summary_res)[1:length(L_parameters_H_IMD_R)] |> 
  mutate(Model = "H_IMD_R")

Summary_res_H_IMD_R

list_models <- c("E_IMD_A", "F_IMD_M", "G_IMD_G", "H_IMD_R")
df_LL_BIC <- data.frame(
  Model = list_models,
  LL = round(unlist(mget(paste0("LL_", list_models))), 2),
  BIC = round(unlist(mget(paste0("BIC_", list_models))), 2)
)
```

```{r resall}
#| tbl-cap: Estimation results from all models. 

list_models <- c("E_IMD_A", "F_IMD_M", "G_IMD_G", "H_IMD_R")
list_model_summary <- mget(paste0("Summary_res_", list_models))

param_order <- c(
  "nec", "b"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = str_c(
        round(Result_mode, 3),
        " [", round(`2.5%`, 3),
        " ; ", round(`97.5%`, 3), "]"
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_model_summary %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  ) |> 
  left_join(df_LL_BIC)

df_result |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )
```

### Chains

::: panel-tabset
## E_IMD_A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_E_IMD_A
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_E_IMD_A$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsE_IMD_A, include = F}
ggsave(
  filename="E_IMD_A_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## F_IMD_M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_F_IMD_M
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_F_IMD_M$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsF_IMD_M, include = F}
ggsave(
  filename="F_IMD_M_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## G_IMD_G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_G_IMD_G
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_G_IMD_G$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsG_IMD_G, include = F}
ggsave(
  filename="G_IMD_G_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## H_IMD_R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_H_IMD_R
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_H_IMD_R$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsH_IMD_R, include = F}
ggsave(
  filename="H_IMD_R_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

### Likelihood

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_E_IMD_A
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_E_IMD_A$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_E_IMD_A$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_E_IMD_A$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_E_IMD_A$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_E_IMD_A$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLE_IMD_A, include = F}
ggsave(
  filename="E_IMD_A_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

### Posterior distributions

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_E_IMD_A
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_E_IMD_A$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_E_IMD_A$Chains_plot <- MCMC_out_E_IMD_A$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_E_IMD_A$Chains_plot, Nom %in% L_parameters_E_IMD_A),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostE_IMD_A, include = F}
ggsave(
  filename="E_IMD_A_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

### Predicted vs. Obs

```{r}
l_param_name_E_IMD_A <- names(Summary_res_E_IMD_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.") 

f_In_predobs_TKTD(path_E_IMD_A, Molec, l_param_name_E_IMD_A)
```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-IMD DEB_setpoint_predobs_${j}.in
done
```

```{r, results=F, message=F, warning=F}

Nb_experiment <- 18

df_data_obs_IMD <- df_data_fit_IMD |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

######## E_IMD_A ###############################################################

df_pred_E_IMD_A <- f_read_predobs(path_E_IMD_A, Nb_experiment, df_data_obs_IMD)

df_pred_Weight_E_IMD_A <- subset(df_pred_E_IMD_A, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_E_IMD_A <- subset(df_pred_E_IMD_A, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_E_IMD_A <- df_data_obs_IMD |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_E_IMD_A, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_E_IMD_A <- df_data_obs_IMD |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_E_IMD_A, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_E_IMD_A
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)

seq_line <- seq(0.05, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_E_IMD_A,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Condition
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(5, 30, 0.1)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_E_IMD_A,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Condition
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs

```

```{r savepredobsE_IMD_A, include = F}

ggsave(
  filename = "E_IMD_A_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

### Predicted trajectories for Weight and Reproduction

```{r setpointfullin}

Nb_experiment <- 18
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Reproduction"


l_param_name_E_IMD_A <- names(Summary_res_E_IMD_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_E_IMD_A, Molec, 
  l_param_name_E_IMD_A, step_sim, Endpoints_print
  )


l_param_name_F_IMD_M <- names(Summary_res_F_IMD_M) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_F_IMD_M, Molec, 
  l_param_name_F_IMD_M, step_sim, Endpoints_print
  )

l_param_name_G_IMD_G <- names(Summary_res_G_IMD_G) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_G_IMD_G, Molec, 
  l_param_name_G_IMD_G, step_sim, Endpoints_print
  )

l_param_name_H_IMD_R <- names(Summary_res_H_IMD_R) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_H_IMD_R, Molec, 
  l_param_name_H_IMD_R, step_sim, Endpoints_print
  )


```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-IMD DEB_setpoint_full_${j}.in
done
```

```{r, message = F, warning = F}

width_plot <- 12
height_plot <- 12

file_rds_E_IMD_A <- file.path(path_E_IMD_A, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_E_IMD_A)) {
  df_pred_full_E_IMD_A <- readRDS(file_rds_E_IMD_A)
} else {
  df_pred_full_E_IMD_A <- f_read_Setpoint_full_TKTD(path_E_IMD_A, Molec, select_times, step_sim)
}

file_rds_F_IMD_M <- file.path(path_F_IMD_M, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_F_IMD_M)) {
  df_pred_full_F_IMD_M <- readRDS(file_rds_F_IMD_M)
} else {
  df_pred_full_F_IMD_M <- f_read_Setpoint_full_TKTD(path_F_IMD_M, Molec, select_times, step_sim)
}

file_rds_G_IMD_G <- file.path(path_G_IMD_G, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_G_IMD_G)) {
  df_pred_full_G_IMD_G <- readRDS(file_rds_G_IMD_G)
} else {
  df_pred_full_G_IMD_G <- f_read_Setpoint_full_TKTD(path_G_IMD_G, Molec, select_times, step_sim)
}

file_rds_H_IMD_R <- file.path(path_H_IMD_R, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_H_IMD_R)) {
  df_pred_full_H_IMD_R <- readRDS(file_rds_H_IMD_R)
} else {
  df_pred_full_H_IMD_R <- f_read_Setpoint_full_TKTD(path_H_IMD_R, Molec, select_times, step_sim)
}

```

## E_IMD_A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_E_IMD_A
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_E_IMD_A, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_E_IMD_A, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_E_IMD_A, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_E_IMD_A, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pA <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pA
```

```{r savetrajWRE_IMD_A, include = F}
ggsave(
  filename="E_IMD_A_trajWR.png", 
  plot=pA, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## F_IMD_M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_F_IMD_M
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_F_IMD_M, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_M, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_F_IMD_M, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_M, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pB <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pB
```

```{r savetrajWRF_IMD_M, include = F}
ggsave(
  filename="F_IMD_M_trajWR.png", 
  plot=pB, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## G_IMD_G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_G_IMD_G
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_G_IMD_G, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_G_IMD_G, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_G_IMD_G, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_G_IMD_G, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pC <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pC
```

```{r savetrajWRG_IMD_G, include = F}
ggsave(
  filename="G_IMD_G_trajWR.png", 
  plot=pC, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```

## H_IMD_R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_H_IMD_R
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_H_IMD_R, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_H_IMD_R, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_H_IMD_R, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_H_IMD_R, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_IMD,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

pD <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

pD
```

```{r savetrajWRH_IMD_R, include = F}
ggsave(
  filename="H_IMD_R_trajWR.png", 
  plot=pD, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```
