```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# DEB-TKTD

## Available data

```{r}
Condition_order <- c("Ctrl", "C1", "C2", "C3", "C4", "C5", "C6", "C7", "C8", "C9", "C10")

df_data_EC50 <- f_import_data_DEBTKTD() |> 
  mutate(
    #Condition = fct_reorder(Condition, Dose)
    Condition = fct_relevel(Condition, Condition_order)
  ) |> 
  filter(!(Experiment_type == "Repro" & Time == 14))

pWg <- ggplot(
    data = df_data_EC50 |> filter(Experiment_type == "Growth"),
    aes(
      x = Time,
      y = Weight,
      color = Molecule
    )
  )+
  geom_point(alpha = 0.7)+
  geom_line(alpha = 0.5)+
  facet_wrap(~Condition)+
  scale_color_manual(
    values = col_Molecule
  )+
  theme_minimal()

pWr <- ggplot(
    data = df_data_EC50 |> filter(Experiment_type == "Repro"),
    aes(
      x = Time,
      y = Weight,
      color = Molecule
    )
  )+
  geom_point(alpha = 0.7)+
  geom_line(alpha = 0.5)+
  facet_wrap(~Condition)+
  scale_color_manual(
    values = col_Molecule
  )+
  theme_minimal()

pRr <- ggplot(
    data = df_data_EC50 |> filter(Experiment_type == "Repro"),
    aes(
      x = Time,
      y = Reproduction,
      color = Molecule
    )
  )+
  geom_point(alpha = 0.7)+
  geom_line(alpha = 0.5)+
  facet_wrap(~Condition)+
  scale_color_manual(
    values = col_Molecule
  )+
  theme_minimal()

```

```{r}

# faire des panels
pWg
pWr
pRr
```

## Relationship between W, E, and Eh for juveniles

The juvenile growth experiments were conducted with juvenile individuals housed individually in cosms containing 200 g of Closeaux soil, maintained at 18°C, and fed 3 g of horse dung per individual every 14 days. Individuals were exposed to a range of concentrations of either imidacloprid or epoxiconazole. In the DEB-TKTD model, the initial maturity of these individuals must be specified, although it was not and can not be directly measured. We therefore used a proxy based on the relationship between predicted body mass and predicted maturity obtained from the DEB model for the Gollot2026_dens_D5 experiment, which was conducted under the same experimental conditions as the culture from which these earthworms came from.

```{r}
path_D_CWKe <- here::here("mod/D_DEB_CWKe/W_Eh_relationship")

MCMC_out_D_CWKe <- f_MCSim(path_D_CWKe)
L_parameters_D_CWKe <- unique(MCMC_out_D_CWKe$Priors$Nom)

Summary_res_D_CWKe <- 
  as.data.frame(MCMC_out_D_CWKe$Summary_res)[1:length(L_parameters_D_CWKe)] |> 
  mutate(Model = "D_CWKe") 

Nb_experiment <- 1
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Maturity,
    Energy"

l_Experiment_D5 <- c("Gollot2026_dens_D5")

l_param_name_D_CWKe <- names(Summary_res_D_CWKe) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full(
  path_D_CWKe, l_Experiment_D5, 
  Adults_alone = FALSE, OM_diff = TRUE, 
  l_param_name_D_CWKe, step_sim, Endpoints_print
  )

# ./mcsim.DEBcali DEB_setpoint_full_1.in


file_rds_D_CWKe <- file.path(path_D_CWKe, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_D_CWKe)) {
  df_pred_full_D_CWKe <- readRDS(file_rds_D_CWKe)
} else {
  df_pred_full_D_CWKe <- f_read_Setpoint_full(path_D_CWKe, Adults_alone = FALSE, l_Experiment_D5, Nb_experiment, select_times, step_sim, bol_Eh = TRUE)
}

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe |> 
  pivot_wider(
    id_cols = Time,
    names_from = Endpt, 
    values_from = predict.endpoint
    )

```

```{r}
mod_RWEh <- lm(
  Maturity ~ Weight + I(Weight^2), 
  data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.5)
  )
summary(mod_RWEh)

c <- coef(mod_RWEh)[["(Intercept)"]]
b <- coef(mod_RWEh)[["Weight"]]
a <- coef(mod_RWEh)[["I(Weight^2)"]]

equation <- paste0(
  "Maturity = ", round(a, 3), " Weight² + ",
  round(b, 3), " Weight + ",
  round(c, 3)
)

equation
```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Relationship between weight and maturity in the Gollot2026_dens_D1 experiment.
#| label: fig-RWEh
#| fig-height: 4
#| fig-width: 6

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe_wide |>
  mutate(
    Maturity_pred = predict(
      mod_RWEh, 
      newdata = df_pred_full_D_CWKe_wide
      )
    )

col_mod <- Nord_frost[4]

p <- ggplot() +
  geom_line(
    data = df_pred_full_D_CWKe_wide,
    aes(
      x = Weight,
      y = Maturity
    ),
    linewidth = 2,
    linetype = "dotted",
    color = Nord_polar[1]
  )+
  geom_line(
    data = df_pred_full_D_CWKe_wide,
    aes(
      x = Weight,
      y = Maturity_pred
    ),
    color = col_mod,
    linewidth = 1
  )+
  labs(
    x = "Weight (g)",
    y = "Maturity (J)",
    title = "Relationship between Weight and Maturity",
    subtitle = equation,
    caption = "Experiment : Gollot2026_dens_D5"
  )+
  theme_minimal()+
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = col_mod)
  )

p

```

As the initial weight in this dataset range from 0.055 to 0.141 g, a relationship established for weights under 0.5 g is enough.

```{r}
mod_RWEn <- lm(
  Energy ~ Weight + I(Weight^2) + I(Weight^3), 
  data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.2 & Weight > 0.05)
  )
summary(mod_RWEn)
coef(mod_RWEn)

c <- coef(mod_RWEn)[["(Intercept)"]]
b <- coef(mod_RWEn)[["Weight"]]
a <- coef(mod_RWEn)[["I(Weight^2)"]]

equation <- paste0(
  "Energy = ", round(a, 3), " Weight² + ",
  round(b, 3), " Weight + ",
  round(c, 3)
)

equation
```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Relationship between weight and maturity in the Gollot2026_dens_D1 experiment.
#| label: fig-RWEh
#| fig-height: 4
#| fig-width: 6

df_pred_full_D_CWKe_wide <- df_pred_full_D_CWKe_wide |>
  mutate(
    Energy_pred = predict(
      mod_RWEn, 
      newdata = df_pred_full_D_CWKe_wide
      )
    )

col_mod <- Nord_frost[4]

p <- ggplot() +
  geom_line(
    data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.2 & Weight > 0.05),
    aes(
      x = Weight,
      y = Energy
    ),
    linewidth = 2,
    linetype = "dotted",
    color = Nord_polar[1]
  )+
  geom_line(
    data = df_pred_full_D_CWKe_wide |> filter(Weight < 0.2 & Weight > 0.05),
    aes(
      x = Weight,
      y = Energy_pred
    ),
    color = col_mod,
    linewidth = 1
  )+
  labs(
    x = "Weight (g)",
    y = "Energy in the reserve (J)",
    title = "Relationship between Weight and Energy",
    subtitle = equation,
    caption = "Experiment : Gollot2026_dens_D5"
  )+
  theme_minimal()+
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = col_mod)
  )

p

```

For the initialisation of the energy in the reserve, we assume individuals were well fed in the culture and therefore the energy can be assumed to equal Em at the start of the experiment.

## Effect of EPX

### Model fit

```{r}
Molec <- "EPX"
path_fig <- here::here("fig/DEBTKTD_Models")

path_A_EPX_A <- here::here("mod/Z_DEB-TKTD/A_EPX_A")
path_B_EPX_M <- here::here("mod/Z_DEB-TKTD/B_EPX_M")
path_C_EPX_G <- here::here("mod/Z_DEB-TKTD/C_EPX_G")
path_D_EPX_R <- here::here("mod/Z_DEB-TKTD/D_EPX_R")

df_data_fit_EPX <- f_import_data_DEBTKTD() |> 
  filter(Molecule == Molec) |> 
  mutate(No_sim = case_when(
    Experiment_type == "Repro" ~ No_sim+9,
    .default = No_sim
  ))

df_sim <- f_MCSim_read_sim(file.path(path_A_EPX_A, "sim.out"))


pW <- ggplot()+
  geom_point(
    data = df_data_fit_EPX |> filter(Experiment_type == "Growth"),
    aes(
      x = Time,
      y = Weight
    )
  )+
  geom_line(
    data = df_sim,
    aes(
      x = Time,
      y = Weight
    ),
    color = "red"
  )+
  facet_wrap(~No_sim)

pR <- ggplot()+
  geom_point(
    data = df_data_fit_EPX |> filter(Experiment_type == "Growth"),
    aes(
      x = Time,
      y = Reproduction
    )
  )+
  geom_line(
    data = df_sim,
    aes(
      x = Time,
      y = Reproduction
    ),
    color = "red"
  )+
  facet_wrap(~No_sim)

p <- pW + pR


{
  df_sim <- f_MCSim_read_sim(file.path(path_A_EPX_A, "sim.out"))

pS <- ggplot()+
  geom_line(
    data = df_sim,
    aes(
      x = Time,
      y = Stress
    ),
    color = "red"
  )+
  facet_wrap(~No_sim)

pD <- ggplot()+
  geom_line(
    data = df_sim,
    aes(
      x = Time,
      y = Damage
    ),
    color = "red"
  )+
  facet_wrap(~No_sim)

pCi <- ggplot()+
  geom_line(
    data = df_sim,
    aes(
      x = Time,
      y = Ci
    ),
    color = "red"
  )+
  facet_wrap(~No_sim)

pCe <- ggplot()+
  geom_line(
    data = df_sim,
    aes(
      x = Time,
      y = Ce
    ),
    color = "red"
  )+
  facet_wrap(~No_sim)


p <- pS + pD + pCi
}

```

```{r fit_A_EPX_A, message=F, warning=F}

path_fig <- here::here("fig/DEBTKTD_Models")
Molecule <- "EPX"
df_data_fit_EPX <- f_import_data_DEBTKTD() |> filter(Molecule == Molecule)

NbIter <- 30000
OM_diff <- TRUE
RTOL <- 1e-7
ATOL <- 1e-6

######## A_EPX_A ##############################################################
seeds <- c(C1 = 3303, C2 = 3666, C3 = 2212)

path_A_EPX_A <- here::here("mod/Z_DEB-TKTD/A_EPX_A")

# Distrib (kr,           TruncNormal,           1,      0.2,  0.00001,     100000);

text_priors <- '
Distrib (nec,          TruncNormal,           1,      0.2,  0.01,     100);
Distrib (b,            TruncNormal,           1,      0.2,  0.001,    100);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_TKTD_tot(path_A_EPX_A, Molecule, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## B_EPX_M ##############################################################
seeds <- c(C1 = 3303, C2 = 3666, C3 = 2212)

path_B_EPX_M <- here::here("mod/Z_DEB-TKTD/B_EPX_M")

# Distrib (kr,           TruncNormal,           1,      0.2,  0.00001,     100000);

text_priors <- '
Distrib (nec,          TruncNormal,           1000,      0.2,  0.01,     100 000);
Distrib (b,            TruncNormal,           1,      0.2,  0.001,    100);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_TKTD_tot(path_B_EPX_M, Molecule, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## C_EPX_G ##############################################################
seeds <- c(C1 = 3303, C2 = 3666, C3 = 2212)

path_C_EPX_G <- here::here("mod/Z_DEB-TKTD/C_EPX_G")

# Distrib (kr,           TruncNormal,           1,      0.2,  0.00001,     100000);

text_priors <- '
Distrib (nec,          TruncNormal,           1,      0.2,  0.01,     100);
Distrib (b,            TruncNormal,           1,      0.2,  0.001,    100);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_TKTD_tot(path_C_EPX_G, Molecule, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## D_EPX_R ##############################################################
seeds <- c(C1 = 3303, C2 = 3666, C3 = 2212)

path_D_EPX_R <- here::here("mod/Z_DEB-TKTD/D_EPX_R")

# Distrib (kr,           TruncNormal,           1,      0.2,  0.00001,     100000);

text_priors <- '
Distrib (nec,          TruncNormal,           1,      0.2,  0.01,     100);
Distrib (b,            TruncNormal,           1,      0.2,  0.001,    100);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  5, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

f_In_TKTD_tot(path_D_EPX_R, Molecule, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)


```

### Estimates results

```{r}
n_data_Weight <- length(na.omit(df_data_fit_EPX$Weight))
n_data_Reproduction <- length(na.omit(df_data_fit_EPX$Reproduction))
n_data_fit <- n_data_Weight + n_data_Reproduction

######### A_EPX_A ###############################################################

MCMC_out_A_EPX_A <- f_MCSim(path_A_EPX_A)

NC_A_EPX_A <- MCMC_out_A_EPX_A$NC
Nb_param_A_EPX_A <- MCMC_out_A_EPX_A$Nb_param
Nb_experiment_A_EPX_A <- MCMC_out_A_EPX_A$Nb_experiment
Nb_iter_kept_A_EPX_A <- MCMC_out_A_EPX_A$Nb_iter_kept
N_iter_setpoint_A_EPX_A <- MCMC_out_A_EPX_A$N_iter_setpoint
L_parameters_A_EPX_A <- unique(MCMC_out_A_EPX_A$Priors$Nom)

LL_A_EPX_A <- f_get_mode(MCMC_out_A_EPX_A$df_LnData$LnData)
k_A_EPX_A <- Nb_param_A_EPX_A - 1 # On enlève le Sigma_W

BIC_A_EPX_A <- -2*LL_A_EPX_A+k_A_EPX_A*log(n_data_fit)

Summary_res_A_EPX_A <- 
  as.data.frame(MCMC_out_A_EPX_A$Summary_res)[1:length(L_parameters_A_EPX_A)] |> 
  mutate(Model = "A_EPX_A")

Summary_res_A_EPX_A

######### B_EPX_M ###############################################################

MCMC_out_B_EPX_M <- f_MCSim(path_B_EPX_M)

NC_B_EPX_M <- MCMC_out_B_EPX_M$NC
Nb_param_B_EPX_M <- MCMC_out_B_EPX_M$Nb_param
Nb_experiment_B_EPX_M <- MCMC_out_B_EPX_M$Nb_experiment
Nb_iter_kept_B_EPX_M <- MCMC_out_B_EPX_M$Nb_iter_kept
N_iter_setpoint_B_EPX_M <- MCMC_out_B_EPX_M$N_iter_setpoint
L_parameters_B_EPX_M <- unique(MCMC_out_B_EPX_M$Priors$Nom)

LL_B_EPX_M <- f_get_mode(MCMC_out_B_EPX_M$df_LnData$LnData)
k_B_EPX_M <- Nb_param_B_EPX_M - 1 # On enlève le Sigma_W

BIC_B_EPX_M <- -2*LL_B_EPX_M+k_B_EPX_M*log(n_data_fit)

Summary_res_B_EPX_M <- 
  as.data.frame(MCMC_out_B_EPX_M$Summary_res)[1:length(L_parameters_B_EPX_M)] |> 
  mutate(Model = "B_EPX_M")

Summary_res_B_EPX_M

######### C_EPX_G ###############################################################

MCMC_out_C_EPX_G <- f_MCSim(path_C_EPX_G)

NC_C_EPX_G <- MCMC_out_C_EPX_G$NC
Nb_param_C_EPX_G <- MCMC_out_C_EPX_G$Nb_param
Nb_experiment_C_EPX_G <- MCMC_out_C_EPX_G$Nb_experiment
Nb_iter_kept_C_EPX_G <- MCMC_out_C_EPX_G$Nb_iter_kept
N_iter_setpoint_C_EPX_G <- MCMC_out_C_EPX_G$N_iter_setpoint
L_parameters_C_EPX_G <- unique(MCMC_out_C_EPX_G$Priors$Nom)

LL_C_EPX_G <- f_get_mode(MCMC_out_C_EPX_G$df_LnData$LnData)
k_C_EPX_G <- Nb_param_C_EPX_G - 1 # On enlève le Sigma_W

BIC_C_EPX_G <- -2*LL_C_EPX_G+k_C_EPX_G*log(n_data_fit)

Summary_res_C_EPX_G <- 
  as.data.frame(MCMC_out_C_EPX_G$Summary_res)[1:length(L_parameters_C_EPX_G)] |> 
  mutate(Model = "C_EPX_G")

Summary_res_C_EPX_G

######### D_EPX_R ###############################################################

MCMC_out_D_EPX_R <- f_MCSim(path_D_EPX_R)

NC_D_EPX_R <- MCMC_out_D_EPX_R$NC
Nb_param_D_EPX_R <- MCMC_out_D_EPX_R$Nb_param
Nb_experiment_D_EPX_R <- MCMC_out_D_EPX_R$Nb_experiment
Nb_iter_kept_D_EPX_R <- MCMC_out_D_EPX_R$Nb_iter_kept
N_iter_setpoint_D_EPX_R <- MCMC_out_D_EPX_R$N_iter_setpoint
L_parameters_D_EPX_R <- unique(MCMC_out_D_EPX_R$Priors$Nom)

LL_D_EPX_R <- f_get_mode(MCMC_out_D_EPX_R$df_LnData$LnData)
k_D_EPX_R <- Nb_param_D_EPX_R - 1 # On enlève le Sigma_W

BIC_D_EPX_R <- -2*LL_D_EPX_R+k_D_EPX_R*log(n_data_fit)

Summary_res_D_EPX_R <- 
  as.data.frame(MCMC_out_D_EPX_R$Summary_res)[1:length(L_parameters_D_EPX_R)] |> 
  mutate(Model = "D_EPX_R")

Summary_res_D_EPX_R



list_models <- c("A_EPX_A", "B_EPX_M", "C_EPX_G", "D_EPX_R")
df_LL_BIC <- data.frame(
  Model = list_models,
  LL = round(unlist(mget(paste0("LL_", list_models))), 2),
  BIC = round(unlist(mget(paste0("BIC_", list_models))), 2)
)
```

```{r resall}
#| tbl-cap: Estimation results from all models. 

list_models <- c("A_EPX_A", "B_EPX_M", "C_EPX_G", "D_EPX_R")
list_model_summary <- mget(paste0("Summary_res_", list_models))

param_order <- c(
  "nec", "b"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = str_c(
        round(Result_mode, 3),
        " [", round(`2.5%`, 3),
        " ; ", round(`97.5%`, 3), "]"
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_model_summary %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  ) |> 
  left_join(df_LL_BIC)

df_result |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )
```

### Chains

::: panel-tabset
## A_EPX_A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_A_EPX_A
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_A_EPX_A$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## B_EPX_M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_B_EPX_M
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_B_EPX_M$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsB_EPX_M, include = F}
ggsave(
  filename="B_EPX_M_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## C_EPX_G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_C_EPX_G
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_C_EPX_G$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC_EPX_G, include = F}
ggsave(
  filename="C_EPX_G_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```

## D_EPX_R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-chains_D_EPX_R
#| fig-height: 8
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_D_EPX_R$Chains |> 
      filter(Iteration !=1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = pal_chains)+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsD_EPX_R, include = F}
ggsave(
  filename="D_EPX_R_chains.png", 
  plot=p_chains, 
  width=8, height = 8, 
  path=path_fig
  )
```
:::

### Likelihood

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_A_EPX_A
#| fig-height: 8
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_A_EPX_A$df_LnPost_start |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_A_EPX_A$df_LnPost |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_EPX_A$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_A_EPX_A$df_Devc |> 
      filter(iteration !=1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = lab_chains, values = pal_chains) +
  labs(
    x = paste(MCMC_out_A_EPX_A$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveLLA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

### Posterior distributions

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_A_EPX_A
#| fig-height: 8
#| fig-width: 8

n_samples <- 1e5 # Simulation of the distribution

df_priors_dist <- MCMC_out_A_EPX_A$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution %in% c("TruncNormal", "TruncNormal_cv") ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples)

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_IMD

MCMC_out_A_EPX_A$Chains_plot <- MCMC_out_A_EPX_A$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) 

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_A_EPX_A$Chains_plot, Nom %in% L_parameters_A_EPX_A),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_text(face="bold")
  )

p_post
```

```{r savepostA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_post.png", 
  plot=p_post, 
  width=8, height = 8, 
  path=path_fig
  )
```

### Predicted vs. Obs

```{r}
l_param_name_A_EPX_A <- names(Summary_res_A_EPX_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.") 

f_In_predobs_TKTD(path_A_EPX_A, Molec, l_param_name_A_EPX_A)
```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-EPX DEB_setpoint_predobs_${j}.in
done
```

```{r, results=F, message=F, warning=F}

Nb_experiment <- 18

df_data_obs_EPX <- df_data_fit_EPX |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

######## A_EPX_A ###############################################################

df_pred_A_EPX_A <- f_read_predobs(path_A_EPX_A, Nb_experiment, df_data_obs_EPX)

df_pred_Weight_A_EPX_A <- subset(df_pred_A_EPX_A, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_A_EPX_A <- subset(df_pred_A_EPX_A, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_A_EPX_A <- df_data_obs_EPX |> 
  filter(Time !=0) |>
  left_join(df_pred_Reproduction_A_EPX_A, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_A_EPX_A <- df_data_obs_EPX |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_A_EPX_A, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_A_EPX_A
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)

seq_line <- seq(0.05, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_A_EPX_A,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Condition
    ),
    alpha = 0.5
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(5, 30, 0.1)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_A_EPX_A,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Condition
    ),
    alpha = 0.5
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs

```

```{r savepredobsA_EPX_A, include = F}

ggsave(
  filename = "A_EPX_A_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

### Predicted trajectories for Weight and Reproduction

```{r setpointfullin}

Nb_experiment <- 18
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Reproduction"


l_param_name_A_EPX_A <- names(Summary_res_A_EPX_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_A_EPX_A, Molec, 
  l_param_name_A_EPX_A, step_sim, Endpoints_print
  )
```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-EPX DEB_setpoint_full_${j}.in
done
```

```{r, message = F, warning = F}

width_plot <- 12
height_plot <- 12

file_rds_A_EPX_A <- file.path(path_A_EPX_A, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_A_EPX_A)) {
  df_pred_full_A_EPX_A <- readRDS(file_rds_A_EPX_A)
} else {
  df_pred_full_A_EPX_A <- f_read_Setpoint_full_TKTD(path_A_EPX_A, Molec, select_times, step_sim)
}

```

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_A_EPX_A
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  rev(nord("aurora", 12)[1:8]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)
  
  pW <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_A_EPX_A, Endpt == "Weight"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A, Endpt == "Weight"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment,
      ncol = wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 1.1))+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Earthworm growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  pR <- ggplot()+
    
    # geom_ribbon(
    #   data = subset(df_pred_full_A_EPX_A, Endpt == "Reproduction"),
    #   aes(
    #     x = Time,
    #     ymax = up,
    #     ymin = low,
    #     fill = ID_experiment
    #   ),
    #   alpha = alpha_ribbon
    # )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A, Endpt == "Reproduction"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = df_data_obs_EPX,    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.8,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~ID_experiment, 
      ncol=wrap_nb_col
      )+
    scale_y_continuous(limits = c(0, 20))+
    labs(
      x="Time (days)", 
      y = "Reproduction (#)",
      title ="Earthworm reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold")
  )
  
  

p <- pW + pR +
  plot_layout(guides = "collect") &
  guides(color = guide_legend("Experiments")) &
  theme(legend.position = "none")

p
```

```{r savetrajWRA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_trajWR.png", 
  plot=p, 
  width=width_plot, height = height_plot, 
  path=path_fig
  )
```
