```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)

pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

## Epoxiconazole

### Model fit

```{r}
Molec <- "EPX"
path_fig <- here::here("fig/DEBTKTD_Models")

# 1 pMoA
path_A_EPX_A <- here::here("mod/Z_DEB-TKTD/EPX/A_EPX_A")
path_B_EPX_M <- here::here("mod/Z_DEB-TKTD/EPX/B_EPX_M")
path_C_EPX_G <- here::here("mod/Z_DEB-TKTD/EPX/C_EPX_G")
path_D_EPX_R <- here::here("mod/Z_DEB-TKTD/EPX/D_EPX_R")

# 2 pMoA
path_E_EPX_AM <- here::here("mod/Z_DEB-TKTD/EPX/E_EPX_AM")
path_F_EPX_AG <- here::here("mod/Z_DEB-TKTD/EPX/F_EPX_AG")
path_G_EPX_AR <- here::here("mod/Z_DEB-TKTD/EPX/G_EPX_AR")
path_H_EPX_MG <- here::here("mod/Z_DEB-TKTD/EPX/H_EPX_MG")
path_I_EPX_MR <- here::here("mod/Z_DEB-TKTD/EPX/I_EPX_MR")
path_J_EPX_GR <- here::here("mod/Z_DEB-TKTD/EPX/J_EPX_GR")

df_data_fit_EPX <- f_import_data_DEBTKTD() |> 
  filter(Molecule == Molec) |> 
  mutate(No_sim = case_when(
    Experiment_type == "Repro" ~ No_sim+9,
    .default = No_sim
  ))


```

```{r fit_EPX, message=F, warning=F}

path_fig <- here::here("fig/DEBTKTD_Models")
Molec <- "EPX"
df_data_fit_EPX <- f_import_data_DEBTKTD() |> filter(Molecule == Molec)
OM_diff <- TRUE

NbIter <- 30000
RTOL <- 1e-10
ATOL <- 1e-9

text_priors <- '

Distrib (nec,          TruncNormal_cv,                50000,     0.5, 100, 10000000);
Distrib (b,            LogUniform,                0.0000001,          0.01);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  0.005, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W); 
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

######## A_EPX_A ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_A_EPX_A, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## B_EPX_M ##############################################################
seeds <- c(C1 = 3345, C2 = 6666, C3 = 2112)
f_In_TKTD_tot(path_B_EPX_M, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## C_EPX_G ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_C_EPX_G, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## D_EPX_R ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_D_EPX_R, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## E_EPX_AM ##############################################################
seeds <- c(C1 = 3345, C2 = 6666, C3 = 2112)
f_In_TKTD_tot(path_E_EPX_AM, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## F_EPX_AG ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_F_EPX_AG, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## G_EPX_AR ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_G_EPX_AR, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## H_EPX_MG ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_H_EPX_MG, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## I_EPX_MR ##############################################################
seeds <- c(C1 = 3345, C2 = 6666, C3 = 2222)
f_In_TKTD_tot(path_I_EPX_MR, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## J_EPX_GR ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_J_EPX_GR, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

# ./mcsim.DEB-EPX DEB_TKTD_C1.in

```

### Estimates results

```{r, warning=F, message=F}

n_data_Weight <- length(na.omit(df_data_fit_EPX$Weight))
n_data_Reproduction <- length(na.omit(df_data_fit_EPX$Reproduction))
n_data_fit <- n_data_Weight + n_data_Reproduction

######### A_EPX_A ###############################################################

MCMC_out_A_EPX_A <- f_MCSim(path_A_EPX_A)

NC_A_EPX_A <- MCMC_out_A_EPX_A$NC
Nb_param_A_EPX_A <- MCMC_out_A_EPX_A$Nb_param
Nb_experiment_A_EPX_A <- MCMC_out_A_EPX_A$Nb_experiment
Nb_iter_kept_A_EPX_A <- MCMC_out_A_EPX_A$Nb_iter_kept
N_iter_setpoint_A_EPX_A <- MCMC_out_A_EPX_A$N_iter_setpoint
L_parameters_A_EPX_A <- unique(MCMC_out_A_EPX_A$Priors$Nom)

LL_A_EPX_A <- f_get_mode(MCMC_out_A_EPX_A$df_LnData$LnData)
k_A_EPX_A <- Nb_param_A_EPX_A - 1 # On enlève le Sigma_W

BIC_A_EPX_A <- -2*LL_A_EPX_A+k_A_EPX_A*log(n_data_fit)

Summary_res_A_EPX_A <- 
  as.data.frame(MCMC_out_A_EPX_A$Summary_res)[1:length(L_parameters_A_EPX_A)] |>
  mutate(Model = "A_EPX_A")

#Summary_res_A_EPX_A

######### B_EPX_M ###############################################################

MCMC_out_B_EPX_M <- f_MCSim(path_B_EPX_M)

NC_B_EPX_M <- MCMC_out_B_EPX_M$NC
Nb_param_B_EPX_M <- MCMC_out_B_EPX_M$Nb_param
Nb_experiment_B_EPX_M <- MCMC_out_B_EPX_M$Nb_experiment
Nb_iter_kept_B_EPX_M <- MCMC_out_B_EPX_M$Nb_iter_kept
N_iter_setpoint_B_EPX_M <- MCMC_out_B_EPX_M$N_iter_setpoint
L_parameters_B_EPX_M <- unique(MCMC_out_B_EPX_M$Priors$Nom)

LL_B_EPX_M <- f_get_mode(MCMC_out_B_EPX_M$df_LnData$LnData)
k_B_EPX_M <- Nb_param_B_EPX_M - 1 # On enlève le Sigma_W

BIC_B_EPX_M <- -2*LL_B_EPX_M+k_B_EPX_M*log(n_data_fit)

Summary_res_B_EPX_M <-
  as.data.frame(MCMC_out_B_EPX_M$Summary_res)[1:length(L_parameters_B_EPX_M)] |>
  mutate(Model = "B_EPX_M")

# Summary_res_B_EPX_M

######### C_EPX_G ###############################################################

MCMC_out_C_EPX_G <- f_MCSim(path_C_EPX_G)

NC_C_EPX_G <- MCMC_out_C_EPX_G$NC
Nb_param_C_EPX_G <- MCMC_out_C_EPX_G$Nb_param
Nb_experiment_C_EPX_G <- MCMC_out_C_EPX_G$Nb_experiment
Nb_iter_kept_C_EPX_G <- MCMC_out_C_EPX_G$Nb_iter_kept
N_iter_setpoint_C_EPX_G <- MCMC_out_C_EPX_G$N_iter_setpoint
L_parameters_C_EPX_G <- unique(MCMC_out_C_EPX_G$Priors$Nom)

LL_C_EPX_G <- f_get_mode(MCMC_out_C_EPX_G$df_LnData$LnData)
k_C_EPX_G <- Nb_param_C_EPX_G - 1 # On enlève le Sigma_W

BIC_C_EPX_G <- -2*LL_C_EPX_G+k_C_EPX_G*log(n_data_fit)

Summary_res_C_EPX_G <- 
  as.data.frame(MCMC_out_C_EPX_G$Summary_res)[1:length(L_parameters_C_EPX_G)] |> 
  mutate(Model = "C_EPX_G")

#Summary_res_C_EPX_G

######### D_EPX_R ###############################################################

MCMC_out_D_EPX_R <- f_MCSim(path_D_EPX_R)

NC_D_EPX_R <- MCMC_out_D_EPX_R$NC
Nb_param_D_EPX_R <- MCMC_out_D_EPX_R$Nb_param
Nb_experiment_D_EPX_R <- MCMC_out_D_EPX_R$Nb_experiment
Nb_iter_kept_D_EPX_R <- MCMC_out_D_EPX_R$Nb_iter_kept
N_iter_setpoint_D_EPX_R <- MCMC_out_D_EPX_R$N_iter_setpoint
L_parameters_D_EPX_R <- unique(MCMC_out_D_EPX_R$Priors$Nom)

LL_D_EPX_R <- f_get_mode(MCMC_out_D_EPX_R$df_LnData$LnData)
k_D_EPX_R <- Nb_param_D_EPX_R - 1 # On enlève le Sigma_W

BIC_D_EPX_R <- -2*LL_D_EPX_R+k_D_EPX_R*log(n_data_fit)

Summary_res_D_EPX_R <- 
  as.data.frame(MCMC_out_D_EPX_R$Summary_res)[1:length(L_parameters_D_EPX_R)] |>
  mutate(Model = "D_EPX_R")

#Summary_res_D_EPX_R

######### E_EPX_AM ###############################################################

MCMC_out_E_EPX_AM <- f_MCSim(path_E_EPX_AM)

NC_E_EPX_AM <- MCMC_out_E_EPX_AM$NC
Nb_param_E_EPX_AM <- MCMC_out_E_EPX_AM$Nb_param
Nb_experiment_E_EPX_AM <- MCMC_out_E_EPX_AM$Nb_experiment
Nb_iter_kept_E_EPX_AM <- MCMC_out_E_EPX_AM$Nb_iter_kept
N_iter_setpoint_E_EPX_AM <- MCMC_out_E_EPX_AM$N_iter_setpoint
L_parameters_E_EPX_AM <- unique(MCMC_out_E_EPX_AM$Priors$Nom)

LL_E_EPX_AM <- f_get_mode(MCMC_out_E_EPX_AM$df_LnData$LnData)
k_E_EPX_AM <- Nb_param_E_EPX_AM - 1 # On enlève le Sigma_W

BIC_E_EPX_AM <- -2*LL_E_EPX_AM+k_E_EPX_AM*log(n_data_fit)

Summary_res_E_EPX_AM <- 
  as.data.frame(MCMC_out_E_EPX_AM$Summary_res)[1:length(L_parameters_E_EPX_AM)] |>
  mutate(Model = "E_EPX_AM")

######### F_EPX_AG ###############################################################

MCMC_out_F_EPX_AG <- f_MCSim(path_F_EPX_AG)

NC_F_EPX_AG <- MCMC_out_F_EPX_AG$NC
Nb_param_F_EPX_AG <- MCMC_out_F_EPX_AG$Nb_param
Nb_experiment_F_EPX_AG <- MCMC_out_F_EPX_AG$Nb_experiment
Nb_iter_kept_F_EPX_AG <- MCMC_out_F_EPX_AG$Nb_iter_kept
N_iter_setpoint_F_EPX_AG <- MCMC_out_F_EPX_AG$N_iter_setpoint
L_parameters_F_EPX_AG <- unique(MCMC_out_F_EPX_AG$Priors$Nom)

LL_F_EPX_AG <- f_get_mode(MCMC_out_F_EPX_AG$df_LnData$LnData)
k_F_EPX_AG <- Nb_param_F_EPX_AG - 1 # On enlève le Sigma_W

BIC_F_EPX_AG <- -2*LL_F_EPX_AG+k_F_EPX_AG*log(n_data_fit)

Summary_res_F_EPX_AG <- 
  as.data.frame(MCMC_out_F_EPX_AG$Summary_res)[1:length(L_parameters_F_EPX_AG)] |>
  mutate(Model = "F_EPX_AG")

######### G_EPX_AR ###############################################################

MCMC_out_G_EPX_AR <- f_MCSim(path_G_EPX_AR)

NC_G_EPX_AR <- MCMC_out_G_EPX_AR$NC
Nb_param_G_EPX_AR <- MCMC_out_G_EPX_AR$Nb_param
Nb_experiment_G_EPX_AR <- MCMC_out_G_EPX_AR$Nb_experiment
Nb_iter_kept_G_EPX_AR <- MCMC_out_G_EPX_AR$Nb_iter_kept
N_iter_setpoint_G_EPX_AR <- MCMC_out_G_EPX_AR$N_iter_setpoint
L_parameters_G_EPX_AR <- unique(MCMC_out_G_EPX_AR$Priors$Nom)

LL_G_EPX_AR <- f_get_mode(MCMC_out_G_EPX_AR$df_LnData$LnData)
k_G_EPX_AR <- Nb_param_G_EPX_AR - 1 # On enlève le Sigma_W

BIC_G_EPX_AR <- -2*LL_G_EPX_AR+k_G_EPX_AR*log(n_data_fit)

Summary_res_G_EPX_AR <- 
  as.data.frame(MCMC_out_G_EPX_AR$Summary_res)[1:length(L_parameters_G_EPX_AR)] |>
  mutate(Model = "G_EPX_AR")

#Summary_res_G_EPX_AR

######### H_EPX_MG ###############################################################

MCMC_out_H_EPX_MG <- f_MCSim(path_H_EPX_MG)

NC_H_EPX_MG <- MCMC_out_H_EPX_MG$NC
Nb_param_H_EPX_MG <- MCMC_out_H_EPX_MG$Nb_param
Nb_experiment_H_EPX_MG <- MCMC_out_H_EPX_MG$Nb_experiment
Nb_iter_kept_H_EPX_MG <- MCMC_out_H_EPX_MG$Nb_iter_kept
N_iter_setpoint_H_EPX_MG <- MCMC_out_H_EPX_MG$N_iter_setpoint
L_parameters_H_EPX_MG <- unique(MCMC_out_H_EPX_MG$Priors$Nom)

LL_H_EPX_MG <- f_get_mode(MCMC_out_H_EPX_MG$df_LnData$LnData)
k_H_EPX_MG <- Nb_param_H_EPX_MG - 1 # On enlève le Sigma_W

BIC_H_EPX_MG <- -2*LL_H_EPX_MG+k_H_EPX_MG*log(n_data_fit)

Summary_res_H_EPX_MG <- 
  as.data.frame(MCMC_out_H_EPX_MG$Summary_res)[1:length(L_parameters_H_EPX_MG)] |>
  mutate(Model = "H_EPX_MG")

#Summary_res_H_EPX_MG

######### I_EPX_MR ###############################################################

MCMC_out_I_EPX_MR <- f_MCSim(path_I_EPX_MR)

NC_I_EPX_MR <- MCMC_out_I_EPX_MR$NC
Nb_param_I_EPX_MR <- MCMC_out_I_EPX_MR$Nb_param
Nb_experiment_I_EPX_MR <- MCMC_out_I_EPX_MR$Nb_experiment
Nb_iter_kept_I_EPX_MR <- MCMC_out_I_EPX_MR$Nb_iter_kept
N_iter_setpoint_I_EPX_MR <- MCMC_out_I_EPX_MR$N_iter_setpoint
L_parameters_I_EPX_MR <- unique(MCMC_out_I_EPX_MR$Priors$Nom)

LL_I_EPX_MR <- f_get_mode(MCMC_out_I_EPX_MR$df_LnData$LnData)
k_I_EPX_MR <- Nb_param_I_EPX_MR - 1 # On enlève le Sigma_W

BIC_I_EPX_MR <- -2*LL_I_EPX_MR+k_I_EPX_MR*log(n_data_fit)

Summary_res_I_EPX_MR <- 
  as.data.frame(MCMC_out_I_EPX_MR$Summary_res)[1:length(L_parameters_I_EPX_MR)] |>
  mutate(Model = "I_EPX_MR")

#Summary_res_I_EPX_MR

######### J_EPX_GR ###############################################################

MCMC_out_J_EPX_GR <- f_MCSim(path_J_EPX_GR)

NC_J_EPX_GR <- MCMC_out_J_EPX_GR$NC
Nb_param_J_EPX_GR <- MCMC_out_J_EPX_GR$Nb_param
Nb_experiment_J_EPX_GR <- MCMC_out_J_EPX_GR$Nb_experiment
Nb_iter_kept_J_EPX_GR <- MCMC_out_J_EPX_GR$Nb_iter_kept
N_iter_setpoint_J_EPX_GR <- MCMC_out_J_EPX_GR$N_iter_setpoint
L_parameters_J_EPX_GR <- unique(MCMC_out_J_EPX_GR$Priors$Nom)

LL_J_EPX_GR <- f_get_mode(MCMC_out_J_EPX_GR$df_LnData$LnData)
k_J_EPX_GR <- Nb_param_J_EPX_GR - 1 # On enlève le Sigma_W

BIC_J_EPX_GR <- -2*LL_J_EPX_GR+k_J_EPX_GR*log(n_data_fit)

Summary_res_J_EPX_GR <- 
  as.data.frame(MCMC_out_J_EPX_GR$Summary_res)[1:length(L_parameters_J_EPX_GR)] |>
  mutate(Model = "J_EPX_GR")

list_models <- c("A_EPX_A", "B_EPX_M", "C_EPX_G", "D_EPX_R", 
                 "E_EPX_AM", "F_EPX_AG", "G_EPX_AR", "H_EPX_MG", "I_EPX_MR", "J_EPX_GR")
df_LL_BIC <- data.frame(
  Model = list_models,
  LL = round(unlist(mget(paste0("LL_", list_models))), 2),
  BIC = round(unlist(mget(paste0("BIC_", list_models))), 2)
)
```

```{r resall, warning=F, message=F}
#| tbl-cap: Estimation results from all models.
#| label: tbl-ResEPX 

list_models <- c("A_EPX_A", "B_EPX_M", "C_EPX_G", "D_EPX_R", 
                 "E_EPX_AM", "F_EPX_AG", "G_EPX_AR", "H_EPX_MG", "I_EPX_MR", "J_EPX_GR")
list_model_summary <- mget(paste0("Summary_res_", list_models))

param_order <- c(
  "nec", "b"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = if_else(
        param == "b",
        str_c(
          formatC(Result_mode, format = "e", digits = 2),
          " [", formatC(`2.5%`, format = "e", digits = 2),
          " ; ", formatC(`97.5%`, format = "e", digits = 2), "]"
        ),
        str_c(
          round(Result_mode, 3),
          " [", round(`2.5%`, 3),
          " ; ", round(`97.5%`, 3), "]"
        )
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_model_summary %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  ) |> 
  left_join(df_LL_BIC) |> 
  arrange(BIC)

df_result |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )
```

For epoxiconazole, comparison of the candidate physiological modes of action did not clearly discriminate among the three best-supported formulations (@tbl-ResEPX). The lowest BIC was obtained for the assimilation and reproduction pMoA (BIC = -84.5), closely followed by the growth and reproduction model (BIC = -84.4; $\Delta\mathrm{BIC}=0.1$) and the assimilation and growth model (BIC = -83.7; $\Delta\mathrm{BIC}=0.8$). These three formulations therefore received essentially equivalent support from the data. The assimilation-only model also remained plausible (BIC = -83.3; $\Delta\mathrm{BIC}=1.2$), whereas models combining maintenance with reproduction or assimilation received less support, with BIC values of -81.5 and -80.7, respectively. Although the assimilation and reproduction formulation had the lowest BIC and was retained for subsequent analyses, its advantage over the other best-performing models was marginal. The available data therefore support several alternative representations of epoxiconazole effects and do not allow a clear distinction between direct effects on assimilation, growth, and reproduction.

The selected assimilation and reproduction model estimated a no-effect concentration ($c_0$) of 47,992 \[15,105; 100,090\] ng$\cdot$g$^{-1}$ internal concentration and a stress slope parameter ($b$) of $2.4 \times 10^{-6}$ \[$9.7 \times 10^{-7}$ ; $5.5 \times 10^{-6}$\] g$\cdot$ng$^{-1}$. The broad credible interval around $c_0$ indicates substantial uncertainty in the internal concentration at which toxic stress begins. Although $b$ was comparatively better constrained, its credible interval also indicates uncertainty in the subsequent increase in stress above the no-effect concentration.

### Chains

Chains are plotted for all models.

::: panel-tabset
## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_A_EPX_A
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_A_EPX_A)
p_chains
  
```

```{r savechainsA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_B_EPX_M
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_B_EPX_M)
p_chains
  
```

```{r savechainsB_EPX_M, include = F}
ggsave(
  filename="B_EPX_M_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_C_EPX_G
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_C_EPX_G)
p_chains
  
```

```{r savechainsC_EPX_G, include = F}
ggsave(
  filename="C_EPX_G_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_D_EPX_R
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_D_EPX_R)
p_chains
  
```

```{r savechainsD_EPX_R, include = F}
ggsave(
  filename="D_EPX_R_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A & M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_E_EPX_AM
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_E_EPX_AM)
p_chains
  
```

```{r savechainsE_EPX_AM, include = F}
ggsave(
  filename="E_EPX_AM_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_F_EPX_AG
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_F_EPX_AG)
p_chains
  
```

```{r savechainsF_EPX_AG, include = F}
ggsave(
  filename="F_EPX_AG_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_G_EPX_AR
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_G_EPX_AR)
p_chains
  
```

```{r savechainsG_EPX_AR, include = F}
ggsave(
  filename="G_EPX_AR_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## M & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_H_EPX_MG
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_H_EPX_MG)
p_chains
  
```

```{r savechainsH_EPX_MG, include = F}
ggsave(
  filename="H_EPX_MG_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## M & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_I_EPX_MR
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_I_EPX_MR)
p_chains
  
```

```{r savechainsI_EPX_MR, include = F}
ggsave(
  filename="I_EPX_MR_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## G & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_J_EPX_GR
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_J_EPX_GR)
p_chains
  
```

```{r savechainsJ_EPX_GR, include = F}
ggsave(
  filename="J_EPX_GR_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```
:::

### Likelihood

::: panel-tabset
## A & R

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_G_EPX_AR
#| fig-height: 8
#| fig-width: 8


p_LL <- f_Plots_MCMC_Likelihood(MCMC_out_G_EPX_AR)
p_LL

```

```{r saveLLG_EPX_AR, include = F}
ggsave(
  filename="G_EPX_AR_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_A_EPX_A
#| fig-height: 8
#| fig-width: 8

p_LL <- f_Plots_MCMC_Likelihood(MCMC_out_A_EPX_A)
p_LL
```

```{r saveLLA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```
:::

## Chains convergence

::: panel-tabset
## A & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_G_EPX_AR
#| fig-height: 8
#| fig-width: 8

gelman <- f_Plot_Convergence(MCMC_out_G_EPX_AR)
print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_G_EPX_AR
#| fig-height: 5
#| fig-width: 6

file_rds <- here::here("fig/DEBTKTD_Models/G_EPX_AR_ipairs_plot.png")

f_Plot_ipairs(MCMC_out_G_EPX_AR, file_rds)

```

```{r, include = F}

col_corr <- colorRampPalette(c(
  "#BF616A",  # corrélations négatives
  "white",
  "#5E81AC"   # corrélations positives
))(200)

params_keep <- c("nec.1.", "b.1.")

mcmc_list_corr_G_EPX_AR <- f_mcmc_list_corr(MCMC_out_G_EPX_AR)

df_corr_G_EPX_AR <- cor(as.matrix(mcmc_list_corr_G_EPX_AR)[, params_keep])

dimnames(df_corr_G_EPX_AR) <- lapply(
  dimnames(df_corr_G_EPX_AR),
  \(x) gsub("\\.1\\.$", "", x)
)

png(file.path(path_fig, "G_EPX_AR_corrplot_article.png"), width = 2000, height = 2000, res = 300)

op <- par(font = 2)

corrplot.mixed(
  df_corr_G_EPX_AR,
  lower = "ellipse",
  upper = "number",
  tl.col = "#2E3440",
  tl.cex = 0.6,
  tl.pos = "d",
  number.cex = 0.7,
  tl.srt = 45,
  lower.col = col_corr,
  upper.col = col_corr
)

par(op)

dev.off()

```

## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_A_EPX_A
#| fig-height: 8
#| fig-width: 8

gelman <- f_Plot_Convergence(MCMC_out_A_EPX_A)
print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_A_EPX_A
#| fig-height: 5
#| fig-width: 6

file_rds <- here::here("fig/DEBTKTD_Models/A_EPX_A_ipairs_plot.png")

f_Plot_ipairs(MCMC_out_A_EPX_A, file_rds)
```
:::

A moderate positive correlation was observed for epoxiconazole ($r=0.64$), suggesting partial parameter dependence and greater difficulty in independently identifying the tolerance threshold and stress slope from the available data (Supplementary Information @fig-corr_G_EPX_AR).

## Posterior distributions

::: panel-tabset
## A & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_G_EPX_AR
#| fig-height: 4
#| fig-width: 8

p_post <- f_Plot_Posteriors(MCMC_out_G_EPX_AR)
p_post
```

```{r savepostG_EPX_AR, include = F}
ggsave(
  filename="G_EPX_AR_post.png", 
  plot=p_post, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_A_EPX_A
#| fig-height: 4
#| fig-width: 8

p_post <- f_Plot_Posteriors(MCMC_out_A_EPX_A)
p_post
```

```{r savepostA_EPX_A, include = F}
ggsave(
  filename="A_EPX_A_post.png", 
  plot=p_post, 
  width=8, height = 4, 
  path=path_fig
  )
```
:::

## Predicted vs. Obs

```{r}
l_param_name_G_EPX_AR <- names(Summary_res_G_EPX_AR) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.") 

f_In_predobs_TKTD(path_G_EPX_AR, Molec, l_param_name_G_EPX_AR)

l_param_name_A_EPX_A <- names(Summary_res_A_EPX_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.") 

f_In_predobs_TKTD(path_A_EPX_A, Molec, l_param_name_A_EPX_A)

```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-EPX DEB_setpoint_predobs_${j}.in
done
```

```{r, results=F, message=F, warning=F}

Nb_experiment <- 18

df_data_obs_EPX <- df_data_fit_EPX |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

Condition_order <- c(
  "Control", "C1", "C2", "C3", "C4", "C5",
  "C6", "C7", "C8"
)

######## G_EPX_AR ###############################################################

df_pred_G_EPX_AR <- f_read_predobs(path_G_EPX_AR, Nb_experiment, df_data_obs_EPX)

df_pred_Weight_G_EPX_AR <- subset(df_pred_G_EPX_AR, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_G_EPX_AR <- subset(df_pred_G_EPX_AR, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_G_EPX_AR <- df_data_obs_EPX |> 
  filter(Time !=0 & Reproduction_obs != 0) |>
  left_join(df_pred_Reproduction_G_EPX_AR, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()|> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

df_predobs_Weight_G_EPX_AR <- df_data_obs_EPX |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_G_EPX_AR, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()|> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

######## A_EPX_A ###############################################################

df_pred_A_EPX_A <- f_read_predobs(path_A_EPX_A, Nb_experiment, df_data_obs_EPX)

df_pred_Weight_A_EPX_A <- subset(df_pred_A_EPX_A, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_A_EPX_A <- subset(df_pred_A_EPX_A, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_A_EPX_A <- df_data_obs_EPX |> 
  filter(Time !=0 & Reproduction_obs != 0) |>
  left_join(df_pred_Reproduction_A_EPX_A, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()|> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

df_predobs_Weight_A_EPX_A <- df_data_obs_EPX |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_A_EPX_A, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()|> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

```

::: panel-tabset
## A & R

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_G_EPX_AR
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exp1 <- c(
  rev(nord("aurora", 12)[1:9]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)

seq_line <- seq(0.05, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_G_EPX_AR,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Condition
    ),
    alpha = 0.7
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(1, 15, 0.1)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_G_EPX_AR,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Condition
    ),
    alpha = 0.7
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()+
  theme(
    legend.position = "none"
  )

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs

```

```{r savepredobsG_EPX_AR, include = F}
ggsave(
  filename = "G_EPX_AR_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

## A

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_A_EPX_A
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exp1 <- c(
  rev(nord("aurora", 12)[1:9]),
  Nord_aurora[4]
)

col_experiment <- rep(col_exp1, 2)

seq_line <- seq(0.05, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_A_EPX_A,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Condition
    ),
    alpha = 0.7
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(1, 15, 0.1)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_A_EPX_A,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Condition
    ),
    alpha = 0.7
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()+
  theme(
    legend.position = "none"
  )

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs

```

```{r savepredobsA_EPX_A, include = F}
ggsave(
  filename = "A_EPX_A_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```
:::

## Predicted trajectories for Weight and Reproduction

```{r setpointfullin}

Nb_experiment <- 18
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Reproduction"


l_param_name_G_EPX_AR <- names(Summary_res_G_EPX_AR) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_G_EPX_AR, Molec, 
  l_param_name_G_EPX_AR, step_sim, Endpoints_print
  )


l_param_name_A_EPX_A <- names(Summary_res_A_EPX_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_A_EPX_A, Molec, 
  l_param_name_A_EPX_A, step_sim, Endpoints_print
  )

```

```{bash, eval=F, execute=F}
for j in $(seq 1 18); do
./mcsim.DEB-EPX DEB_setpoint_full_${j}.in
done
```

```{r, message = F, warning = F}

width_plot <- 12
height_plot <- 12

file_rds_G_EPX_AR <- file.path(path_G_EPX_AR, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_G_EPX_AR)) {
  df_pred_full_G_EPX_AR <- readRDS(file_rds_G_EPX_AR)
} else {
  df_pred_full_G_EPX_AR <- f_read_Setpoint_full_TKTD(path_G_EPX_AR, Molec, select_times, step_sim)
}

file_rds_A_EPX_A <- file.path(path_A_EPX_A, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_A_EPX_A)) {
  df_pred_full_A_EPX_A <- readRDS(file_rds_A_EPX_A)
} else {
  df_pred_full_A_EPX_A <- f_read_Setpoint_full_TKTD(path_A_EPX_A, Molec, select_times, step_sim)
}

######### Plot preparation #####################################################

Condition_order <- c(
  "Control", "C1", "C2", "C3", "C4", "C5",
  "C6", "C7", "C8"
)

df_Exp_type_Dose_Condition_G <- df_data_obs_EPX |> 
  filter(Experiment_type == "Growth") |> 
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |> 
  distinct() |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

df_Exp_type_Dose_Condition_R <- df_data_obs_EPX |> 
  filter(Experiment_type == "Repro") |> 
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |> 
  distinct() |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

ID_levels_growth <- df_Exp_type_Dose_Condition_G |> 
  filter(Experiment_type == "Growth") |> 
  arrange(Condition) |> 
  pull(ID_experiment)

Facet_levels_growth <- df_Exp_type_Dose_Condition_G |> 
  filter(Experiment_type == "Growth") |> 
  arrange(Condition) |> 
  mutate(Facet_label = paste(Condition, ":", Dose/1000, "mg/kg")) |> 
  pull(Facet_label)

ID_levels_repro <- df_Exp_type_Dose_Condition_R |> 
  filter(Experiment_type == "Repro") |> 
  arrange(Condition) |> 
  pull(ID_experiment)

Facet_levels_repro <- df_Exp_type_Dose_Condition_R |> 
  filter(Experiment_type == "Repro") |> 
  arrange(Condition) |> 
  mutate(Facet_label = paste(Condition, ":", Dose/1000, "mg/kg")) |> 
  pull(Facet_label)

df_data_obs_EPX_G <- df_data_obs_EPX |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_data_obs_EPX_R <- df_data_obs_EPX |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )

######### G_EPX_AR ############################################################
df_pred_full_G_EPX_AR_plot_G <- df_pred_full_G_EPX_AR |> 
  left_join(
    df_Exp_type_Dose_Condition_G,
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_pred_full_G_EPX_AR_plot_R <- df_pred_full_G_EPX_AR |> 
  left_join(
    df_Exp_type_Dose_Condition_R,
    by = c("ID_experiment")
  ) |> 
  filter(Experiment_type == "Repro") |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )

######### G_EPX_AR ############################################################
df_pred_full_A_EPX_A_plot_G <- df_pred_full_A_EPX_A |> 
  left_join(
    df_Exp_type_Dose_Condition_G,
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_pred_full_A_EPX_A_plot_R <- df_pred_full_A_EPX_A |> 
  left_join(
    df_Exp_type_Dose_Condition_R,
    by = c("ID_experiment")
  ) |> 
  filter(Experiment_type == "Repro") |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )

```

::: panel-tabset
## A & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_G_EPX_ARsummary
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  max_WG <- 0.55
  max_WR <- 1.1
  max_RR <- 10
  
col_exp1 <- c(
  Nord_aurora[4],
  rev(nord("aurora", 12)[1:10])
)

col_experiment <- rep(col_exp1, 2)
  
  pW_G <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_G_EPX_AR_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_G_EPX_AR_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_G, Experiment_type == "Growth"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on juvenile growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
  pW_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on adult growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
   pR_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Cumulated reproduction (#)",
      title ="Effect of epoxiconazole on reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

p_WR_R <- pW_R + pR_R 

p_WR_summary <- pW_G + pW_R + pR_R +
  plot_layout(ncol=3)

p_WR_summary

```

```{r savetrajWRG_EPX_AR_summary, include = F}
ggsave(
  filename="G_EPX_AR_trajWR_G.png", 
  plot=pW_G, 
  width=6, height = 6, 
  path=path_fig
  )

ggsave(
  filename="G_EPX_AR_trajWR_R.png", 
  plot=p_WR_R, 
  width=12, height = 6, 
  path=path_fig
  )
ggsave(
  filename="G_EPX_AR_trajWR_summary.png", 
  plot=p_WR_summary, 
  width=12, height = 9, 
  path=path_fig
  )
```

## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_A_EPX_Asummary
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  Nord_aurora[4],
  rev(nord("aurora", 12)[1:10])
)

col_experiment <- rep(col_exp1, 2)
  
  pW_G <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_A_EPX_A_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_G, Experiment_type == "Growth"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on juvenile growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
  pW_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_A_EPX_A_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on adult growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
   pR_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_A_EPX_A_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_EPX_A_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Cumulated reproduction (#)",
      title ="Effect of epoxiconazole on reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

p_WR_R <- pW_R + pR_R 

p_WR_summary <- pW_G + pW_R + pR_R +
  plot_layout(ncol=3)
p_WR_summary

```

```{r savetrajWRA_EPX_A_summary, include = F}
ggsave(
  filename="A_EPX_A_trajWR_G.png", 
  plot=pW_G, 
  width=6, height = 6, 
  path=path_fig
  )

ggsave(
  filename="A_EPX_A_trajWR_R.png", 
  plot=p_WR_R, 
  width=12, height = 6, 
  path=path_fig
  )
ggsave(
  filename="A_EPX_A_trajWR_summary.png", 
  plot=p_WR_summary, 
  width=12, height = 9, 
  path=path_fig
  )
```
:::

Overall, the selected DEB-TKTD model reproduced the concentration-dependent responses observed for juvenile growth, adult growth, and reproduction (@fig-pred_G_EPX_ARsummary & @fig-predobs_G_EPX_AR). The model captured the general magnitude and shape of the decline in life-history performance with increasing epoxiconazole exposure. However, some systematic deviations remained. Growth effects were underestimated at the lowest tested concentrations, between 0.928 and 9.28 mg$\cdot$kg$^{-1}$, resulting in predicted growth values above the observations. Reproductive effects were also underestimated at the highest concentrations, between 43.1 and 200 mg$\cdot$kg$^{-1}$, with predicted cocoon production exceeding the observed values. Despite these discrepancies, the combined assimilation and reproduction pMoA provided an overall satisfactory description of epoxiconazole effects across the three endpoints.

## Summary

```{r, message=F, warning=F}
EPX_low_doses <- c(0, 928, 2000)
EPX_int_doses <- c(4300, 9280, 20000)
EPX_high_doses <- c(43100, 92800, 200000)

Dose_level_levels <- c("Low doses", "Intermediate doses", "High doses")


df_pred_full_G_EPX_AR_plot_G <- df_pred_full_G_EPX_AR_plot_G |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% EPX_low_doses ~ "Low doses",
      Dose %in% EPX_int_doses ~ "Intermediate doses",
      Dose %in% EPX_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

df_data_obs_EPX_G <- df_data_obs_EPX_G |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% EPX_low_doses ~ "Low doses",
      Dose %in% EPX_int_doses ~ "Intermediate doses",
      Dose %in% EPX_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

df_pred_full_G_EPX_AR_plot_R <- df_pred_full_G_EPX_AR_plot_R |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% EPX_low_doses ~ "Low doses",
      Dose %in% EPX_int_doses ~ "Intermediate doses",
      Dose %in% EPX_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

df_data_obs_EPX_R <- df_data_obs_EPX_R |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% EPX_low_doses ~ "Low doses",
      Dose %in% EPX_int_doses ~ "Intermediate doses",
      Dose %in% EPX_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

```

```{r, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each experiment.
#| label: fig-pred_G_EPX_AR_summary_article
#| fig-height: 10
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  alpha_point <- 0.9
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 1
  max_WG <- 0.55
  max_WR <- 1.1
  max_RR <- 10
  

col_experiment <- c(
  # Low doses
  "#4C566A", #"#DDE8D3",
  "#A3BE8C",
  "#718A5C",

  # Intermediate doses
  "#F2DFA3",
  "#E2B984",
  "#D08770",

  # High doses
  "#E4B6B9",
  "#BF616A",
  "#91434C"
)

  
  pW_G <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_G_EPX_AR_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_G_EPX_AR_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_G, Experiment_type == "Growth"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = alpha_point,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Condition",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Condition",
      values = col_experiment
      )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on juvenile growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none",
    strip.text = element_blank()
  )
  
  pW_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = alpha_point,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Condition",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Condition",
      values = col_experiment
      )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on adult growth"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
   pR_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = Facet_label
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_G_EPX_AR_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = Facet_label
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_EPX_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = Facet_label  
        ),
      alpha = alpha_point,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Conditions",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Conditions",
      values = col_experiment
      )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Cumulated reproduction (#)",
      title ="Effect of epoxiconazole on reproduction"
    )+
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.title = element_text(face = "bold"),
    strip.text = element_blank()
  )

p_WR_R <- pW_R + pR_R 

p_WR_summary <- pW_G + pW_R + pR_R +
  plot_layout(ncol=3)

p_WR_summary

```

```{r savetrajWRG_EPX_AR_article, include = F}
ggsave(
  filename="G_EPX_AR_trajWR_article.png", 
  plot=p_WR_summary, 
  width=12, height = 8, 
  path=path_fig
  )
```
