```{r lib, include = F}
library(here)
source(file = here::here("functions/fun.R"))
source(file = here::here("functions/fun_MCSim.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)

pal_chains <- c(Nord_aurora, Nord_frost, Nord_polar)
lab_chains <- c("1", "2", "3", "4", "5", "6", "7", "8")
```

# Imidacloprid

```{r, warning=F, message=F}
Condition_order <- c("Ctrl", "C1", "C2", "C3", "C4", "C5", "C6", "C7", "C8", "C9", "C10")

df_data_EC50 <- f_import_data_DEBTKTD() |> 
  mutate(
    #Condition = fct_reorder(Condition, Dose)
    Condition = fct_relevel(Condition, Condition_order)
  ) |> 
  filter(!(Experiment_type == "Repro" & Time == 14))


```

## Model fit

```{r, warning=F, message=F}
Molec <- "IMD"
path_fig <- here::here("fig/DEBTKTD_Models")

# 1 pMoA
path_A_IMD_A <- here::here("mod/Z_DEB-TKTD/IMD/A_IMD_A")
path_B_IMD_M <- here::here("mod/Z_DEB-TKTD/IMD/B_IMD_M")
path_C_IMD_G <- here::here("mod/Z_DEB-TKTD/IMD/C_IMD_G")
path_D_IMD_R <- here::here("mod/Z_DEB-TKTD/IMD/D_IMD_R")

# 2 pMoA
path_E_IMD_AM <- here::here("mod/Z_DEB-TKTD/IMD/E_IMD_AM")
path_F_IMD_AG <- here::here("mod/Z_DEB-TKTD/IMD/F_IMD_AG")
path_G_IMD_AR <- here::here("mod/Z_DEB-TKTD/IMD/G_IMD_AR")
path_H_IMD_MG <- here::here("mod/Z_DEB-TKTD/IMD/H_IMD_MG")
path_I_IMD_MR <- here::here("mod/Z_DEB-TKTD/IMD/I_IMD_MR")
path_J_IMD_GR <- here::here("mod/Z_DEB-TKTD/IMD/J_IMD_GR")

df_data_fit_IMD <- f_import_data_DEBTKTD() |> 
  filter(Molecule == Molec) |> 
  mutate(No_sim = case_when(
    Experiment_type == "Repro" ~ No_sim+9,
    .default = No_sim
  ))

```

```{r fit_IMD, message=F, warning=F}

path_fig <- here::here("fig/DEBTKTD_Models")
Molec <- "IMD"
df_data_fit_IMD <- f_import_data_DEBTKTD() |> filter(Molecule == Molec)
OM_diff <- TRUE

NbIter <- 30000
RTOL <- 1e-10
ATOL <- 1e-9

text_priors <- '
Distrib (nec,          TruncNormal_cv,            1000,     0.2, 10, 100000);
Distrib (b,            LogUniform,                0.0001,          10);

# Calcul des vraissemblances
Distrib (Sigma_W, TruncNormal,  0.005, 1, 0.01, 100);'

text_likelihood <- 'Likelihood (Weight,   Normal, Prediction(Weight), Sigma_W);  
Likelihood (Reproduction, Poisson, Prediction(Reproduction));'

######## A_IMD_A ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_A_IMD_A, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## B_IMD_M ##############################################################
seeds <- c(C1 = 3345, C2 = 6666, C3 = 2112)
f_In_TKTD_tot(path_B_IMD_M, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## C_IMD_G ##############################################################
seeds <- c(C1 = 3303, C2 = 6666, C3 = 2212)
f_In_TKTD_tot(path_C_IMD_G, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## D_IMD_R ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_D_IMD_R, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## E_IMD_AM ##############################################################
seeds <- c(C1 = 3345, C2 = 6666, C3 = 2112)
f_In_TKTD_tot(path_E_IMD_AM, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## F_IMD_AG ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_F_IMD_AG, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## G_IMD_AR ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_G_IMD_AR, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## H_IMD_MG ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_H_IMD_MG, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## I_IMD_MR ##############################################################
seeds <- c(C1 = 3345, C2 = 6666, C3 = 2222)
f_In_TKTD_tot(path_I_IMD_MR, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

######## J_IMD_GR ##############################################################
seeds <- c(C1 = 3345, C2 = 3666, C3 = 2212)
f_In_TKTD_tot(path_J_IMD_GR, Molec, text_priors, text_likelihood, NbIter, seeds, RTOL, ATOL)

# ./mcsim.DEB-IMD DEB_TKTD_C1.in

```

## Estimates results

```{r, warning=F, message=F}
n_data_Weight <- length(na.omit(df_data_fit_IMD$Weight))
n_data_Reproduction <- length(na.omit(df_data_fit_IMD$Reproduction))
n_data_fit <- n_data_Weight + n_data_Reproduction

######### A_IMD_A ###############################################################

MCMC_out_A_IMD_A <- f_MCSim(path_A_IMD_A)

NC_A_IMD_A <- MCMC_out_A_IMD_A$NC
Nb_param_A_IMD_A <- MCMC_out_A_IMD_A$Nb_param
Nb_experiment_A_IMD_A <- MCMC_out_A_IMD_A$Nb_experiment
Nb_iter_kept_A_IMD_A <- MCMC_out_A_IMD_A$Nb_iter_kept
N_iter_setpoint_A_IMD_A <- MCMC_out_A_IMD_A$N_iter_setpoint
L_parameters_A_IMD_A <- unique(MCMC_out_A_IMD_A$Priors$Nom)

LL_A_IMD_A <- f_get_mode(MCMC_out_A_IMD_A$df_LnData$LnData)
k_A_IMD_A <- Nb_param_A_IMD_A - 1 # On enlève le Sigma_W

BIC_A_IMD_A <- -2*LL_A_IMD_A+k_A_IMD_A*log(n_data_fit)

Summary_res_A_IMD_A <- 
  as.data.frame(MCMC_out_A_IMD_A$Summary_res)[1:length(L_parameters_A_IMD_A)] |> 
  mutate(Model = "A_IMD_A")

#Summary_res_A_IMD_A

######### B_IMD_M ###############################################################

MCMC_out_B_IMD_M <- f_MCSim(path_B_IMD_M)

NC_B_IMD_M <- MCMC_out_B_IMD_M$NC
Nb_param_B_IMD_M <- MCMC_out_B_IMD_M$Nb_param
Nb_experiment_B_IMD_M <- MCMC_out_B_IMD_M$Nb_experiment
Nb_iter_kept_B_IMD_M <- MCMC_out_B_IMD_M$Nb_iter_kept
N_iter_setpoint_B_IMD_M <- MCMC_out_B_IMD_M$N_iter_setpoint
L_parameters_B_IMD_M <- unique(MCMC_out_B_IMD_M$Priors$Nom)

LL_B_IMD_M <- f_get_mode(MCMC_out_B_IMD_M$df_LnData$LnData)
k_B_IMD_M <- Nb_param_B_IMD_M - 1 # On enlève le Sigma_W

BIC_B_IMD_M <- -2*LL_B_IMD_M+k_B_IMD_M*log(n_data_fit)

Summary_res_B_IMD_M <- 
  as.data.frame(MCMC_out_B_IMD_M$Summary_res)[1:length(L_parameters_B_IMD_M)] |> 
  mutate(Model = "B_IMD_M")

#Summary_res_B_IMD_M

######### C_IMD_G ###############################################################

MCMC_out_C_IMD_G <- f_MCSim(path_C_IMD_G)

NC_C_IMD_G <- MCMC_out_C_IMD_G$NC
Nb_param_C_IMD_G <- MCMC_out_C_IMD_G$Nb_param
Nb_experiment_C_IMD_G <- MCMC_out_C_IMD_G$Nb_experiment
Nb_iter_kept_C_IMD_G <- MCMC_out_C_IMD_G$Nb_iter_kept
N_iter_setpoint_C_IMD_G <- MCMC_out_C_IMD_G$N_iter_setpoint
L_parameters_C_IMD_G <- unique(MCMC_out_C_IMD_G$Priors$Nom)

LL_C_IMD_G <- f_get_mode(MCMC_out_C_IMD_G$df_LnData$LnData)
k_C_IMD_G <- Nb_param_C_IMD_G - 1 # On enlève le Sigma_W

BIC_C_IMD_G <- -2*LL_C_IMD_G+k_C_IMD_G*log(n_data_fit)

Summary_res_C_IMD_G <- 
  as.data.frame(MCMC_out_C_IMD_G$Summary_res)[1:length(L_parameters_C_IMD_G)] |> 
  mutate(Model = "C_IMD_G")

#Summary_res_C_IMD_G

######### D_IMD_R ###############################################################

MCMC_out_D_IMD_R <- f_MCSim(path_D_IMD_R)

NC_D_IMD_R <- MCMC_out_D_IMD_R$NC
Nb_param_D_IMD_R <- MCMC_out_D_IMD_R$Nb_param
Nb_experiment_D_IMD_R <- MCMC_out_D_IMD_R$Nb_experiment
Nb_iter_kept_D_IMD_R <- MCMC_out_D_IMD_R$Nb_iter_kept
N_iter_setpoint_D_IMD_R <- MCMC_out_D_IMD_R$N_iter_setpoint
L_parameters_D_IMD_R <- unique(MCMC_out_D_IMD_R$Priors$Nom)

LL_D_IMD_R <- f_get_mode(MCMC_out_D_IMD_R$df_LnData$LnData)
k_D_IMD_R <- Nb_param_D_IMD_R - 1 # On enlève le Sigma_W

BIC_D_IMD_R <- -2*LL_D_IMD_R+k_D_IMD_R*log(n_data_fit)

Summary_res_D_IMD_R <- 
  as.data.frame(MCMC_out_D_IMD_R$Summary_res)[1:length(L_parameters_D_IMD_R)] |> 
  mutate(Model = "D_IMD_R")

#Summary_res_D_IMD_R

######### E_IMD_AM ###############################################################

MCMC_out_E_IMD_AM <- f_MCSim(path_E_IMD_AM)

NC_E_IMD_AM <- MCMC_out_E_IMD_AM$NC
Nb_param_E_IMD_AM <- MCMC_out_E_IMD_AM$Nb_param
Nb_experiment_E_IMD_AM <- MCMC_out_E_IMD_AM$Nb_experiment
Nb_iter_kept_E_IMD_AM <- MCMC_out_E_IMD_AM$Nb_iter_kept
N_iter_setpoint_E_IMD_AM <- MCMC_out_E_IMD_AM$N_iter_setpoint
L_parameters_E_IMD_AM <- unique(MCMC_out_E_IMD_AM$Priors$Nom)

LL_E_IMD_AM <- f_get_mode(MCMC_out_E_IMD_AM$df_LnData$LnData)
k_E_IMD_AM <- Nb_param_E_IMD_AM - 1 # On enlève le Sigma_W

BIC_E_IMD_AM <- -2*LL_E_IMD_AM+k_E_IMD_AM*log(n_data_fit)

Summary_res_E_IMD_AM <- 
  as.data.frame(MCMC_out_E_IMD_AM$Summary_res)[1:length(L_parameters_E_IMD_AM)] |> 
  mutate(Model = "E_IMD_AM")

#Summary_res_E_IMD_AM

######### F_IMD_AG ###############################################################

MCMC_out_F_IMD_AG <- f_MCSim(path_F_IMD_AG)

NC_F_IMD_AG <- MCMC_out_F_IMD_AG$NC
Nb_param_F_IMD_AG <- MCMC_out_F_IMD_AG$Nb_param
Nb_experiment_F_IMD_AG <- MCMC_out_F_IMD_AG$Nb_experiment
Nb_iter_kept_F_IMD_AG <- MCMC_out_F_IMD_AG$Nb_iter_kept
N_iter_setpoint_F_IMD_AG <- MCMC_out_F_IMD_AG$N_iter_setpoint
L_parameters_F_IMD_AG <- unique(MCMC_out_F_IMD_AG$Priors$Nom)

LL_F_IMD_AG <- f_get_mode(MCMC_out_F_IMD_AG$df_LnData$LnData)
k_F_IMD_AG <- Nb_param_F_IMD_AG - 1 # On enlève le Sigma_W

BIC_F_IMD_AG <- -2*LL_F_IMD_AG+k_F_IMD_AG*log(n_data_fit)

Summary_res_F_IMD_AG <- 
  as.data.frame(MCMC_out_F_IMD_AG$Summary_res)[1:length(L_parameters_F_IMD_AG)] |> 
  mutate(Model = "F_IMD_AG")

#Summary_res_F_IMD_AG

######### G_IMD_AR ###############################################################

MCMC_out_G_IMD_AR <- f_MCSim(path_G_IMD_AR)

NC_G_IMD_AR <- MCMC_out_G_IMD_AR$NC
Nb_param_G_IMD_AR <- MCMC_out_G_IMD_AR$Nb_param
Nb_experiment_G_IMD_AR <- MCMC_out_G_IMD_AR$Nb_experiment
Nb_iter_kept_G_IMD_AR <- MCMC_out_G_IMD_AR$Nb_iter_kept
N_iter_setpoint_G_IMD_AR <- MCMC_out_G_IMD_AR$N_iter_setpoint
L_parameters_G_IMD_AR <- unique(MCMC_out_G_IMD_AR$Priors$Nom)

LL_G_IMD_AR <- f_get_mode(MCMC_out_G_IMD_AR$df_LnData$LnData)
k_G_IMD_AR <- Nb_param_G_IMD_AR - 1 # On enlève le Sigma_W

BIC_G_IMD_AR <- -2*LL_G_IMD_AR+k_G_IMD_AR*log(n_data_fit)

Summary_res_G_IMD_AR <- 
  as.data.frame(MCMC_out_G_IMD_AR$Summary_res)[1:length(L_parameters_G_IMD_AR)] |> 
  mutate(Model = "G_IMD_AR")

#Summary_res_G_IMD_AR

######### H_IMD_MG ###############################################################

MCMC_out_H_IMD_MG <- f_MCSim(path_H_IMD_MG)

NC_H_IMD_MG <- MCMC_out_H_IMD_MG$NC
Nb_param_H_IMD_MG <- MCMC_out_H_IMD_MG$Nb_param
Nb_experiment_H_IMD_MG <- MCMC_out_H_IMD_MG$Nb_experiment
Nb_iter_kept_H_IMD_MG <- MCMC_out_H_IMD_MG$Nb_iter_kept
N_iter_setpoint_H_IMD_MG <- MCMC_out_H_IMD_MG$N_iter_setpoint
L_parameters_H_IMD_MG <- unique(MCMC_out_H_IMD_MG$Priors$Nom)

LL_H_IMD_MG <- f_get_mode(MCMC_out_H_IMD_MG$df_LnData$LnData)
k_H_IMD_MG <- Nb_param_H_IMD_MG - 1 # On enlève le Sigma_W

BIC_H_IMD_MG <- -2*LL_H_IMD_MG+k_H_IMD_MG*log(n_data_fit)

Summary_res_H_IMD_MG <- 
  as.data.frame(MCMC_out_H_IMD_MG$Summary_res)[1:length(L_parameters_H_IMD_MG)] |> 
  mutate(Model = "H_IMD_MG")

#Summary_res_H_IMD_MG

######### I_IMD_MR ###############################################################

MCMC_out_I_IMD_MR <- f_MCSim(path_I_IMD_MR)

NC_I_IMD_MR <- MCMC_out_I_IMD_MR$NC
Nb_param_I_IMD_MR <- MCMC_out_I_IMD_MR$Nb_param
Nb_experiment_I_IMD_MR <- MCMC_out_I_IMD_MR$Nb_experiment
Nb_iter_kept_I_IMD_MR <- MCMC_out_I_IMD_MR$Nb_iter_kept
N_iter_setpoint_I_IMD_MR <- MCMC_out_I_IMD_MR$N_iter_setpoint
L_parameters_I_IMD_MR <- unique(MCMC_out_I_IMD_MR$Priors$Nom)

LL_I_IMD_MR <- f_get_mode(MCMC_out_I_IMD_MR$df_LnData$LnData)
k_I_IMD_MR <- Nb_param_I_IMD_MR - 1 # On enlève le Sigma_W

BIC_I_IMD_MR <- -2*LL_I_IMD_MR+k_I_IMD_MR*log(n_data_fit)

Summary_res_I_IMD_MR <- 
  as.data.frame(MCMC_out_I_IMD_MR$Summary_res)[1:length(L_parameters_I_IMD_MR)] |> 
  mutate(Model = "I_IMD_MR")

#Summary_res_I_IMD_MR

######### J_IMD_GR ###############################################################

MCMC_out_J_IMD_GR <- f_MCSim(path_J_IMD_GR)

NC_J_IMD_GR <- MCMC_out_J_IMD_GR$NC
Nb_param_J_IMD_GR <- MCMC_out_J_IMD_GR$Nb_param
Nb_experiment_J_IMD_GR <- MCMC_out_J_IMD_GR$Nb_experiment
Nb_iter_kept_J_IMD_GR <- MCMC_out_J_IMD_GR$Nb_iter_kept
N_iter_setpoint_J_IMD_GR <- MCMC_out_J_IMD_GR$N_iter_setpoint
L_parameters_J_IMD_GR <- unique(MCMC_out_J_IMD_GR$Priors$Nom)

LL_J_IMD_GR <- f_get_mode(MCMC_out_J_IMD_GR$df_LnData$LnData)
k_J_IMD_GR <- Nb_param_J_IMD_GR - 1 # On enlève le Sigma_W

BIC_J_IMD_GR <- -2*LL_J_IMD_GR+k_J_IMD_GR*log(n_data_fit)

Summary_res_J_IMD_GR <- 
  as.data.frame(MCMC_out_J_IMD_GR$Summary_res)[1:length(L_parameters_J_IMD_GR)] |> 
  mutate(Model = "J_IMD_GR")



list_models <- c("A_IMD_A", "B_IMD_M", "C_IMD_G", "D_IMD_R", "E_IMD_AM", "F_IMD_AG", "G_IMD_AR", "H_IMD_MG", "I_IMD_MR", "J_IMD_GR")


df_LL_BIC <- data.frame(
  Model = list_models,
  LL = round(unlist(mget(paste0("LL_", list_models))), 2),
  BIC = round(unlist(mget(paste0("BIC_", list_models))), 2)
)
```

```{r resall, warning=F, message=F}
#| tbl-cap: Estimation results from all models. 
#| label: tbl-IMDTKTDres

list_models <- c("A_IMD_A", "B_IMD_M", "C_IMD_G", "D_IMD_R", "E_IMD_AM", "F_IMD_AG", "G_IMD_AR", "H_IMD_MG", "I_IMD_MR", "J_IMD_GR")

list_model_summary <- mget(paste0("Summary_res_", list_models))

param_order <- c(
  "nec", "b"
)

format_summary <- function(df) {
  df %>%
    rename_with(~ str_remove(., "\\.1\\.$")) %>%
    rownames_to_column("stat") %>%
    pivot_longer(
      cols = -c(stat, Model),
      names_to = "param",
      values_to = "value"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    mutate(
      value = str_c(
        round(Result_mode, 4),
        " [", round(`2.5%`, 4),
        " ; ", round(`97.5%`, 4), "]"
      )
    ) %>%
    dplyr::select(Model, param, value) %>%
    pivot_wider(
      names_from = param,
      values_from = value
    )
}

df_result <- list_model_summary %>%
  map(format_summary) %>%
  bind_rows() %>%
  dplyr::select(
    Model,
    any_of(param_order),
    everything()
  ) |> 
  left_join(df_LL_BIC) |> 
  arrange(BIC)

df_result |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )
```

For imidacloprid, comparison of the candidate physiological modes of action showed that the best-supported model combined effects on assimilation and growth (@tbl-IMDTKTDres). This formulation had the lowest BIC (BIC = -64.7), followed by the growth and reproduction model (BIC = -60.7; $\Delta\mathrm{BIC}=4.0$) and the assimilation and reproduction model (BIC = -57.1; $\Delta\mathrm{BIC}=7.6$). The assimilation-only formulation received substantially less support (BIC = -49.7; $\Delta\mathrm{BIC}=15.0$). These results provide clear support for the combined assimilation and growth pMoA, while the growth and reproduction formulation remained a plausible, although less supported, alternative. Overall, imidacloprid effects were best represented by impaired energy assimilation combined with a direct effect on growth, rather than by reduced assimilation alone or by effects restricted to maintenance or reproduction.

The selected assimilation and growth model estimated a no-effect concentration ($c_0$) of 1,122 \[893 ; 1,511\] ng$\cdot$g$^{-1}$ (internal concentration) and a stress slope parameter ($b$) of 0.014 \[0.011 ; 8.1\] g$\cdot$ng$^{-1}$. The broader relative uncertainty associated with $b$ indicates that the increase in stress above the no-effect concentration was less precisely estimated than the threshold itself.

## Chains

::: panel-tabset
## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_A_IMD_A
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_A_IMD_A)
p_chains
  
```

```{r savechainsA_IMD_A, include = F}
ggsave(
  filename="A_IMD_A_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_B_IMD_M
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_B_IMD_M)
p_chains
  
```

```{r savechainsB_IMD_M, include = F}
ggsave(
  filename="B_IMD_M_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_C_IMD_G
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_C_IMD_G)
p_chains
  
```

```{r savechainsC_IMD_G, include = F}
ggsave(
  filename="C_IMD_G_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_D_IMD_R
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_D_IMD_R)
p_chains
  
```

```{r savechainsD_IMD_R, include = F}
ggsave(
  filename="D_IMD_R_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A & M

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_E_IMD_AM
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_E_IMD_AM)
p_chains
  
```

```{r savechainsE_IMD_AM, include = F}
ggsave(
  filename="E_IMD_AM_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_F_IMD_AG
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_F_IMD_AG)
p_chains
  
```

```{r savechainsF_IMD_AG, include = F}
ggsave(
  filename="F_IMD_AG_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_G_IMD_AR
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_G_IMD_AR)
p_chains
  
```

```{r savechainsG_IMD_AR, include = F}
ggsave(
  filename="G_IMD_AR_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## M & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_H_IMD_MG
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_H_IMD_MG)
p_chains
  
```

```{r savechainsH_IMD_MG, include = F}
ggsave(
  filename="H_IMD_MG_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## M & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_I_IMD_MR
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_I_IMD_MR)
p_chains
  
```

```{r savechainsI_IMD_MR, include = F}
ggsave(
  filename="I_IMD_MR_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```

## G & R

```{r, echo=F, message=F, warning=F}
#| fig-cap: Parameters chains. Only the last `r Nb_iter_kept` are represented.
#| label: fig-chains_J_IMD_GR
#| fig-height: 4
#| fig-width: 8

p_chains <- f_Plot_MCMC_Chains(MCMC_out_J_IMD_GR)
p_chains
  
```

```{r savechainsJ_IMD_GR, include = F}
ggsave(
  filename="J_IMD_GR_chains.png", 
  plot=p_chains, 
  width=8, height = 4, 
  path=path_fig
  )
```
:::

## Likelihood

::: panel-tabset
## A & G

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_F_IMD_AG
#| fig-height: 8
#| fig-width: 4

p_LL <- f_Plots_MCMC_Likelihood(MCMC_out_F_IMD_AG)
p_LL

```

```{r saveLLF_IMD_AG, include = F}
ggsave(
  filename="F_IMD_AG_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A

```{r, message=F, warning=F, echo=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-like_A_IMD_A
#| fig-height: 8
#| fig-width: 4

p_LL <- f_Plots_MCMC_Likelihood(MCMC_out_A_IMD_A)
p_LL

```

```{r saveLLA_IMD_A, include = F}
ggsave(
  filename="A_IMD_A_chainsLL.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig
  )
```
:::

## Chains convergence

::: panel-tabset
## A & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_F_IMD_AG
#| fig-height: 8
#| fig-width: 8

gelman <- f_Plot_Convergence(MCMC_out_F_IMD_AG)
print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_F_IMD_AG
#| fig-height: 5
#| fig-width: 6

file_rds <- here::here("fig/DEBTKTD_Models/F_IMD_AG_ipairs_plot.png")

f_Plot_ipairs(MCMC_out_F_IMD_AG, file_rds)

```

```{r, include = F}

col_corr <- colorRampPalette(c(
  "#BF616A",  # corrélations négatives
  "white",
  "#5E81AC"   # corrélations positives
))(200)

params_keep <- c("nec.1.", "b.1.")

mcmc_list_corr_F_IMD_AG <- f_mcmc_list_corr(MCMC_out_F_IMD_AG)

df_corr_F_IMD_AG <- cor(as.matrix(mcmc_list_corr_F_IMD_AG)[, params_keep])

dimnames(df_corr_F_IMD_AG) <- lapply(
  dimnames(df_corr_F_IMD_AG),
  \(x) gsub("\\.1\\.$", "", x)
)

png(file.path(path_fig, "F_IMD_AG_corrplot_article.png"), width = 2000, height = 2000, res = 300)

op <- par(font = 2)

corrplot.mixed(
  df_corr_F_IMD_AG,
  lower = "ellipse",
  upper = "number",
  tl.col = "#2E3440",
  tl.cex = 0.6,
  tl.pos = "d",
  number.cex = 0.7,
  tl.srt = 45,
  lower.col = col_corr,
  upper.col = col_corr
)

par(op)

dev.off()

```

## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Chains convergence.
#| label: fig-chainsconvergence_A_IMD_A
#| fig-height: 8
#| fig-width: 8

gelman <- f_Plot_Convergence(MCMC_out_A_IMD_A)
print(gelman)
```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr_A_IMD_A
#| fig-height: 5
#| fig-width: 6

file_rds <- here::here("fig/DEBTKTD_Models/A_IMD_A_ipairs_plot.png")
f_Plot_ipairs(MCMC_out_A_IMD_A, file_rds)

```

```{r, include = F}

col_corr <- colorRampPalette(c(
  "#BF616A",  # corrélations négatives
  "white",
  "#5E81AC"   # corrélations positives
))(200)

params_keep <- c("nec.1.", "b.1.")

mcmc_list_corr_A_IMD_A <- f_mcmc_list_corr(MCMC_out_A_IMD_A)

df_corr_A_IMD_A <- cor(as.matrix(mcmc_list_corr_A_IMD_A)[, params_keep])

dimnames(df_corr_A_IMD_A) <- lapply(
  dimnames(df_corr_A_IMD_A),
  \(x) gsub("\\.1\\.$", "", x)
)

png(file.path(path_fig, "A_IMD_A_corrplot_article.png"), width = 2000, height = 2000, res = 300)

op <- par(font = 2)

corrplot.mixed(
  df_corr_A_IMD_A,
  lower = "ellipse",
  upper = "number",
  tl.col = "#2E3440",
  tl.cex = 0.6,
  tl.pos = "d",
  number.cex = 0.7,
  tl.srt = 45,
  lower.col = col_corr,
  upper.col = col_corr
)

par(op)

dev.off()

```
:::

The posterior correlation between ($c_0$) and ($b$) was negligible for imidacloprid ($r=0.02$), indicating that the two toxicodynamic parameters were estimated largely independently (@fig-corr_F_IMD_AG).

## Posterior distributions

::: panel-tabset
## A & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_F_IMD_AG
#| fig-height: 4
#| fig-width: 8

p_post <- f_Plot_Posteriors(MCMC_out_F_IMD_AG)
p_post
```

```{r savepostF_IMD_AG, include = F}
ggsave(
  filename="F_IMD_AG_post.png", 
  plot=p_post, 
  width=8, height = 4, 
  path=path_fig
  )
```

## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-post_A_IMD_A
#| fig-height: 4
#| fig-width: 8

p_post <- f_Plot_Posteriors(MCMC_out_A_IMD_A)
p_post
```

```{r savepostA_IMD_A, include = F}
ggsave(
  filename="A_IMD_A_post.png", 
  plot=p_post, 
  width=8, height = 4, 
  path=path_fig
  )

```
:::

## Predicted vs. Obs

```{r setpointfullin}

Nb_experiment <- 22
step_sim <- 0.05
select_times <- seq(0,400, 0.1)

Endpoints_print <- "Weight,
    Reproduction,
    Ci"

l_param_name_F_IMD_AG <- names(Summary_res_F_IMD_AG) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_F_IMD_AG, Molec, 
  l_param_name_F_IMD_AG, step_sim, Endpoints_print
  )


l_param_name_A_IMD_A <- names(Summary_res_A_IMD_A) |>
  head(-1) |>
  stringr::str_remove_all("\\.1\\.")

f_In_Setpoint_full_TKTD(
  path_A_IMD_A, Molec, 
  l_param_name_A_IMD_A, step_sim, Endpoints_print
  )

```

```{bash, eval=F, execute=F}
for j in $(seq 1 22); do
./mcsim.DEB-IMD DEB_setpoint_full_${j}.in
done
```

```{r, message = F, warning = F}

width_plot <- 12
height_plot <- 12

file_rds_F_IMD_AG <- file.path(path_F_IMD_AG, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_F_IMD_AG)) {
  df_pred_full_F_IMD_AG <- readRDS(file_rds_F_IMD_AG)
} else {
  df_pred_full_F_IMD_AG <- f_read_Setpoint_full_TKTD(path_F_IMD_AG, Molec, select_times, step_sim)
}

file_rds_A_IMD_A <- file.path(path_A_IMD_A, paste0("Sim.Res.Exp.full.rds"))

if (file.exists(file_rds_A_IMD_A)) {
  df_pred_full_A_IMD_A <- readRDS(file_rds_A_IMD_A)
} else {
  df_pred_full_A_IMD_A <- f_read_Setpoint_full_TKTD(path_A_IMD_A, Molec, select_times, step_sim)
}

Nb_experiment <- 22

df_data_obs_IMD <- df_data_fit_IMD |> 
  mutate(
    Weight_obs = Weight,
    Reproduction_obs = Reproduction
    ) |> 
  dplyr::select(-c(Weight, Reproduction))

Condition_order <- c(
  "Control", "C1", "C2", "C3", "C4", "C5",
  "C6", "C7", "C8", "C9", "C10"
)

```

```{r, results=F, message=F, warning=F}

######## F_IMD_AG ###############################################################

Times_obs <- c(0,14,28)

df_pred_F_IMD_AG <- df_pred_full_F_IMD_AG |> 
  filter(Time %in% Times_obs)

df_pred_Weight_F_IMD_AG <- subset(df_pred_F_IMD_AG, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_F_IMD_AG <- subset(df_pred_F_IMD_AG, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_F_IMD_AG <- df_data_obs_IMD |> 
  filter(Time !=0 & Reproduction_obs !=0) |>
  left_join(df_pred_Reproduction_F_IMD_AG, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na() |> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

df_predobs_Weight_F_IMD_AG <- df_data_obs_IMD |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_F_IMD_AG, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na() |> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))


######## A_IMD_A ###############################################################

Times_obs <- c(0,14,28)

df_pred_A_IMD_A <- df_pred_full_A_IMD_A |> 
  filter(Time %in% Times_obs)

df_pred_Weight_A_IMD_A <- subset(df_pred_A_IMD_A, Endpt == "Weight" & Time !=0)
df_pred_Reproduction_A_IMD_A <- subset(df_pred_A_IMD_A, Endpt == "Reproduction" & Time !=0)

df_predobs_Reproduction_A_IMD_A <- df_data_obs_IMD |> 
  filter(Time !=0 & Reproduction_obs !=0) |>
  left_join(df_pred_Reproduction_A_IMD_A, suffix = c("_obs", "_pred")) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na() |> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

df_predobs_Weight_A_IMD_A <- df_data_obs_IMD |> 
  filter(Time !=0) |>
  left_join(df_pred_Weight_A_IMD_A, suffix = c("_obs", "_pred"))|>
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na() |> 
  mutate(Condition = ifelse(Dose == 0, "Control", Condition)) |> 
  mutate(Condition = factor(Condition, Condition_order))

#############################################

df_Exp_type_Dose_Condition_G <- df_data_obs_IMD |> 
  filter(Experiment_type == "Growth") |> 
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |> 
  distinct() |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

df_Exp_type_Dose_Condition_R <- df_data_obs_IMD |> 
  filter(Experiment_type == "Repro") |> 
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |> 
  distinct() |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

ID_levels_growth <- df_Exp_type_Dose_Condition_G |> 
  filter(Experiment_type == "Growth") |> 
  arrange(Condition) |> 
  pull(ID_experiment)

Facet_levels_growth <- df_Exp_type_Dose_Condition_G |> 
  filter(Experiment_type == "Growth") |> 
  arrange(Condition) |> 
  mutate(Facet_label = paste(Condition, ":", Dose/1000, "mg/kg")) |> 
  pull(Facet_label)

ID_levels_repro <- df_Exp_type_Dose_Condition_R |> 
  filter(Experiment_type == "Repro") |> 
  arrange(Condition) |> 
  pull(ID_experiment)

Facet_levels_repro <- df_Exp_type_Dose_Condition_R |> 
  filter(Experiment_type == "Repro") |> 
  arrange(Condition) |> 
  mutate(Facet_label = paste(Condition, ":", Dose/1000, "mg/kg")) |> 
  pull(Facet_label)

df_data_obs_IMD_G <- df_data_obs_IMD |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_data_obs_IMD_R <- df_data_obs_IMD |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )

###################################################@

df_predobs_Weight_F_IMD_AG_tmp <-  df_predobs_Weight_F_IMD_AG |> 
  left_join(
    (df_Exp_type_Dose_Condition_G |> dplyr::select(-c("Dose", "Experiment_type", "Condition"))),
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_predobs_Reproduction_F_IMD_AG_tmp <-  df_predobs_Reproduction_F_IMD_AG |> 
  left_join(
    (df_Exp_type_Dose_Condition_R |> dplyr::select(-c("Dose", "Experiment_type", "Condition"))),
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  ) 

###

df_predobs_Weight_A_IMD_A_tmp <-  df_predobs_Weight_A_IMD_A |> 
  left_join(
    (df_Exp_type_Dose_Condition_G |> dplyr::select(-c("Dose", "Experiment_type", "Condition"))),
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_predobs_Reproduction_A_IMD_A_tmp <-  df_predobs_Reproduction_A_IMD_A |> 
  left_join(
    (df_Exp_type_Dose_Condition_R |> dplyr::select(-c("Dose", "Experiment_type", "Condition"))),
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  ) 


```

::: panel-tabset
## A & G

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_F_IMD_AG
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  
  # Control + low doses
  "#4C566A", # Control
  "#DDE8D3",
  "#A3BE8C",
  "#879F72",
  "#718A5C",

  # Intermediate doses
  "#F2DFA3",
  "#E2B984",
  "#D08770",

  # High doses
  "#E4B6B9",
  "#BF616A",
  "#91434C"
)


seq_line <- seq(0.02, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_F_IMD_AG_tmp,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Facet_label,
    shape = Experiment_type
    ),
    alpha = 0.7
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "",
    values = col_experiment
    )+
  scale_shape_manual(
    name = "",
    values = c(shape_IMD, shape_EPX),
    label = c("Juveniles", "Adults")
  )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.05, 15, 0.05)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_F_IMD_AG_tmp,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Facet_label
    ),
    alpha = 0.7,
    shape = shape_EPX
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()#,
  # breaks = c(Val_Ctrl, 0.001, 0.01, 0.1, 1, 10, 100, 1000),
   #labels = c("0", "0.001", "0.01", "0.1", "1", "10", "100", "1000")
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()+
  theme(
    legend.position = "none"
  )

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs_IMD <- p_W + p_R + plot_layout(guides="collect")

p_predobs

```

```{r savepredobsF_IMD_AG, include = F}

ggsave(
  filename = "F_IMD_AG_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```

```{r, execute = F, include = F}

# hjust_plot <- 0
# 
# p_predobs_tot <- wrap_elements(p_predobs_IMD +
#   plot_annotation(
#     title = "Imidacloprid",
#     theme = theme(
#       plot.title = element_text(
#         face = "bold",
#         hjust = hjust_plot
#       )
#     )
#   )) / wrap_elements(p_predobs_EPX+
#   plot_annotation(
#     title = "Epoxiconazole",
#     theme = theme(
#       plot.title = element_text(
#         face = "bold",
#         hjust = hjust_plot
#       )
#     )
#   )) +
#   plot_annotation(tag_levels = "A")
# 
# ggsave(
#   filename = "FG_IMDEPX_predobs.png",
#   plot = p_predobs_tot,
#   width = 10, height = 8,
#   path = path_fig
# )
```

## A

```{r, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-predobs_A_IMD_A
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_experiment <- c(
  
  # Control + low doses
  "#4C566A", # Control
  "#DDE8D3",
  "#A3BE8C",
  "#879F72",
  "#718A5C",

  # Intermediate doses
  "#F2DFA3",
  "#E2B984",
  "#D08770",

  # High doses
  "#E4B6B9",
  "#BF616A",
  "#91434C"
)


seq_line <- seq(0.02, 1.5, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_A_IMD_A_tmp,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
    color = Facet_label,
    shape = Experiment_type
    ),
    alpha = 0.7
  )+
  scale_x_log10(
    labels = scales::label_number()
    )+
  scale_y_log10(
    labels = scales::label_number()
    )+
  scale_color_manual(
    name = "",
    values = col_experiment
    )+
  scale_shape_manual(
    name = "",
    values = c(shape_IMD, shape_EPX),
    label = c("Juveniles", "Adults")
  )+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.05, 15, 0.05)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_R <- ggplot(
  data = df_predobs_Reproduction_A_IMD_A_tmp,
  mapping = aes(
      x = Reproduction_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Facet_label
    ),
    alpha = 0.7,
    shape = shape_EPX
  )+
  labs(
    x = "Observed reproduction (#)",
    y = "Predicted reproduction (#)"
  )+
  scale_color_manual(
    name = "Experiments",
    values = col_experiment
    )+
  scale_x_log10(
   labels = scales::label_number()#,
  # breaks = c(Val_Ctrl, 0.001, 0.01, 0.1, 1, 10, 100, 1000),
   #labels = c("0", "0.001", "0.01", "0.1", "1", "10", "100", "1000")
    )+
  scale_y_log10(
   labels = scales::label_number()
    )+
  theme_minimal()+
  theme(
    legend.position = "none"
  )

p_predobs <- p_W + p_R +plot_layout(guides="collect") +
  plot_annotation(tag_levels = "A")

p_predobs

```

```{r savepredobsA_IMD_A, include = F}
ggsave(
  filename = "A_IMD_A_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig
) 
```
:::

## Predicted trajectories for Weight and Reproduction

```{r}

######### Plot preparation #####################################################

Condition_order <- c(
  "Control", "C1", "C2", "C3", "C4", "C5",
  "C6", "C7", "C8", "C9", "C10"
)

df_Exp_type_Dose_Condition_G <- df_data_obs_IMD |> 
  filter(Experiment_type == "Growth") |> 
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |> 
  distinct() |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

df_Exp_type_Dose_Condition_R <- df_data_obs_IMD |> 
  filter(Experiment_type == "Repro") |> 
  dplyr::select(ID_experiment, Experiment_type, Dose, Condition) |> 
  distinct() |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order)
  )

ID_levels_growth <- df_Exp_type_Dose_Condition_G |> 
  filter(Experiment_type == "Growth") |> 
  arrange(Condition) |> 
  pull(ID_experiment)

Facet_levels_growth <- df_Exp_type_Dose_Condition_G |> 
  filter(Experiment_type == "Growth") |> 
  arrange(Condition) |> 
  mutate(Facet_label = paste(Condition, ":", Dose/1000, "mg/kg")) |> 
  pull(Facet_label)

ID_levels_repro <- df_Exp_type_Dose_Condition_R |> 
  filter(Experiment_type == "Repro") |> 
  arrange(Condition) |> 
  pull(ID_experiment)

Facet_levels_repro <- df_Exp_type_Dose_Condition_R |> 
  filter(Experiment_type == "Repro") |> 
  arrange(Condition) |> 
  mutate(Facet_label = paste(Condition, ":", Dose/1000, "mg/kg")) |> 
  pull(Facet_label)

df_data_obs_IMD_G <- df_data_obs_IMD |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_data_obs_IMD_R <- df_data_obs_IMD |> 
  mutate(
    Condition = dplyr::recode(Condition, "Ctrl" = "Control"),
    Condition = factor(Condition, levels = Condition_order),
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )


######### F_IMD_AG ############################################################
df_pred_full_F_IMD_AG_plot_G <- df_pred_full_F_IMD_AG |> 
  left_join(
    df_Exp_type_Dose_Condition_G,
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_pred_full_F_IMD_AG_plot_R <- df_pred_full_F_IMD_AG |> 
  left_join(
    df_Exp_type_Dose_Condition_R,
    by = c("ID_experiment")
  ) |> 
  filter(Experiment_type == "Repro") |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )

######### A_IMD_A ############################################################
df_pred_full_A_IMD_A_plot_G <- df_pred_full_A_IMD_A |> 
  left_join(
    df_Exp_type_Dose_Condition_G,
    by = c("ID_experiment")
  ) |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_growth),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_growth)
  )

df_pred_full_A_IMD_A_plot_R <- df_pred_full_A_IMD_A |> 
  left_join(
    df_Exp_type_Dose_Condition_R,
    by = c("ID_experiment")
  ) |> 
  filter(Experiment_type == "Repro") |> 
  mutate(
    ID_experiment = factor(ID_experiment, levels = ID_levels_repro),
    Facet_label = paste(Condition, ":", Dose/1000, "mg/kg"),
    Facet_label = factor(Facet_label, levels = Facet_levels_repro)
  )

```

::: panel-tabset
## A & G

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each exposure condition and experiment.
#| label: fig-pred_F_IMD_AGsummary
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  max_WG <- 0.55
  max_WR <- 1.1
  max_RR <- 10
  
col_exp1 <- c(
  Nord_aurora[4],
  rev(nord("aurora", 12)[1:10])
)

col_experiment <- rep(col_exp1, 2)
  
  pW_G <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_F_IMD_AG_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_G, Experiment_type == "Growth"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of imidacloprid on juvenile growth"
    )+
    scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
    lims(y=c(0, max_WG))+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
  pW_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of imidacloprid on adult growth"
    )+
    scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
    lims(y=c(0, max_WR))+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
   pR_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Cumulated reproduction (#)",
      title ="Effect of imidacloprid on reproduction"
    )+
     scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
     lims(y = c(0,max_RR))+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

p_WR_R <- pW_R + pR_R 

p_WR_summary <- pW_G + pW_R + pR_R +
  plot_layout(ncol=3)
p_WR_summary

```

```{r savetrajWRF_IMD_AG_summary, include = F}
ggsave(
  filename="F_IMD_AG_trajWR_G.png", 
  plot=pW_G, 
  width=6, height = 6, 
  path=path_fig
  )

ggsave(
  filename="F_IMD_AG_trajWR_R.png", 
  plot=p_WR_R, 
  width=12, height = 6, 
  path=path_fig
  )
ggsave(
  filename="F_IMD_AG_trajWR_summary.png", 
  plot=p_WR_summary, 
  width=12, height = 9, 
  path=path_fig
  )
```

## A

```{r, echo=F, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for each exposure condition and experiment.
#| label: fig-pred_A_IMD_Asummary
#| fig-height: 18
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 2
  
col_exp1 <- c(
  Nord_aurora[4],
  rev(nord("aurora", 12)[1:10])
)

col_experiment <- rep(col_exp1, 2)
  
  pW_G <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_A_IMD_A_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_IMD_A_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_G, Experiment_type == "Growth"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on juvenile growth"
    )+
    scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
  pW_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_A_IMD_A_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_IMD_A_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of epoxiconazole on adult growth"
    )+
    scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
   pR_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_A_IMD_A_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_A_IMD_A_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = ID_experiment  
        ),
      alpha = 0.7,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Experiments",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Experiments",
      values = col_experiment
      )+
    facet_wrap(
      ~Facet_label,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Cumulated reproduction (#)",
      title ="Effect of epoxiconazole on reproduction"
    )+
     scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )

p_WR_R <- pW_R + pR_R 

p_WR_summary <- pW_G + pW_R + pR_R +
  plot_layout(ncol=3)
p_WR_summary


```

```{r savetrajWRA_IMD_A_summary, include = F}
ggsave(
  filename="A_IMD_A_trajWR_G.png", 
  plot=pW_G, 
  width=6, height = 6, 
  path=path_fig
  )

ggsave(
  filename="A_IMD_A_trajWR_R.png", 
  plot=p_WR_R, 
  width=12, height = 6, 
  path=path_fig
  )
ggsave(
  filename="A_IMD_A_trajWR_summary.png", 
  plot=p_WR_summary, 
  width=12, height = 9, 
  path=path_fig
  )
```
:::

Overall, the selected DEB-TKTD model captured the main concentration-response patterns observed for juvenile growth, adult growth, and reproduction (@fig-pred_F_IMD_AGsummary & @fig-predobs_F_IMD_AG). It reproduced the general decline in life-history performance with increasing imidacloprid exposure, supporting a physiological mode of action involving both reduced assimilation and altered growth processes.

Nevertheless, some systematic deviations remained across the exposure gradient. The model overestimated the effect on juvenile growth at intermediate imidacloprid concentrations (0.158 and 0.5 mg$\cdot$kg$^{-1}$) resulting in predicted values below the observations. Reproduction was similarly underestimated over this intermediate concentration range. At the highest concentrations, between 1.6 and 5 mg$\cdot$kg$^{-1}$, the model moderately underestimated the effect on growth and cocoon production.

## Summary

```{r, message=F, warning=F}
IMD_low_doses <- c(0, 1.6, 5, 16, 50)
IMD_int_doses <- c(158, 280, 500)
IMD_high_doses <- c(890, 1581, 5000)

Dose_level_levels <- c("Low doses", "Intermediate doses", "High doses")


df_pred_full_F_IMD_AG_plot_G <- df_pred_full_F_IMD_AG_plot_G |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% IMD_low_doses ~ "Low doses",
      Dose %in% IMD_int_doses ~ "Intermediate doses",
      Dose %in% IMD_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

df_data_obs_IMD_G <- df_data_obs_IMD_G |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% IMD_low_doses ~ "Low doses",
      Dose %in% IMD_int_doses ~ "Intermediate doses",
      Dose %in% IMD_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

df_pred_full_F_IMD_AG_plot_R <- df_pred_full_F_IMD_AG_plot_R |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% IMD_low_doses ~ "Low doses",
      Dose %in% IMD_int_doses ~ "Intermediate doses",
      Dose %in% IMD_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

df_data_obs_IMD_R <- df_data_obs_IMD_R |> 
  mutate(
    Dose_level = factor(case_when(
      Dose %in% IMD_low_doses ~ "Low doses",
      Dose %in% IMD_int_doses ~ "Intermediate doses",
      Dose %in% IMD_high_doses ~ "High doses"
    ), Dose_level_levels)
  )

```

```{r, message=F, warning=F}
#| fig-cap: Predicted Weight and Reproduction for exposure condition.
#| label: fig-pred_F_IMD_AG_summary_article
#| fig-height: 10
#| fig-width: 12

# Plot
  alpha_ribbon <- 0.15
  alpha_point <- 0.9
  line_width <- 1.1
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 1
  max_WG <- 0.55
  max_WR <- 1.1
  max_RR <- 10
  

col_experiment <- c(
  
  # Control + low doses
  "#4C566A", # Control
  "#DDE8D3",
  "#A3BE8C",
  "#879F72",
  "#718A5C",

  # Intermediate doses
  "#F2DFA3",
  "#E2B984",
  "#D08770",

  # High doses
  "#E4B6B9",
  "#BF616A",
  "#91434C"
)

  
  pW_G <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_F_IMD_AG_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_G, Endpt == "Weight" & Experiment_type == "Growth"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_G, Experiment_type == "Growth"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = alpha_point,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Condition",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Condition",
      values = col_experiment
      )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of imidacloprid on juvenile growth"
    )+
    scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none",
    strip.text = element_blank()
  )
  
  pW_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = ID_experiment
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Weight" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = ID_experiment
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Weight_obs, 
          color = ID_experiment  
        ),
      alpha = alpha_point,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "Condition",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "Condition",
      values = col_experiment
      )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Weight (g)",
      title ="Effect of imidacloprid on adult growth"
    )+
    scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.position = "none"
  )
  
   pR_R <- ggplot()+

    geom_ribbon(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        ymax = up,
        ymin = low,
        fill = Facet_label
      ),
      alpha = alpha_ribbon
    )+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_R, Endpt == "Reproduction" & Experiment_type == "Repro"),
      aes(
        x = Time,
        y = predict.endpoint,
        color = Facet_label
      ),
      linewidth = line_width,
      alpha = alpha_line
    )+
    
    geom_point(
      data = subset(df_data_obs_IMD_R, Experiment_type == "Repro"),    
      mapping = 
        aes(  
          x = Time, 
          y = Reproduction_obs, 
          color = Facet_label  
        ),
      alpha = alpha_point,
      stroke = point_stroke
    )+
    
    scale_color_manual(
      name = "",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "",
      values = col_experiment
      )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col
      )+
    labs(
      x="Time (days)", 
      y = "Cumulated reproduction (#)",
      title ="Effect of imidacloprid on reproduction"
    )+
     scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
    theme_minimal()+
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.title = element_text(face = "bold"),
    strip.text = element_blank()
  )

p_WR_R <- pW_R + pR_R 

p_WR_summary <- pW_G + pW_R + pR_R +
  plot_layout(ncol=3)

p_WR_summary

```

```{r savetrajWRF_IMD_AG_article, include = F}
ggsave(
  filename="F_IMD_AG_trajWR_article.png", 
  plot=p_WR_summary, 
  width=12, height = 8, 
  path=path_fig
  )
```

```{r, message=F, warning=F}
#| fig-cap: Predicted internal concentration in imadacloprid for each exposure condition.
#| label: fig-pred_F_IMD_AG_summary_Ciarticle
#| fig-height: 6
#| fig-width: 6

# Plot
  alpha_ribbon <- 0.15
  alpha_point <- 0.9
  line_width <- 0.8
  point_stroke <- 0.9
  alpha_line <- 0.7
  wrap_nb_col <- 1
  max_WG <- 0.55
  max_WR <- 1.1
  max_RR <- 10
  

col_experiment <- c(
  
  # Control + low doses
  "#4C566A", # Control
  "#DDE8D3",
  "#A3BE8C",
  "#879F72",
  "#718A5C",

  # Intermediate doses
  "#F2DFA3",
  "#E2B984",
  "#D08770",

  # High doses
  "#E4B6B9",
  "#BF616A",
  "#91434C"
)

df_pred_full_F_IMD_AG_plot_tot <- rbind(df_pred_full_F_IMD_AG_plot_G, df_pred_full_F_IMD_AG_plot_R)

  
  p_Ci_summary <- ggplot()+
    
    geom_line(
      data = subset(df_pred_full_F_IMD_AG_plot_tot, Endpt == "Ci" & Experiment_type %in% c("Growth", "Repro")),
      aes(
        x = Time,
        y = predict.endpoint,
        color = Facet_label,
        linetype = Experiment_type
      ),
      linewidth = line_width
    )+
    
    scale_color_manual(
      name = "",
      values = col_experiment
      )+
    scale_fill_manual(
      name = "",
      values = col_experiment
      )+
    scale_linetype_manual(
      name = "",
      label = c("Juveniles", "Adults"),
      values = c(3, 1)
    )+
    facet_wrap(
      ~Dose_level,
      ncol = wrap_nb_col,
      scales = "free_y"
      )+
    labs(
      x="Time (days)", 
      y = "Internal concentration of imidacloprid (ng/g)"
    )+
    theme_minimal()+
  scale_x_continuous(
    limits = c(0, 28),        
    breaks = seq(0, 28, by = 14)
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 11),
    legend.title = element_text(face = "bold")
  )
  

p_Ci_summary

p_Ci_summary_IMD <- p_Ci_summary

```

```{r savetrajCi_F_IMD_AG_article, include = F}
ggsave(
  filename="F_IMD_AG_trajCi_article.png", 
  plot=p_Ci_summary, 
  width=5, height = 6, 
  path=path_fig
  )
```

```{r}
#| tbl-cap: Predicted $C_{i, \mathrm{max}}$ and $t_{\mathrm{max}}$ for each exposure concentration and experiment.
#| label: tbl-Cirecap

df_pred_Ci_F_IMD_AG_summary <- subset(df_pred_full_F_IMD_AG, Endpt == "Ci" & Time !=0)|>
  group_by(ID_experiment) |>
  filter(predict.endpoint == max(predict.endpoint, na.rm = TRUE)) |>
  slice_min(Time, n = 1, with_ties = FALSE) |>
  ungroup() |>
  dplyr::select(ID_experiment, Time, predict.endpoint)

df_pred_Ci_F_IMD_AG_summary |> datatable()
```
